### 2023-12-11 manuscript-figures.Rmd
initial commit

---
title: "Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission"
author: |
    | Kyle J.-M. Dahlin, Suzanne M. O'Regan, Barbara A. Han,
    | John Paul Schmidt, John M. Drake
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    keep_tex: yes
    extra_dependencies: ["float"]
    includes:
      in_header: header.tex
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "doc") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp)
library(reshape2)
library(cowplot)
library(viridis)
library(RColorBrewer) # for colorblind friendly color palettes
library(MetBrewer) # for colorblind friendly color palettes
library(cols4all) # for colorblind friendly color palettes
library(here)
library(lemon)
library(see) # for half-violin plots
library(zplyr) #devtools::install_github("burchill/zplyr") from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contdact comparison figure

# Plot settings ----

# Set theme
theme_set(theme_minimal(10))

# Helper function: adds a "point at infinity" for plots with infinite sigmaH
inf_skew_func <- function(df, skew, divide, n_rows_to_add) {
  # Get the largest value of log10(sigmaH) in the data frame
  max_log10sigmaH <- filter(df, is.finite(sigmaH)) %>%
    select(sigmaH) %>%
    max() %>%
    log10()

  # Define the gap dividing finite and infinite sigmaH
  infinite_divide <- 10^mean(log10(c(divide, skew)))

  # Create a proxy sigmaH variable that replaces Inf with the value of "skew"
  df <- mutate(df, sigmaH_proxy = ifelse(is.finite(sigmaH),
                                         sigmaH, skew
  ))

  # add more proxy sigmaH values to make a "spread" at Inf
  added_sigma_vals <- seq(divide, skew, length.out = n_rows_to_add)
  for (i in 1:n_rows_to_add) {
    bump_val <- 1 + 0.05 * (i - 1)
    temp <- filter(df, is.infinite(sigmaH)) %>%
      mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                                   added_sigma_vals[i]
      ))
    df <- add_row(df, temp) %>% distinct()
  }
  return(df)
}

# Label functions:
appender_sigmaH <- function(string) {
  ifelse(string == "Inf",
         unname(TeX(paste("$\\sigma_H = \\infty$"))),
         unname(TeX(paste("$\\sigma_H = $", string)))
  )
}
appender_KH <- function(string) {
  unname(TeX(paste("$K_H = $", string)))
}

sens_labels <- as_labeller(c(
  "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti* and  \nDENV",
  "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti* and   \nZIKV",
  "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand DENV",
  "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae* and  \n*P. falciparum*",
  "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
))

# Helper function: place legends in empty facets of plot grids
# Code by: Artem Sokolov, found here: https://stackoverflow.com/questions/54438495/shift-legend-into-empty-facets-of-a-faceted-plot-in-ggplot2
shift_legend <- function(p) {
  pnls <- cowplot::plot_to_gtable(p) %>%
    gtable::gtable_filter("panel") %>%
    with(setNames(grobs, layout$name)) %>%
    purrr::keep(~ identical(.x, zeroGrob()))

  if (length(pnls) == 0) stop("No empty facets in the plot")

  lemon::reposition_legend(p, "center", panel = names(pnls))
}

# Helper function: apply nice labels for pathosystems
pathosystem_labeller <- function(df) {
  df <- df %>%
    ungroup() %>%
    mutate(system_label = case_when(
      system_ID == "Aedes aegypti / DENV" ~ "(a) *Ae. aegypti* and DENV",
      system_ID == "Aedes aegypti / ZIKV" ~ "(b) *Ae. aegypti* and ZIKV",
      system_ID == "Aedes albopictus / DENV" ~ "(c&#41; *Ae. albopictus* and DENV",
      system_ID == "Anopheles gambiae / Plasmodium falciparum" ~ "(d) *An. gambiae* and *P. falciparum*",
      system_ID == "Culex quinquefasciatus / WNV" ~ "(e) *Cx. quinquefasciatus* and WNV"
    ))
  return(df)
}

# Helper function: apply nice labels for focal variables
focalvar_labeller <- function(df) {
  df <- df %>%
    mutate(focal_var = factor(focal_var,
                              levels = c("total", "muV", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "etaV", "betaV"),
                              labels = c(
                                TeX("Overall"),
                                TeX("Adult mortality rate"),
                                TeX("Biting frequency"),
                                TeX("Eggs per female per day"),
                                TeX("Immature development rate"),
                                TeX("Prob. of immature survival"),
                                TeX("Parasite development rate"),
                                TeX("Vector competence")
                              )
    ))
}

# Load required data ----

eps <- .Machine$double.eps

# Vector trait TPC data

# Create data frame of TPCs

data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
  pathosystem_labeller()

# thin_size <- 500
# num_samples <- length(unique(data.Vec$sample_num))
# sample_inds <- sample(1:num_samples, thin_size, replace = FALSE)
# 
# data.Vec <- filter(data.Vec, sample_num %in% sample_inds)

# R0 data
data.R0_TPCs <- read_rds("results/R0_TPC_vals.rds") %>%
  pathosystem_labeller()

data.R0 <- read_rds("results/R0_vals.rds") %>%
  pathosystem_labeller()

# Topt data
data.Topt <- read_rds("results/Topt_vals.rds") %>%
  pathosystem_labeller()

# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds") %>%
  pathosystem_labeller()

# Local sensitivity of R0 to mosquito traits
data.dR0dvar <- read_rds("results/dR0dk_vals.rds") %>%
  ungroup() %>%
  pathosystem_labeller() %>%
  focalvar_labeller()

# Densities of CTmin/max and Topt
all.density.df <- read_rds("results/CTminmaxTopt_densities.rds") %>%
  ungroup() %>%
  pathosystem_labeller() %>%
  filter(KH > 0.01)

# Uncertainty data for R0
R0.HPD <- read_rds("results/R0_HPD_unc.rds") %>%
  ungroup() %>%
  pathosystem_labeller() %>%
  focalvar_labeller()

# Uncertainty data for the derivative of R0 wrt temperature
ddTR0.HPD <- read_rds("results/ddTR0_HPD_unc.rds") %>%
  ungroup() %>%
  pathosystem_labeller() %>%
  focalvar_labeller()

# Uncertainty data for Topt
Topt.HPD <- read_rds("results/Topt_HPD_unc.rds") %>%
  mutate(focal_var = ifelse(focal_var == "lf", "muV", focal_var)) %>% 
  ungroup() %>%
  pathosystem_labeller() %>%
  focalvar_labeller()

# Uncertainty data for critical thermal extrema
CT.HPD <- read_rds("results/CT_HPD_unc.rds") %>%
  ungroup() %>%
  pathosystem_labeller() %>%
  focalvar_labeller()

# Derivative of Topt with respect to host pop. density
dToptdKH.HPD <- read_rds("results/dToptdKH_HPD_unc.rds") %>%
  ungroup() %>%
  distinct() %>%
  filter(!is.na(HPD_width)) %>%
  pathosystem_labeller() %>%
  focalvar_labeller()

# Configure data sets for plotting ----

## Get values of vector traits across samples
# Mean values
mean.Vec <- read_rds("results/meanVec_vals.rds")

# Median values (this one is used more frequently)
median.Vec <- read_rds("results/medianVec_vals.rds")

# Compute *mosquito* thermal tolerance range (minimum and maximum)
MosqThermRange_df <- mean.Vec %>%
  pathosystem_labeller() %>%
  group_by(system_label) %>%
  filter(V0 > 0) %>%
  mutate(CTmin_V0 = min(Temperature)) %>%
  mutate(CTmax_V0 = max(Temperature)) %>%
  dplyr::select(system_ID, system_label, CTmin_V0, CTmax_V0) %>%
  distinct()
```

# Figures

```{r fig-1_contact_comparison, dev = c('pdf','svg', 'png'), out.width='100%', fig.align='center', fig.height=5, fig.width=7, fig.align='center', fig.cap='\\label{fig:contact_comparison} A comparison of the Chitnis dynamic contact rate and the standard Ross-Macdonald contact rate models. In the left columns, mosquito population is held constant while in the right columns host population density is held constant. Upper panel: In the Ross-Macdonald model, the mosquito biting rate is constant with respect to both host and mosquito population density (a and b, blue lines) while in the Chitnis model mosquito biting increases with host population density (a, red curve) and decreases with mosquito population density (b, red curve). Lower panels: The relationships between the number of bites that a host receives per day and host and mosquito densities diverge at low host population densities (c) and, to a lesser extent, at high mosquito densities (d). For plots (a) and (c), mosquito population density is fixed at 1000 individuals per km2. For plots (b) and (d), host population density is fixed at 10 individuals per square kilometer. Maximum mosquito biting rate is 0.45 bites per mosquito per day and maximum host biting rate is 100 bites per host per day. Mosquito and host population densities are plotted on a logarithmic scale. '}
# resolution setting
resolution <- 1E2

## Define the contact models
# For each model, there is a vector-to-host and host-to-vector term

# Bites per mosquito per day
vector_host_contact_func <- function(df) {
  with(as.list(df), {
    ret <- case_when(
      # Ross-Macdonald aka Reservoir frequency dependence
      model == "RM" ~ sigma_V,
      # Chitnis dynamic
      model == "CD" ~ sigma_V * sigma_H * H / (sigma_H * H + sigma_V * V)
    )
  })
}

# Bites per host per day
host_vector_contact_func <- function(df) {
  with(as.list(df), {
    ret <- case_when(
      # Ross-Macdonald aka Reservoir frequency dependence
      model == "RM" ~ sigma_V * V / H,
      # Chitnis dynamic
      model == "CD" ~ sigma_H * sigma_V * V / (sigma_H * H + sigma_V * V)
    )
  })
}

## Set up density ranges
host_density_range <- c(1E0, 1E3)
host_fixed_value <- 10
host_density_vec <- sort(c(10^seq(log10(host_density_range[1]),
                                  log10(host_density_range[2]),
                                  length.out = resolution
), host_fixed_value))

vector_density_range <- c(1E0, 1E3)
vector_fixed_value <- 1000
vector_density_vec <- sort(c(10^seq(log10(vector_density_range[1]),
                                    log10(vector_density_range[2]),
                                    length.out = resolution
), vector_fixed_value))

## Set other parameters
max_biting_rate <- 0.45
sigma_V <- max_biting_rate

host_annoyance_threshold <- 100
sigma_H <- host_annoyance_threshold

## Create contact dynamics dataframe
models <- c("RM", "CD")
names(models) <- c("Ross-Macdonald", "Chitnis dynamic")

contact_df <- expand.grid(
  H = host_density_vec,
  V = vector_density_vec,
  sigma_V = sigma_V,
  sigma_H = sigma_H,
  model = models
) %>%
  mutate("Transmission model" = names(model)) %>%
  mutate(bites_mosquito_time = vector_host_contact_func(.)) %>%
  mutate(bites_host_time = host_vector_contact_func(.)) %>%
  rename("Host population density" = H) %>%
  rename("Mosquito population density" = V) %>%
  rename("Bites per mosquito per day" = bites_mosquito_time) %>%
  rename("Bites per host per day" = bites_host_time)

## Put plots together:
new_df <- contact_df %>%
  filter(`Mosquito population density` == vector_fixed_value |
           `Host population density` == host_fixed_value) %>%
  select(-sigma_V, -sigma_H, -model) %>%
  melt(
    id = c(
      "Transmission model", "Bites per mosquito per day",
      "Bites per host per day"
    ),
    value.name = "x_vals"
  ) %>%
  rename(x_vars = variable) %>%
  melt(id = c("Transmission model", "x_vars", "x_vals"), value.name = "y_vals") %>%
  rename(y_vars = variable) %>%
  filter(x_vals != host_fixed_value & x_vals != vector_fixed_value) %>%
  mutate(y_max = 1.05 * y_vals) %>%
  mutate(label = case_when(
    x_vars == "Host population density" & y_vars == "Bites per mosquito per day" ~ "(a)",
    x_vars == "Mosquito population density" & y_vars == "Bites per mosquito per day" ~ "(b)",
    x_vars == "Host population density" & y_vars == "Bites per host per day" ~ "(c)",
    x_vars == "Mosquito population density" & y_vars == "Bites per host per day" ~ "(d)"
  )) %>%
  distinct()

# x = Host population density, y = Bites per mosquito per day
plot_HD_MC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per mosquito per day",
    expand = c(0, 0)
  )

# x = Mosquito population density, y = Bites per mosquito per day
plot_MD_MC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per mosquito per day") %>%
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    # limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)

# x = Mosquito population density, y = Bites per host per day
plot_MD_HC <- new_df %>%
  filter(x_vars == "Mosquito population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "Mosquito population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "",
    expand = c(0, 0),
    # limits = c(0, NA)
  )

# x = Host population density, y = Bites per host per day
plot_HD_HC <- new_df %>%
  filter(x_vars == "Host population density") %>%
  filter(y_vars == "Bites per host per day") %>%
  # x = density variables, y = contact rates
  ggplot(aes(x = x_vals, y = y_vals, colour = `Transmission model`)) +
  # curves:
  geom_path(size = 1) +
  geom_blank(aes(y = y_max)) +
  # plot labels
  geom_abs_text(aes(xpos = 0.08, ypos = 0.89, label = label),
                color = "black", show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = "Host population density",
    expand = expansion(mult = c(0, .025))
  ) +
  # y-axis:
  scale_y_continuous(
    name = "Bites per host per day",
    expand = c(0, 0),
    # limits = c(0, NA)
  ) +
  # hide legend
  guides(color = FALSE)

# Combine plots into a grid and remove legends
contact_plot <- plot_grid(
  plot_HD_MC + theme(legend.position = "none"),
  plot_MD_MC + theme(legend.position = "none"),
  plot_HD_HC + theme(legend.position = "none"),
  plot_MD_HC + theme(legend.position = "none")
)

# Set legend to bottom of grid
legend <- get_legend(
  plot_HD_MC +
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)

# Put together grid and legend
contact_plot <- plot_grid(contact_plot, legend, ncol = 1, rel_heights = c(1, .05))

# Plot
contact_plot
```

```{r fig-3_MosquitoThermalTraits, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model. Curves are shown in color for each of the five systems we considered. Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive). Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d). Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7. The \\textit{Aedes aegypti} and DENV and \\textit{Ae. aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al. (2018)). All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020. Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions. A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
## Set up plot dataframe
MosqThermTraits_df <- median.Vec %>%
  # Mortality rate
  mutate(muV = 1 / lf) %>%
  # Recruitment rate
  mutate(lambdaV = V0 * muV) %>%
  # Prob. of surviving EIP
  mutate(P_EIP = exp(-muV / etaV)) %>%
  # Prob. of larval survival
  # Select relevant traits and parameters
  dplyr::select(Temperature, system_ID, sigmaV, sigmaV_f, rhoL, lf, deltaL, P_EIP, betaV) %>%
  # Turn all columns except Temperature and system_ID into variables
  melt(id = c("Temperature", "system_ID")) %>%
  mutate(variable = factor(variable,
                           levels = c("lf", "sigmaV", "sigmaV_f", "rhoL", "deltaL", "P_EIP", "betaV"),
                           labels = c(
                             TeX("(a) Adult lifespan: $1/\\mu_V$ (days)"),
                             TeX("(b) Biting frequency: $\\sigma_V$ (day$^{-1}$)"),
                             TeX("(c) Eggs per female per day: $\\sigma_V f$"),
                             TeX("(d) Immature mosquito development rate: $\\rho_L$ (day$^{-1}$)"),
                             TeX("(e) Probability of immature mosquito survival: $\\delta_L$"),
                             TeX("(f) Probability of surviving EIP: $\\theta_V$"),
                             TeX("(g) Vector competence: $\\beta_V$")
                           )
  )) %>%
  group_by(Temperature, system_ID)

MosqThermTraits_plot <- MosqThermTraits_df %>%
  # Set up plotting variables and theme
  # x = Temperature, y = trait value
  ggplot(mapping = aes(x = Temperature, y = value, group = system_ID)) +
  # Plot trait values:
  geom_line(aes(colour = system_ID), size = 1) +
  # x-axis:
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0),
    limits = c(10, 40),
    breaks = seq(10, 40, 2)
  ) +
  # y-axis:
  scale_y_continuous(expand = c(0.05, 0)) +
  # color:
  scale_color_manual(
    name = "System:",
    values = met.brewer("Egypt", 5, direction = -1),
    labels = function(x) {
      case_when(
        x == "Aedes aegypti / DENV" ~ "*Aedes aegypti* and DENV",
        x == "Aedes aegypti / ZIKV" ~ "*Ae. aegypti* and ZIKV",
        x == "Aedes albopictus / DENV" ~ "*Aedes albopictus* and DENV",
        x == "Anopheles gambiae / Plasmodium falciparum" ~ "*Anopheles gambiae* and *Plasmodium falciparum*",
        x == "Culex quinquefasciatus / WNV" ~ "*Culex quinquefasciatus* and WNV"
      )
    }
  ) +
  # faceting:
  facet_wrap(~variable,
             nrow = 3, scales = "free",
             labeller = labeller(variable = label_parsed)
  ) +
  # legend:
  guides(color = guide_legend(override.aes = list(size = 4))) +
  # theme options:
  theme_minimal_vgrid(10) +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom",
    legend.margin = margin(),
    legend.text = ggtext::element_markdown(),
    legend.direction = "vertical",
    legend.justification = "center",
    axis.title.x = element_text(hjust = 0),
    strip.text = element_text(
      face = "bold",
      hjust = 0
    )
  )

shift_legend(MosqThermTraits_plot)
```

```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} $\\mathcal{R}_0$ as a function of temperature has the usual properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value. The shape of the $\\mathcal{R}_0$ TPC depends on vertebrate host availability and the mosquito-parasite system. The shape of the thermal response of $\\mathcal{R}_0$ derived from the Ross-Macdonald model (dotted black curves) is independent of vertebrate host population density while those derived from the Chitnis dynamic model are dependent on vertebrate host population density (solid lines in color). Shown here are the median values of $\\mathcal{R}_0$ with respect to the mosquito trait TPC posterior distributions. $\\mathcal{R}_0$ is normalized by dividing by its maximum value in each system, for the given value of biting tolerance and vertebrate host population density. Vertebrate host population density is varied on a log$_{10}$ scale.'}
# Plot R0 vs. temperature curves. One plot for each system
# One curve for Ross-Macdonald, a few for Chitnis

# x-axes = temperature
# y-axes = R0 (normalized so that max(R0) = 1)
# plots = one for each mosquito+pathogen combination, "system_ID"
# curve 1 = Ross-Macdonald R0 (shape doesn't depend on KH)
# curves  = Chitnis dynamic R0,
#   - colour = value of KH. place it on a color scale in the bottom right corner
# newKH_vals <- unique(data.R0$KH)[seq(1, length(unique(data.R0$KH)), length.out = 21)]

data.R0_norm <- data.R0_TPCs %>%
  filter(KH %in% unique(data.R0_TPCs$KH)[seq(1, length(unique(data.R0_TPCs$KH)), length.out = 21)]) %>%
  filter(variable == "R0") %>%
  select(-variable) %>%
  # normalize median of R0 distribution to have a maximum of one
  group_by(system_ID, Model, sigmaH, KH) %>%
  mutate(median_norm = median / max(median)) %>%
  arrange(system_ID, sigmaH, KH, Temperature, median_norm)

R0_plot <- ggplot(mapping = aes(x = Temperature, group = KH)) +
  # path of mean, normalized R0 as a function of temperature (finite sigmaH):
  geom_path(
    data = filter(data.R0_norm, sigmaH == 100),
    aes(y = median_norm, colour = KH, linetype = "finite"),
    lwd = 1
  ) +
  # path of mean, normalized R0 as a function of temperature (infinite sigmaH):
  geom_path(
    data = filter(data.R0_norm, sigmaH == Inf),
    aes(y = median_norm, linetype = "infinite", colour = "black"),
    colour = "black",
    lwd = 1.5
  ) +
  # x-axis:
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0),
    limits = c(14, 34)
  ) +
  # y-axis:
  scale_y_continuous(
    name = TeX("Normalized $R_0$"),
    expand = c(0, .05)
  ) +
  # color: scaled log10, color-blind friendly
  scale_color_viridis(
    name = "Vertebrate host population\ndensity (ind/ha)",
    trans = "log10",
    breaks = 10^seq(-2, 4),
    labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
    option = "plasma"
  ) +
  # fill: scaled log10, color-blind friendly
  scale_fill_viridis(
    name = "Vertebrate host population\ndensity (ind/ha)",
    trans = "log10",
    breaks = 10^seq(-2, 4),
    labels = unname(c(0.01, 0.1, 1, 10, 100, TeX("$10^3$"), TeX("$10^4$"))),
    option = "plasma"
  ) +
  # linetype:
  scale_linetype_manual(
    name = "Biting tolerance\n(bites per host per day)",
    breaks = c("finite", "infinite"),
    labels = unname(c(TeX("100 (Chitnis)"), TeX("$\\infty$ (Ross-Macdonald)"))),
    values = c("solid", "22")
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend
  guides(
    color = guide_colourbar(
      title.position = "top",
      nrow = 1,
      barwidth = 12,
      show.limits = TRUE,
      direction = "horizontal"
    ),
    linetype = guide_legend(
      title.position = "top",
      nrow = 2,
      keywidth = 4,
      direction = "vertical"
    )
  ) +
  # theme options:
  theme_minimal_vgrid(10) +
  theme(
    legend.box = "vertical",
    legend.margin = margin(),
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(R0_plot)
```

```{r fig-5_Topt, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt} The thermal optimum for transmission, $T_{\\mathrm{opt}}$, may be sensitive to vertebrate host population density and biting tolerance. Here, $T_{\\mathrm{opt}}$ is plotted as a function of vertebrate host population density and biting tolerance for each of the five systems. In the Ross-Macdonald model, where biting tolerance is assumed to be infinite, $T_{\\mathrm{opt}}$ is independent of vertebrate host population density (upper bars in plots). But when biting tolerance is limited, $T_{\\mathrm{opt}}$ can vary as much as 5\textdegree C (d). $T_{\\mathrm{opt}}$ may increase (d) or decrease (a, b, c, e) as vertebrate host population density or biting tolerance is increased. Shown here are the median values of $T_{\\mathrm{opt}}$ with respect to the mosquito trait TPC posterior distributions. Both biting tolerance and vertebrate host population density are varied on a $\\log_{10}$ scale. $\\mathcal{R}_0$ is greater than one in the region contained within the black $\\mathcal{R}_0=1$ curve. All remaining parameters are given in Table 1 and Figure 3. '}
# Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.

#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = width of parasite thermal niche (CTmax - CTmin)
# Facets = systems

# Value of sigmaH to replace 'Inf' with for plotting
infinite_skew <- 10^2.35
# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^2.7
Toptalt_df <- data.Topt %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, median) %>%
  mutate(sigmaH_proxy = sigmaH) %>% 
  filter(sigmaH_proxy < infinite_skew | is.infinite(sigmaH_proxy))

# add many proxy sigmaH points at infinity to make the values easier to see there
max_sigmaH <- max(filter(Toptalt_df, is.finite(sigmaH))$sigmaH)

Toptalt_df <- inf_skew_func(Toptalt_df, infinite_skew, infinite_divide, 8)

# Define sigmaH tick breaks and labels
sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

min_Topt <- floor(min(min(Toptalt_df$mean), min(Toptalt_df$median)))
max_Topt <- ceiling(max(max(Toptalt_df$mean), max(Toptalt_df$median)))
Topt_breaks <- seq(min_Topt, max_Topt, by = 1)

# Plot median of Topt heat map
Toptalt_plots <- Toptalt_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # Topt for FINITE sigmaH:
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy < 10^2.2),
    breaks = Topt_breaks
  ) +
  # Topt for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(Toptalt_df, sigmaH_proxy > infinite_skew) %>%
      group_by(system_ID) %>%
      mutate(median = median(median), .groups = "keep"),
    size = 1,
    breaks = Topt_breaks
  ) +
  # # R0 = 1 contour: use where CTwidth = 0 (i.e. where R0<1 at any temperature)
  geom_contour(
    data = filter(data.CT, variable == "CTwidth", sigmaH < infinite_divide),
    aes(y = sigmaH, z = median, colour = "R0 = 1"),
    breaks = min(filter(data.CT, variable == "CTwidth", median > 0)$median),
    size = 1
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.01, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
  scale_fill_manual(
    name = "Transmission thermal optimum (°C)",
    values = met.brewer("Johnson",
                        n = length(Topt_breaks),
                        direction = -1
    )
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c("R0=1" = unname(TeX("$\\mathcal{R}_0=1$"))),
    values = c("black"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(1, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "vertical",
    legend.position = "right",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(Toptalt_plots)
```

```{r fig-6_CT_Width, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Width} The parasite population thermal niche, the range of temperatures at which parasite transmission is expected to persist, is widest when biting tolerance is high and vertebrate host population density is low. As vertebrate host population density approaches an upper threshold, the width of the parasite population thermal niche shrinks to zero. At low levels of biting tolerance, there is also a lower threshold to vertebrate host population density. Shown here are the median values of $\\textrm{CT}_{\\textrm{width}}$ with respect to the mosquito trait TPC posterior distributions. Vertebrate host population density and biting tolerance are both plotted on $\\log_{10}$ scales. Biting tolerance is varied from one to one thousand bites per day, with an additional point at infinity to illustrate the case where biting tolerance is unlimited (the Ross-Macdonald model). Both biting tolerance and vertebrate host population density are varied on a $\\log_{10}$ scale. All remaining parameters are given in Table 1 and Figure 3.'}
# Shows how the parasite thermal niche (temperatures between CT_min and CT_max)
# depends on vertebrate host availability (density and biting tolerance) in each
# of the focal systems.

#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = width of parasite thermal niche (CTmax - CTmin)
# Facets = systems

CTwidth_df <- data.CT %>%
  filter(variable == "CTwidth") %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>%
  ungroup()

CTwidth_df <- inf_skew_func(CTwidth_df, infinite_skew, infinite_divide, 8)

CTWidth_heat_plots <- CTwidth_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # CTwidth for FINITE sigmaH:
  geom_contour_filled(data = filter(CTwidth_df, sigmaH_proxy < 10^2.2)) +
  # CTwidth for INFINITE sigmaH:
  geom_contour_filled(data = filter(
    CTwidth_df,
    sigmaH_proxy > 10^2.4,
    sigmaH_proxy < infinite_divide
  )) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Parasite thermal tolerance\nrange width (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12, # unit(5, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(CTWidth_heat_plots)
```

# Supplementary Figures

```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density. The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp. and \\textit{P. falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased. Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density. Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions. Vertebrate host population density is varied on a $\\log_{10}$ scale. All remaining parameters are given in Table 1 and Figure 3.'}
# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.

# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
# y = Temperature
# color = R0
# curves:
#   R0 = 1 contour (black curve)
#   Topt (red curve)

# Facets:
# Rows = levels of vertebrate host population density
# Columns = two MBPT systems
# Total = 6 plots

## Set up plot data frame
# We re-create the output data frame so that we can vary sigmaH correctly.
# We also drop the resolution of KH down to just three values
# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"

## Configure data frame for plotting
R0_df <- data.R0 %>%
  select(system_ID, system_label, Temperature, sigmaH, KH, median, mean) %>%
  rename(R0 = mean) %>%
  # Consider only 3 values of KH (on a log10-scale)
  filter(KH %in% c(.1, 1, 10)) %>%
  # Choose a limited range of sigmaH values
  filter(sigmaH < 10^2.275 | is.infinite(sigmaH)) %>%
  # Group by plotting variables
  group_by(system_ID, KH, sigmaH) %>%
  # Calculate Topt (which.max requires grouping)
  mutate(Topt = `Temperature`[which.max(R0)]) %>%
  as_tibble() %>%
  arrange(system_ID, sigmaH, Temperature)

## Add a "point at infinity" for sigmaH
# Value of sigmaH to replace 'Inf' with for plotting
infinite_skew <- 10^2.75

# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^2.4

R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 8)

Topt_for_R0_df <- data.Topt %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, KH, median) %>%
  mutate(sigmaH_proxy = sigmaH)
Topt_for_R0_df <- inf_skew_func(Topt_for_R0_df, infinite_skew, infinite_divide, 8)

## PLOTTING ##

## Options
# Define sigmaH tick breaks and labels
sigmaH_breaks_heatmap <- c(10^c(seq(-1, 2, by = 1)), infinite_divide, infinite_skew)
sigmaH_labels_heatmap <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

# Labels for facet rows
R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
mylabels <- as_labeller(c(
  `0.1` = "0.1 vertebrate hosts / ha",
  `1` = "1 vertebrate host / ha",
  `10` = "10 vertebrate hosts / ha"
))

R0_heatmap_labels <- as_labeller(c(
  "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti*  \nand  DENV",
  "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti*  \nand  ZIKV",
  "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand  DENV",
  "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae*  \nand  *P. falciparum*",
  "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
))

# Breaks used to decide fill for the heat map
fill_breaks <- c(1, seq(5, 20, by = 5), Inf)

# Define colors for heat map so that values of R0>1 go from yellow to red
my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))

## PLOT ##
R0_plot <- R0_df %>%
  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature)) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # R0 contours for FINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 contours for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
    mapping = aes(z = R0),
    breaks = fill_breaks
  ) +
  # R0 = 1 contour:
  geom_contour(aes(colour = "R0=1", z = R0), breaks = c(1), size = 1) +
  # Topt curve:
  geom_path(
    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)) %>% arrange(sigmaH_proxy),
    mapping = aes(
      x = sigmaH_proxy,
      y = median,
      colour = "Topt"
    ),
    lwd = 1,
    linetype = 1
  ) +
  # white lines breaking up finite/infinite sigmaH values
  geom_vline(
    aes(xintercept = 0.85 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.2 * infinite_divide),
    colour = "white",
    lwd = .8,
    show.legend = FALSE
  ) +
  # x-axis:
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    breaks = sigmaH_breaks_heatmap,
    labels = sigmaH_labels_heatmap,
    expand = c(0, 0)
  ) +
  # y-axis:
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0, 0),
    limits = c(16, 35),
    breaks = seq(10, 36, by = 2)
  ) +
  # color:
  scale_colour_manual(
    name = "",
    labels = c(
      "R0=1" = unname(TeX("$R_0=1$")),
      "Topt" = "Transmission\nthermal\noptimum",
      "VTTR" = "Mosquito\npopulation\nthermal\nniche"
    ),
    values = c("black", "purple", "grey"),
    guide = guide_legend(
      order = 1,
      keyheight = unit(2, "cm"),
      override.aes = list(size = 6)
    )
  ) +
  # fill:
  scale_fill_manual(
    name = TeX("$R_0$"),
    values = my.cols,
    guide = guide_colorsteps(
      order = 2,
      breaks = fill_breaks,
      barheight = unit(8, "cm")
    )
  ) +
  # faceting:
  facet_grid(
    rows = vars(KH),
    cols = vars(system_label),
    labeller = labeller(
      .rows = mylabels,
      .cols = R0_heatmap_labels
    ),
    # repeat.tick.labels = "left"
  ) +
  # theme options:
  theme_minimal_hgrid(10) +
  theme(
    axis.line = element_line(),
    legend.text = element_text(size = 10),
    legend.text.align = 0,
    strip.text.y = ggtext::element_markdown(
      size = 7,
      hjust = 0.5
    ),
    strip.text.x = ggtext::element_markdown(
      size = 7,
      hjust = 0
    ),
    panel.spacing = unit(2, "pt")
  )

# Plot it
R0_plot
```

```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density. The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp. and \\textit{P. falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased. Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density. Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions. Vertebrate host population density is varied on a $\\log_{10}$ scale. All remaining parameters are given in Table 1 and Figure 3.'}
Topt_df <- data.Topt %>%
  filter(KH < 10^4 + 1) %>%
  pivot_wider(
    id_cols = c("system_label", "Model", "sigmaH", "KH"),
    names_from = variable,
    values_from = c("mean", "median", "lowHCI", "highHCI")
  ) %>%
  rename(
    mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
    highHCI = highHCI_Topt
  ) %>%
  # Arrange along the plotting variables
  arrange(system_label, KH, median, sigmaH) %>%
  ungroup()

# PLOTTING
Topt_plot <- Topt_df %>%
  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
  ## Set up plot ##
  # color = sigmaH
  ggplot(aes(x = KH, colour = as.factor(sigmaH))) +
  # Topt curves:
  geom_path(aes(y = median), lwd = 1) +
  # x-axis: log10 scale, no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = c(10^c(seq(-1, 4, by = 1))),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0, 0),
    limits = c(21, 30.5),
    breaks = seq(21, 32, by = 1)
  ) +
  # color:
  scale_colour_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  scale_fill_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  # faceting:
  facet_wrap(~system_label, nrow = 2, labeller = labeller()) +
  # theme options:
  theme_minimal(10) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(Topt_plot)
```

```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} The thermal optima predicted by the model can be substantially different at low levels of biting tolerance. At low host population densities, there may be warmer (a, b, c, e) or cooler (d) thermal optima when biting tolerance is low compared to when it is high. Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions. Vertebrate host biting tolerance is varied on a $\\log_{10}$ scale with a break to indicate values of $\\mathcal{R}_0$ when biting tolerance is unlimited. '}
# x-axis = vertebrate host biting tolerance
# y-axis = thermal optimum
# color = vertebrate host population density

infinite_skew <- 10^3.7
# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^3.35 # 10^log10(max_sigmaH*1)

Topt_df <- data.Topt %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
                               sigmaH,
                               infinite_skew
  ))
Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)

sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15 * infinite_divide, infinite_skew)
sigmaH_labels <- c(TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$")), TeX("$\\ldots$"), TeX("$\\infty$"))

Topt_plot <- Topt_df %>%
  # Choose appropriate pop. dens. values and group
  filter(KH %in% 10^seq(0, 3)) %>%
  arrange(system_label, KH, sigmaH, median) %>%
  ## Set up plot ##
  # color = sigmaH
  ggplot(aes(x = sigmaH_proxy, colour = as.factor(KH))) +
  # Topt curves:
  geom_path(aes(y = median), lwd = 1) +
  # white lines breaking up finite/infinite sigmaH values:
  geom_vline(
    aes(xintercept = 1.05 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.15 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.25 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  # x-axis: Use a log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    # limits = c(0.5, 150),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # y-axis
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0, 0), # c(0.05, 0.05),
    limits = c(21, 30), # mean: 21-31, median: 21-32
    breaks = seq(21, 32, by = 1)
  ) +
  # color:
  scale_colour_manual(
    name = "Vertebrate host population\ndensity (ind/ha)",
    values = met.brewer("Hokusai3", 4)
  ) +
  scale_fill_manual(
    name = "Vertebrate host population\ndensity (ind/ha)",
    values = met.brewer("Hokusai3", 4)
  ) +
  # faceting:
  facet_wrap(~system_label,
             scales = "free",
             nrow = 2,
             labeller = labeller()
  ) +
  # theme options:
  theme_minimal(10) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(Topt_plot)
```

```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} The critical thermal minimum for parasite population persistence as a function of vertebrate host population density and biting tolerance. Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature. In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text). Shown here are the median values of the critical thermal minimum with respect to mosquito trait TPC hyperparameter posterior distributions. Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited. '}
#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = parasite critical thermal minimum (CTmin)
# Facets = systems

# add many proxy sigmaH points at infinity to make the values easier to see there
max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
# Value of sigmaH to replace 'Inf' with for plotting
infinite_skew <- 10^2.35
# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^2.7

# Define sigmaH tick breaks and labels
sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

CTmin_df <- data.CT %>%
  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
  pivot_wider(names_from = variable, values_from = median) %>% 
  # If CTwidth is essentially zero, set CTmin to Inf indicating R0 < 1
  mutate(CTmin = if_else(CTwidth < eps, Inf, CTmin)) %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, CTmin) %>%
  ungroup() %>%
  # Assign a value for cases where R0<1 for all temperatures
  mutate(CTmin = ifelse(is.finite(CTmin), CTmin, 100))

CTmin_df <- inf_skew_func(CTmin_df, infinite_skew, infinite_divide, 8)

maxCTmin <- ceiling(max(filter(CTmin_df, CTmin<100)$CTmin))

CTmin_breaks <- c(seq(14, 35, by = 2), 101)

CTmin_heat_plots <- CTmin_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmin)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmin_df,
      sigmaH_proxy < 10^2.2
    ),
    breaks = CTmin_breaks
  ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmin_df,
      sigmaH_proxy > 10^2.4,
      sigmaH_proxy < infinite_divide
    ),
    breaks = CTmin_breaks
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
  scale_fill_manual(
    name = "Critical thermal minimum (°C)",
    values = c(viridis(9), "grey", "grey"),
    labels = ~ ifelse(.x < maxCTmin, .x, "n/a")
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(CTmin_heat_plots)
```

```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} The critical thermal maximum for parasite population persistence as a function of vertebrate host population density and biting tolerance. Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature. In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text). Shown here are the median values of the critical thermal maximum with respect to mosquito trait TPC hyperparameter posterior distributions. Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited. '}
#   x    = biting tolerance (with a point at infinity)
#   y    = vertebrate host population density
# colour = parasite critical thermal maximum (CTmax)
# Facets = systems

# add many proxy sigmaH points at infinity to make the values easier to see there
max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
# Value of sigmaH to replace 'Inf' with for plotting
infinite_skew <- 10^2.35
# Used to create a gap dividing finite and infinite sigmaH
infinite_divide <- 10^2.7

# Define sigmaH tick breaks and labels
sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))

CTmax_df <- data.CT %>%
  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
  pivot_wider(names_from = variable, values_from = median) %>% 
  # If CTwidth is essentially zero, set CTmax to -Inf indicating R0 < 1
  mutate(CTmax = if_else(CTwidth < eps, Inf, CTmax)) %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, CTmax) %>%
  ungroup() %>%
  # Assign a value for cases where R0<1 for all temperatures
  mutate(CTmax = ifelse(is.finite(CTmax), CTmax, -100))

CTmax_df <- inf_skew_func(CTmax_df, infinite_skew, infinite_divide, 8)

minCTmax <- floor(min(filter(CTmax_df, CTmax>0)$CTmax))

CTmax_breaks <- c(-101, seq(21, 35, by = 2))

CTmax_heat_plots <- CTmax_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmax)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmax_df,
      sigmaH_proxy < 10^2.2
    ),
    breaks = CTmax_breaks
  ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmax_df,
      sigmaH_proxy > 10^2.4,
      sigmaH_proxy < infinite_divide
    ),
    breaks = CTmax_breaks
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
  scale_fill_manual(
    name = "Critical thermal maximum (°C)",
    values = c("grey", viridis(9)),
    labels = ~ ifelse(.x < minCTmax - 1, "n/a", .x)
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(CTmax_heat_plots)
```

```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} The critical thermal minimum ($\\textrm{CT}_{\\min}$, blue curves) and maximum ($\\textrm{CT}_{\\max}$, red curves) for parasite population persistence depend on vertebrate host availability, even when vertebrate hosts tolerate any level of mosquito biting (dotted curves). Transmission is sustained ($\\mathcal{R}_0$>1) in the regions enclosed by the red and blue curves. $\\textrm{CT}_{\\min}$ is a convex function of vertebrate host population density while $\\textrm{CT}_{\\max}$ is concave. The points where the red and blue curves touch indicate thresholds of vertebrate host population density beyond which parasite population persistence is no longer possible at any temperature (i.e. $\\mathcal{R}_0$(T)<1) (see Figure 6 in the main text). Shown here are the median values of the critical thermal minimum, maximum, and mosquito thermal tolerance niche with respect to mosquito trait TPC hyperparameter posterior distributions. Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited. All remaining parameters are given in Table 1 and Figure 2.'}
# x-axis = vertebrate host population density
# y-axis = Temperature
# linetype = biting tolerance
# colour = CT_min (blue), CT_max (red)

CTRange_df <- data.CT %>%
  # Arrange along the plotting variables
  select(system_label, sigmaH, KH, variable, value = median) %>%
  # Choose a few sigmaH values to plot, including Inf
  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
  filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 101)]) %>%
  pivot_wider(
    id_cols = c("system_label", "sigmaH", "KH"),
    names_from = variable, values_from = value
  ) %>%
  group_by(system_label, KH, sigmaH) %>%
  mutate(CTwidth = max(CTmax - CTmin, 0)) %>%
  filter(CTwidth > 0.05) %>%
  # Arrange along the plotting variables
  arrange(system_label, KH, sigmaH, CTmax, CTmin) %>%
  ungroup() %>%
  melt(id = c("system_label", "KH", "sigmaH")) %>%
  arrange(KH, sigmaH)

CTRange_plots <- CTRange_df %>%
  ## Set up plot ##
  # x-axis = population density, y-axis = temperature,
  # color = thermal extrema, linetype = sigmaH
  ggplot(
    aes(x = KH, y = value, linetype = as.factor(sigmaH), color = variable)
  ) +
  # Mosquito thermal tolerance range lines
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmin_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  geom_hline(
    data = MosqThermRange_df,
    aes(yintercept = CTmax_V0, colour = "VTTR"),
    lwd = 1.275
  ) +
  # Curves showing CTmin and CTmax
  geom_line(
    data = filter(CTRange_df, variable == "CTmin"),
    lwd = 1
  ) +
  geom_line(
    data = filter(CTRange_df, variable == "CTmax"),
    lwd = 1
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(1E-2, 1E5),
    breaks = 10^seq(-1, 4),
    labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: small buffer space
  scale_y_continuous(
    name = expression("Temperature "(degree * C)),
    expand = c(0.05, 0.05),
    limits = c(min(MosqThermRange_df$CTmin_V0), max(MosqThermRange_df$CTmax_V0)),
    breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
                 floor(range(CTRange_df$value, na.rm = TRUE)[2]),
                 by = 2
    )
  ) +
  # linetype:
  scale_linetype_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c("solid", "dashed", "longdash", "dotted"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  # color:
  scale_colour_manual(
    name = "Thermal extrema",
    breaks = c("CTmax", "CTmin", "VTTR"),
    labels = c("Critical maximum", "Critical minimum", "Mosquito population\nthermal niche"),
    values = c("red", "blue", "grey"),
    guide = guide_legend(keyheight = unit(40, "cm"))
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(
    color = guide_legend(override.aes = list(size = 4), order = 1),
    linetype = guide_legend(keywidth = 4, order = 2),
  ) +
  # theme options:
  theme_minimal_hgrid(10) +
  theme(
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0
    )
  )

# Plot
shift_legend(CTRange_plots)
```

```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}
# Estimating the difference between Topt and Topt_RM numerically using our previous data
Toptdiff_CCH <- data.Topt %>%
  ungroup() %>%
  select(system_ID, sigmaH, KH, median) %>%
  rename(Topt = median) %>%
  filter(is.finite(sigmaH)) %>%
  distinct()

Toptdiff_RM <- data.Topt %>%
  ungroup() %>%
  filter(is.infinite(sigmaH)) %>%
  select(system_ID, KH, median) %>%
  rename(Topt_RM = median) %>%
  distinct()

Toptdiff_df <- left_join(Toptdiff_CCH, Toptdiff_RM) %>%
  mutate(Toptdiff = Topt_RM - Topt) %>%
  mutate(absToptdiff = abs(Toptdiff)) %>%
  mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>%
  mutate(sigmaHKH = sigmaH * KH) %>%
  group_by(system_ID) %>%
  filter(absToptdiff == max(absToptdiff)) %>%
  select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>%
  distinct()

# Calculating Topt0 using the "simplified" equation
Topt0_df <- median.Vec %>%
  filter(V0 > 1) %>%
  mutate(muV = 1 / (lf + eps)) %>%
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(proxy_0 = lf * betaV * P_EIP / (KL * rhoL * (lf - 1 / (sigmaV_f * deltaL)))) %>%
  select(system_ID, Temperature, proxy_0) %>%
  group_by(system_ID)

Topt0_base_estimates <- Topt0_df %>%
  group_by(system_ID) %>%
  # Calculate Topt_0
  filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>%
  rename(Topt_0 = Temperature)

# Calculating Topt0 using the "simplified" equation
ToptRM_df <- median.Vec %>%
  mutate(muV = 1 / (lf + eps)) %>%
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>%
  select(system_ID, Temperature, proxy_RM) %>%
  group_by(system_ID)

ToptRM_base_estimates <- data.Topt %>%
  group_by(system_ID) %>%
  filter(is.infinite(sigmaH)) %>%
  select(system_ID, median) %>%
  rename(Topt_RM = median) %>%
  distinct()

Topt_estimates_median <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
  select(system_ID, Topt_RM, Topt_0) %>%
  mutate(Topt_diff = Topt_RM - Topt_0) %>%
  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)
```

```{r fig-S7_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum and maximum and thermal optimum vary across transmission systems and levels of vertebrate host availability. Distributions for the limited biting tolerance case (solid lines) and unlimited biting tolerance case (dashed lines) are shown above and below the vertebrate host population density levels, respectively. As vertebrate host population density is increased, the distributions become approximately equal, with the critical thermal minimum and maximum converging to each other at sufficiently high population densities. The \\textit{An. gambiae} and \\textit{P. falciparum} system shows the most drastic differences between the limited and unlimited biting tolerance cases at low vertebrate host population density levels. Vertebrate host population density is varied on a $\\log_{10}$ scale. '}
# half-violin plots
plot.densities_violin_inline <- ggplot() +
  # CT min
  geom_violinhalf(
    data = filter(
      all.density.df, variable == "Critical thermal minimum",
      sigmaH == 100
    ),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
    lwd = 0.75
  ) +
  geom_violinhalf(
    data = filter(
      all.density.df, variable == "Critical thermal minimum",
      sigmaH == Inf
    ),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
    lwd = 0.75,
    flip = TRUE
  ) +
  # CT max
  geom_violinhalf(
    data = filter(
      all.density.df, variable == "Critical thermal maximum",
      sigmaH == 100
    ),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
    lwd = 0.75
  ) +
  geom_violinhalf(
    data = filter(
      all.density.df, variable == "Critical thermal maximum",
      sigmaH == Inf
    ),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
    lwd = 0.75,
    flip = TRUE
  ) +
  # Thermal optima
  geom_violinhalf(
    data = filter(
      all.density.df, variable == "Thermal optimum",
      sigmaH == 100
    ),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
    lwd = 0.75
  ) +
  geom_violinhalf(
    data = filter(
      all.density.df, variable == "Thermal optimum",
      sigmaH == Inf
    ),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
    lwd = 0.75,
    flip = TRUE
  ) +
  scale_x_discrete(
    name = "Vertebrate host population density (ind/ha)"
  ) +
  scale_y_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0)
  ) +
  scale_linetype(
    name = "Biting tolerance\n(bites per host per day)"
  ) +
  scale_fill_discrete(
    name = "",
    breaks = c("CTmin", "Topt", "CTmax"),
    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
  ) +
  facet_wrap(~system_label, labeller = labeller(), scales = "free_x") +
  theme_minimal_grid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  ) +
  coord_flip()
shift_legend(plot.densities_violin_inline)
```

```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$. Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence. Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions. Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative. Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system. '}
KH_vals <- c(1, 100)

data.dR0dT <- data.dR0dvar %>%
  filter((KH %in% KH_vals & sigmaH == 10) | (KH == 100 & is.infinite(sigmaH)))

temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
  filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) %>%
  filter(!is.na(median_R0), median_R0 > eps) %>%
  group_by(system_ID) %>% 
  summarise(min_Temp = min(Temperature),
            max_Temp = max(Temperature))

val_lims <- tibble(sigmaH = unique(data.dR0dT$sigmaH), 
                   min_median = c(-90, -0.05), 
                   max_median = c(5, 0.5))

dR0dk.df <- data.dR0dT %>%
  filter(
    KH %in% KH_vals,
    sigmaH %in% unique(data.dR0dT$sigmaH)
  ) %>%
  right_join(select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
               filter(KH %in% KH_vals & sigmaH %in% unique(data.dR0dT$sigmaH))) %>%
  # Restrict to relevant temperatures (V0 and R0 > 0)
  right_join(temp_lims) %>% 
  group_by(system_ID) %>% 
  filter(Temperature > min_Temp, Temperature < max_Temp) %>% 
  filter(!is.na(median)) %>% 
  ungroup() %>% 
  # Restrict plotted values (so all plots are visible)
  right_join(val_lims) %>% 
  group_by(sigmaH) %>% 
  # filter(median > min_median, median < max_median) %>% 
  ungroup() %>% 
  # filter(median_R0 > 0) %>%
  mutate(abs_median = abs(median)) %>%
  # Normalize values to better tell which is most important
  mutate(sign_median = sign(median)) %>%
  group_by(system_ID, sigmaH, KH) %>%
  mutate(norm_median = ifelse(sign_median>0,
                              sign_median * median / max(median, na.rm = TRUE),
                              sign_median * median / min(median, na.rm = TRUE))) %>%
  filter(sign_median != 0, !is.na(sign_median)) %>%
  arrange(sign_median) %>%
  arrange(Temperature)

# # R0 derivative dataframe
# R0deriv_df <- data.R0 %>% 
#   group_by(system_ID, Model, sigmaH, KH) %>% 
#   arrange(system_ID, Model, sigmaH, KH, Temperature) %>%
#   mutate(deriv = (mean - lag(mean)) / (Temperature - lag(Temperature)))

# test_plot <- R0deriv_df %>% 
#   filter(KH %in% c(1), sigmaH %in% c(100, Inf), median > 0) %>% 
#   ggplot(aes(x = Temperature, y = deriv)) +
#   geom_line() +
#   geom_hline(yintercept = 0) +
#   facet_rep_grid(
#     rows = vars(KH, sigmaH),
#     cols = vars(system_label),
#     labeller = labeller(
#       system_label = sens_labels,
#       sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
#       KH = as_labeller(appender_KH, default = label_parsed)
#     ),
#     scales = "free"
#   ) 
# test_plot

# NB: in order to produce an R0 TPC, overall derivative should go from positive to negative
plot.dR0dk <- dR0dk.df %>%
  # filter(focal_var %in% c("Overall")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = norm_median, color = focal_var, 
             # linetype = (as.factor(sign_median))
  )) +
  geom_line(lwd = 0.5) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c(c4a("misc.okabe", 7), "black"))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Normalized local sensitivity of $\\,R_0$ to temperature")),
    # limits = c(-1, 1),
    # limits = 10^c(-4, 4),
    # breaks = 10^(seq(-4, 4)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  # scale_linetype_manual(
  #   name = "Sign of sensitivity:",
  #   values = c(1, 3),
  #   breaks = c(1, -1),
  #   labels = c("Positive", "Negative")
  # ) +
  facet_rep_grid(
    rows = vars(KH, sigmaH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.dR0dk
```

```{r fig-S8_3_dR0dvar_comparison, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$. Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence. Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions. Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative. Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system. '}

comp_dR0dk.df <- dR0dk.df %>%
  # filter(sigmaH == 10) %>% 
  filter(focal_var != "Overall") %>% 
  group_by(system_ID, Temperature, sigmaH, KH) %>% 
  mutate(abs_median = abs(median),
         total_sens = sum(abs_median),
         prop_sens = abs_median / total_sens) %>% 
  arrange(system_label, Temperature, KH, sigmaH, focal_var) #%>% 
# filter(focal_var %in% c("Parasite development rate", "Biting frequency"))
# # mutate(median = abs(median)) %>% 
# select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
# pivot_wider(names_from = KH, values_from = prop_sens) %>% 
# mutate(sens_comp = ifelse(`10` == 0 & `1` == 0,
#                           0,
#                           (`10` - `1`) / ((`10` + `1`)/2)))
# mutate(sens_comp = (`10` - `1`) / `1`)

plot.comp_dR0dk <- comp_dR0dk.df %>%
  # filter(focal_var %in% c("Overall")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = prop_sens, fill = focal_var, color = focal_var,
             # linetype = (as.factor(sign_median))
  )) +
  # geom_area() +
  geom_line(lwd = 1) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Contributions to overall local sensitivity of $\\,R_0$")),
    # limits = c(-100, 100),
    # limits = c(-0.2, 0.1),
    # limits = 10^c(-4, 4),
    # breaks = 10^(seq(-4, 4)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  # scale_linetype_manual(
  #   name = "Sign of sensitivity:",
  #   values = c(1, 3),
  #   breaks = c(1, -1),
  #   labels = c("Positive", "Negative")
  # ) +
  facet_rep_grid(
    rows = vars(sigmaH, KH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.comp_dR0dk
```

```{r fig-S8_4_dR0dvar_compzoom, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$. Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence. Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions. Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative. Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system. '}

compzoom_dR0dk.df <- comp_dR0dk.df %>%
  filter(sigmaH == 10) %>% 
  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
  pivot_wider(names_from = KH, values_from = prop_sens) %>%
  mutate(abs_comp = abs(`1`) - abs(`100`))

plot.compzoom_dR0dk <- compzoom_dR0dk.df %>% 
  # filter(focal_var %in% c("Parasite development rate", "Adult mortality rate", "Biting frequency")) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var,
             # linetype = (as.factor(sign_median))
  )) +
  # geom_area() +
  # geom_smooth(se = FALSE) +
  geom_line(lwd = 1) +
  geom_hline(yintercept = 0, lwd = 0.25) +
  scale_color_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 10$ ")),
    # limits = c(-100, 100),
    # limits = c(-0.2, 0.1),
    # limits = 10^c(-4, 4),
    # breaks = 10^(seq(-4, 4)),
    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
    # trans = "log10",
    expand = c(0, 0)
  ) +
  # scale_linetype_manual(
  #   name = "Sign of sensitivity:",
  #   values = c(1, 3),
  #   breaks = c(1, -1),
  #   labels = c("Positive", "Negative")
  # ) +
  facet_rep_grid(
    rows = vars(sigmaH),
    cols = vars(system_label),
    labeller = labeller(
      system_label = sens_labels,
      # sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
      # KH = as_labeller(appender_KH, default = label_parsed)
    ),
    scales = "free"
  ) +
  guides(linetype = guide_legend(
    title.position = "left",
    title.vjust = 0.5,
    direction = "vertical"
  )) +
  theme_minimal_hgrid(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 8),
    legend.position = "bottom",
    legend.justification = 0.5,
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.compzoom_dR0dk
```

```{r fig-S8_R0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc}  The uncertainty of $\\mathcal{R}_0$ to mosquito traits across temperatures as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$ when vertebrate host population density is set to one individual per hectare. Temperatures are restricted to those at which $\\mathcal{R}_0$ is positive for the given system. At the cool end of the thermal niche, variation in $\\mathcal{R}_0$ is mostly driven by the probability of surviving the extrinsic incubation period, except in the case of (d) \\textit{An. gambiae} and \\textit{P. falciparum}. As temperature is increased, the influence of adult mosquito lifespan also increases to eventually become the most influential parameter for all systems except (e) \\textit{Cx. quinquefasciatus} and WNV.'}
Temp_range_for_plot <- R0.HPD %>%
  ungroup() %>%
  dplyr::filter(rel_HPD_width > eps) %>%
  dplyr::select(Temperature) %>%
  range()

plot.R0.rel.sens <- R0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # For each KH value, sum up all uncertainty values to get total uncertainty across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each uncertainty value by the total uncertainty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.R0.rel.sens
```

```{r fig-S9_ddTR0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_unc} The uncertainty in the sensitivity of $\\mathcal{R}_0$ with respect to temperature.'}
## Plot R0 uncertainty
Temp_range_for_plot <- ddTR0.HPD %>%
  ungroup() %>%
  dplyr::filter(HPD_width > eps) %>%
  select(Temperature) %>%
  range()

plot.ddTR0.rel.sens <- ddTR0.HPD %>%
  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
  # For each KH value, sum up all uncertainty values to get total uncertainty across parameters
  group_by(system_ID, sigmaH, KH, Temperature) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each uncertainty value by the total uncertainty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  arrange(sens_rel) %>%
  arrange(focal_var) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $dR_0 / dT$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    ),
    scales = "free"
  ) +
  theme_minimal(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

plot.ddTR0.rel.sens
```

```{r fig-S10_Topt_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc} The uncertainty of $T_{\\textrm{opt}}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width when $\\sigma_H$ is 100 bites per vertebrate host per day. At high levels of vertebrate host population density, the effect of vertebrate host traits diminishes and the relative sensitivities of $T_{\\textrm{opt}}$ to mosquito traits stabilize. Generally, adult lifespan is an influential parameter and, to lesser extents, vector competence and the probability of surviving the extrinsic incubation period (EIP). Eggs per female per day tends to be most important when vertebrate host population density is low, though this not the case for (e) \\textit{Cx. quinquefasciatus} and WNV.Immature development rate and the probability of immature survival are never very influential parameters. Vertebrate host population density is varied on a $\\log_{10}$ scale. '}
plot.Topt.rel.sens <- Topt.HPD %>%
  ungroup() %>%
  distinct() %>%
  filter(sigmaH == 100) %>%
  filter(!is.na(HPD_width)) %>%
  pathosystem_labeller() %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all uncertainty values to get total uncertainty
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each uncertainty value by the total uncertainty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E3),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $T_{opt}$ HPD width"))
  ) +
  facet_wrap(~system_label) +
  theme_minimal(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.Topt.rel.sens)
```

```{r fig-S10_2_dToptdKH_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc2} The uncertainty in the sensitivity of the thermal optimum to host availability as a function of vertebrate host population density when $\\sigma_H = 100$.'}
dToptdKH.HPD <- dToptdKH.HPD %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all uncertainty values to get total uncertainty
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each uncertainty value by the total uncertainty
  mutate(sens_rel = rel_HPD_width / sens_total)

plot.dToptdKH.rel.sens <- dToptdKH.HPD %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $ dT_{opt}/dK_H$ HPD width"))
  ) +
  facet_wrap(~system_label) +
  theme_minimal(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.dToptdKH.rel.sens)
```

```{r fig-S11_CTmin_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_unc} The uncertainty of $\\textrm{CT}_{\\min}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$. Sensitivities are only plotted when $\\textrm{CT}_{\\min}$ exists for the given value of vertebrate host population density. Generally, eggs per female per day and the probability of surviving the EIP are the most influential parameters. $\\textrm{CT}_{\\min}$ is sensitive to vector competence across the full range of vertebrate host population densities for systems (b) and (e) but, in systems (a), (c), and (d), only when population density is high. Immature development rate and the probability of immature survival are not very influential parameters and $\\textrm{CT}_{\\min}$ is only sensitive to biting frequency in the case of system (e) when vertebrate host population density is high. Vertebrate host population density is varied on a $\\log_{10}$ scale. '}
CTmin_df <- CT.HPD %>%
  filter(variable == "CTmin") %>%
  filter(sigmaH %in% c(100, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all uncertainty values to get total uncertainty
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each uncertainty value by the total uncertainty
  mutate(sens_rel = rel_HPD_width / sens_total) # %>%

# Make a stacked plot, colored by parameter
plot.CTmin.rel.sens <- CTmin_df %>%
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    )
  ) +
  theme_minimal(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 8,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmin.rel.sens
```

```{r fig-S12_CTmax_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax_unc} The uncertainty of $\\textrm{CT}_{\\max}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$. Sensitivities are only plotted when $\\textrm{CT}_{\\max}$ exists for the given value of vertebrate host population density. Generally, adult mosquito life span is the most influential parameter. At low vertebrate host population densities, $\\textrm{CT}_{\\max}$ is sensitive to eggs per female per day in systems (c) and (e). $\\textrm{CT}_{\\max}$ is only sensitive to biting frequency in the case of system (e) when vertebrate host population density is high. The influence of other parameters increases at high levels of vertebrate host population density. Vertebrate host population density is varied on a $\\log_{10}$ scale. '}
plot.CTmax.rel.sens <- CT.HPD %>%
  filter(variable == "CTmax") %>%
  filter(sigmaH %in% c(100, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all uncertainty values to get total uncertainty
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each uncertainty value by the total uncertainty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
    )
  ) +
  theme_minimal(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 8,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTmax.rel.sens
```

```{r fig-S13_CTwidth_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTwidth_unc}  The uncertainty of $\\textrm{CT}_{\\textrm{width}}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$. Sensitivities are only plotted when $\\textrm{CT}_{\\textrm{width}}$exists for the given value of vertebrate host population density. Generally, adult mosquito life span, eggs per female per day, and the probability of surviving the EIP are the most influential parameters, though $\\textrm{CT}_{\\textrm{width}}$ is not sensitive the probability of surviving the EIP in system (d). $\\textrm{CT}_{\\textrm{width}}$ is only sensitive to biting frequency in the case of system (e) when vertebrate host population density is high. Vertebrate host population density is varied on a $\\log_{10}$ scale. '}
plot.CTwidth.rel.sens <- CT.HPD %>%
  filter(variable == "CTwidth") %>%
  filter(sigmaH %in% c(100, Inf)) %>%
  filter(!is.na(rel_HPD_width)) %>%
  # For each KH value, sum up all uncertainty values to get total uncertainty
  group_by(system_ID, sigmaH, KH) %>%
  mutate(sens_total = sum(rel_HPD_width)) %>%
  # Divide each uncertainty value by the total sensitiviWty
  mutate(sens_rel = rel_HPD_width / sens_total) %>%
  # Make a stacked plot, colored by parameter
  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
  geom_area() +
  scale_fill_manual(
    name = "Focal trait:",
    values = rev(c4a("misc.okabe", 7))
  ) +
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    breaks = 10^seq(-2, 4, 1),
    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  scale_y_continuous(
    name = unname(TeX("Relative contribution to $CT_{width}$ HPD width"))
  ) +
  facet_grid(
    cols = vars(system_label),
    rows = vars(sigmaH),
    labeller = labeller(
      system_label = sens_labels,
      sigmaH = as_labeller(
        appender_sigmaH,
        default = label_parsed
      )
    )
  ) +
  theme_minimal(10) +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    axis.title.x = element_text(hjust = 0.5),
    strip.text.x = ggtext::element_markdown(
      size = 8,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    ),
    panel.spacing.x = unit(2, "lines")
  )
plot.CTwidth.rel.sens
```

### 2023-12-11 code/Mordecai_2017/Aedes_prior_fits.R

@@ -1,0 +1,598 @@
+# Fitting models to the prior data
+
+# Load saved versions to save time
+# load("aedes_prior_samps.Rsave")
+# load("aedes_prior_gamma_fits.Rsave")
+
+## Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+library('MASS')
+library('here')
+
+setwd("C:/Users/kd99491/Documents/GitHub/thermal-properties-mbps/code/Mordecai2017")
+
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives.
+source("temp_functions_all.R")  
+
+# Creating a small constant to keep denominators from being zero.
+ec<-0.000001 
+
+## Loading the data; my data will be called aegyptiDENVmodelTempData.csv 
+data.all <- read.csv("Aedes_prior_data.csv", header=TRUE)
+
+## Load the default priors
+priors1<-list()
+priors1$names<-c( "T0", "Tm", "c","tau")
+priors1$fun<-c( "uniform", "uniform", "gamma","gamma")
+priors1$hyper<-matrix(NA, ncol=4, nrow=3)
+priors1$hyper[,1]<-c(0, 24, NA)
+priors1$hyper[,2]<-c(25, 45, NA)
+priors1$hyper[,3]<-c(1, 10, NA)
+priors1$hyper[,4]<-c(0.0001, 0.0001, NA)
+
+# Specifing the parameters that control the MCMC (these will be used throughout the code). 
+
+n.chains <- 5
+n.adapt <- 5000
+n.samps <- 5000
+
+
+######################################
+## The first trait the biting rate, a.
+
+data <- data.all[ which(data.all$trait.name=="a"),]
+
+# Plot the data to see which fucntion, Briere or Quadratic, is a more suitable fit for 
+# the data.
+
+plot(trait ~ T, data = data)
+points(trait ~ T, data = subset(data, ref=="Callado (2002)"), col=2, pch=16)
+
+
+# Given the data we've chosen to use the Briere fucntion. Jag-briere.bug contains the 
+# specifics of the Briere model with the default priors, which is then used to create 
+# an MCMC sample using the data.
+
+jags <- jags.model('jags-briere.bug',
+                   data = list('Y' = data$trait, 'T' = data$T, 'N'= length(data$T)),
[…]

### 2023-12-11 code/Mordecai_2017/Aegypti_DENV_R0_Sensitivity.R

@@ -1,0 +1,188 @@
+### This file will take resulting analysis from the Aegypti DENV model and run 
+### through a bit of sensitvity analysis. 
+
+# Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+setwd("code/Mordecai2017/")
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives
+source("temp_functions_all.R") 
+
+## Loading in samples from the Rsave (DENV_ParameterFits.Rsave), which have the samples
+## for a, b, c, MDR, EFD, e2a, and PDR created in the DENV_IndividualParameterFitCode.R.
+
+# load("Aegypti_DENV_ParameterFits_2016-03-30.Rsave")
+load("Informative_Aegypti_DENV_ParameterFits_2016-03-30.Rsave")
+
+# load("LifespanFits_2016-03-30.Rsave")
+load("LifespanFits_2016-03-30-informative.Rsave")
+lf.samps <- lf.DENV.samps
+
+## Load the outputs from Aegypti_DENV_R0_Analysis.R
+# load("Aegypti_DENV_model_outputs-uninformative.Rsave")
+# load("Aegypti_DENV_trait_means_uninformative.Rsave")
+load("Aegypti_DENV_model_outputs-informative.Rsave")
+load("Aegypti_DENV_trait_means_informative.Rsave")
+
+## Load previously calculated and saved derivatives to save time
+# load("aegy_derivative_outputs-uninformative.Rsave")
+# load("aegy_derivative_outputs-informative.Rsave")
+
+## Next we set up the temperatures over which we will be evaluating
+## R0, etc, as well as the thinning interval for the samples.
+
[…]

### 2023-12-11 code/Mordecai_2017/Aegypti_IndividualParameterFitCode.R

@@ -1,0 +1,504 @@
+### This file will process the temperature data and create the individual parameter 
+### samples for all the traits that are included in the DENV R0 model. 
+
+setwd("C:/Users/kd99491/Documents/GitHub/thermal-properties-mbps/code/Mordecai2017")
+## Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions
+source("temp_functions_all.R") 
+
+# Creating a small constant to keep denominators from being zero.
+ec<-0.000001 
+
+## Loading the data; my data will be called aegyptiDENVmodelTempData.csv 
+data.all <- read.csv("aegyptiDENVmodelTempData_2016-03-30.csv", header=TRUE)
+
+# Exclude the Focks & Barrera 2006 data because they're from a model
+data.all = subset(data.all, ref!=as.character("Focks_Barrera_2006_Research&TrainingTropicalDis_Geneva_Paper"))
+
+## Now the code will choose all the temperature sensitive traits and fit either a
+## Briere or Quadratic model to it using MCMC sampling.
+# Specifing the parameters that control the MCMC (these will be used throughout the code). 
+
+n.chains <- 5
+n.adapt <- 5000
+n.samps <- 5000
+
+######################################
+## The first trait the biting rate, a.
+
+data <- data.all[ which(data.all$trait.name=="GCR"),]
+
+# Plot the data to see which fucntion, Briere or Quadratic, is a more suitable fit for 
+# the data.
+
+plot(trait ~ T, data = data)
+
+# Given the data we've chosen to use the Briere fucntion. Jag-briere.bug contains the 
+# specifics of the Briere model with the default priors, which is then used to create 
+# an MCMC sample using the data.
+
+jags <- jags.model('jags-briere.bug',
+                   data = list('Y' = data$trait, 'T' = data$T, 'N'= length(data$T)),
+                   n.chains = n.chains, inits = list(Tm = 31, T0 = 5, c = 0.00007),
+                   n.adapt = n.adapt)
+
+# The coda.samples() function takes n.samps new samples, and saves
[…]

### 2023-12-11 code/Mordecai_2017/Aegypti_R0_bc_EIP_Sensitivity.R

@@ -1,0 +1,291 @@
+# Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+
+####
+# Load previous model runs to save time
+# load("aegy_model_outputs-sensitivity.Rsave")
+
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives
+source("temp_functions_all.R") 
+
+## Loading in samples from the Rsave (DENV_ParameterFits.Rsave), which have the samples
+## for a, b, c, MDR, EFD, e2a, and PDR created in the DENV_IndividualParameterFitCode.R.
+
+# load("Aegypti_DENV_ParameterFits_2016-03-30.Rsave")
+load("Informative_Aegypti_DENV_ParameterFits_2016-03-30.Rsave")
+
+# load("LifespanFits_2016-03-30.Rsave")
+load("LifespanFits_2016-03-30-informative.Rsave")
+lf.samps <- lf.DENV.samps
+
+## Load the outputs from Aegypti_DENV_R0_Analysis.R
+# load("Aegypti_DENV_model_outputs-uninformative.Rsave")
+# load("Aegypti_DENV_trait_means_uninformative.Rsave")
+load("Aegypti_DENV_model_outputs-informative.Rsave")
+load("Aegypti_DENV_trait_means_informative.Rsave")
+
+
+## Next we set up the temperatures over which we will be evaluating
+## R0, etc, as well as the thinning interval for the samples.
+
+temp = seq(5,45,by=0.1)  ###temperature sequence
+t<-length(temp)
+
+n = dim(a.samps)[1]      ### length of samples
+
+thinned<-seq(1, n, by=5)### thinned samples
+
+lthin<-length(thinned)  ### number of of thinned samples
+
+ec<-0.000001            ### small constant used to keep denominators
+### from being numerically zero
+
[…]

### 2023-12-11 code/Mordecai_2017/Albopictus_IndividualParameterFitCode.R

@@ -1,0 +1,478 @@
+### This file will process the temperature data and create the individual parameter 
+### samples for all the traits that are included in the Aedes albopictus R0 model. 
+
+### This code fits models using UNINFORMATIVE priors
+
+## Remember to set your working directory so the code can access the data and 
+## necessary supplementary code.
+
+## Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives
+source("temp_functions_all.R") 
+
+# Creating a small constant to keep denominators from being zero.
+ec<-0.000001 
+
+# Specifing the parameters that control the MCMC (these will be used throughout the code). 
+
+n.chains <- 5
+n.adapt <- 5000
+n.samps <- 5000
+
+## Loading the data; my data will be called albopictusCHIKVmodelTempData.csv 
+data.all <- read.csv("albopictusCHIKVmodelTempData_2016-03-26.csv", header=TRUE)
+
+## Now the code will choose all the temperature sensitive traits and fit either a
+## Briere or Quadratic model to it using MCMC sampling.
+
+################################
+## The first trait the biting rate, a.
+
+# This chooses the trait, GCD, which is used to model the biting rate, a.
+
+data <- data.all[which(data.all$trait.name=="GCD"),]
+
+# Transforming the GCD into a, the biting rate
+
+data$trait = (1/(data$trait))
+
+# Plot the data to see which fucntion, Briere or Quadratic, is a more suitable fit for 
+# the data.
+par(mfrow=c(1,1))
+plot(trait ~ T, data = data)
+
+# Given the data we've chosen to use the Briere fucntion. Jag-briere.bug contains the 
+# specifics of the Briere model with the default priors, which is then used to create 
+# an MCMC sample using the data.
+
+jags <- jags.model('jags-briere.bug',
+                    data = list('Y' = data$trait, 'T' = data$T, 'N'= length(data$T)),
+                    n.chains = n.chains, inits = list(Tm = 31, T0 = 5, c = 0.00007),
[…]

### 2023-12-11 code/Mordecai_2017/Albopictus_R0_Analysis.R

@@ -1,0 +1,217 @@
+### This file will take the individual parameter samples for all the traits and use
+### them to build the CHIKV R0 model. 
+
+# Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+setwd("code/Mordecai2017/")
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives
+source("temp_functions_all.R") 
+
+## Loading in samples from the Rsave (CHIKV_ParameterFits.Rsave), which have the samples
+## for a, b, c, MDR, TFD, e2a created in the CHIKV_IndividualParameterFitCode.R
+# load("Albopictus_ParameterFits_2016-03-30.Rsave")
+load("Informative_Albopictus_ParameterFits_2016-03-30.Rsave")
+
+# load("LifespanFits_2016-03-30.Rsave")
+load("LifespanFits_2016-03-30-informative.Rsave")
+lf.samps <- lf.CHIKV.samps
+
+
+## Load previously computed and saved model outputs to save time
+# load("Albopictus_model_outputs-uninformative.Rsave")
+load("Albopictus_model_outputs-informative.Rsave")
+
+# Temperature sequence
+temp = seq(5,45,by=0.1)  
+t<-length(temp)
+
+# Length of samples, assuming they're all the same length
+n = dim(a.samps)[1]
+# n.mu = dim(mu.samps)[1]
+
+# Thinned samples
+thinned<-seq(1, n, by = 5) 
+lthin = length(thinned)
+
+# Creating a small constant to keep denominators from being zero.
+ec<-0.000001           
+
+## Creating the function encoding the value of R0 as a function of the parameters
[…]

### 2023-12-11 code/Mordecai_2017/Informative_Aegypti_IndividualParameterFitCode.R

@@ -1,0 +1,579 @@
+# Fit DENV models with informative priors
+
+setwd("code/Mordecai_2017")
+load("aedes_prior_gamma_fits.Rsave")
+
+# Refit everything using informative priors in modified BUGS functions
+
+### This file will process the temperature data and create the individual parameter 
+### samples for all the traits that are included in the DENV R0 model. 
+
+## Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives
+source("temp_functions_all.R") 
+
+# Creating a small constant to keep denominators from being zero.
+ec<-0.000001 
+
+## Loading the data; my data will be called aegyptiDENVmodelTempData.csv
+
+data.all <- read.csv("F:/GitHub/thermal-properties-mbps/data/raw/Mordecai_2017/aegyptiDENVmodelTempData_2016-03-30.csv", header=TRUE)
+
+# Exclude the Focks & Barrera 2006 data because they're from a model
+data.all = subset(data.all, ref!=as.character("Focks_Barrera_2006_Research&TrainingTropicalDis_Geneva_Paper"))
+
+## Now the code will choose all the temperature sensitive traits and fit either a
+## Briere or Quadratic model to it using MCMC sampling.
+
+# Specifing the parameters that control the MCMC (these will be used throughout the code). 
+
+n.chains <- 5
+n.adapt <- 5000
+n.samps <- 5000
+
+
+######################################
+## The first trait the biting rate, a.
+
+data <- data.all[ which(data.all$trait.name=="GCR"),]
+
+# Plot the data to see which fucntion, Briere or Quadratic, is a more suitable fit for 
+# the data.
+
+plot(trait ~ T, data = data)
+
+hypers = gamma.fits.a*0.1
+
+
+# Given the data we've chosen to use the Briere fucntion. Jag-briere.bug contains the 
+# specifics of the Briere model with the default priors, which is then used to create 
+# an MCMC sample using the data.
+
+jags <- jags.model('jags-briere-informative.bug',
[…]

### 2023-12-11 code/Mordecai_2017/Informative_Albopictus_IndividualParameterFitCode.R

@@ -1,0 +1,552 @@
+# Fit CHIKV models with informative priors
+
+load("code/Mordecai2017/aedes_prior_gamma_fits.Rsave")
+
+## Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+
+# This file contains tools for analysis and visualization.
+source("code/Mordecai2017/mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives
+source("code/Mordecai2017/temp_functions_all.R") 
+
+
+# Creating a small constant to keep denominators from being zero.
+ec<-0.000001 
+
+# Specifing the parameters that control the MCMC (these will be used throughout the code). 
+
+n.chains <- 5
+n.adapt <- 5000
+n.samps <- 5000
+
+## Loading the data; my data will be called albopictusCHIKVmodelTempData.csv 
+data.all <- read.csv("code/Mordecai2017/albopictusCHIKVmodelTempData_2016-03-26.csv", header=TRUE)
+
+## Now the code will choose all the temperature sensitive traits and fit either a
+## Briere or Quadratic model to it using MCMC sampling.
+
+################################
+## The first trait the biting rate, a.
+
+# This chooses the trait, GCD, which is used to model the biting rate, a.
+
+data <- data.all[which(data.all$trait.name=="GCD"),]
+
+# Transforming the GCD into a, the biting rate
+
+data$trait = (1/(data$trait))
+
+# Plot the data to see which fucntion, Briere or Quadratic, is a more suitable fit for 
+# the data.
+par(mfrow=c(1,1))
+plot(trait ~ T, data = data)
+
+hypers = gamma.fits.a*0.1
+
+# Given the data we've chosen to use the Briere fucntion. Jag-briere.bug contains the 
+# specifics of the Briere model with the default priors, which is then used to create 
+# an MCMC sample using the data.
+
+jags <- jags.model('code/Mordecai2017/jags-briere-informative.bug',
+                   data = list('Y' = data$trait, 'T' = data$T, 'N'= length(data$T), 'hypers' = hypers),
+                   n.chains = n.chains, inits = list(Tm = 31, T0 = 5, c = 0.00007),
+                   n.adapt = n.adapt)
+
[…]

### 2023-12-11 code/Mordecai_2017/R0_plotting.R

@@ -1,0 +1,942 @@
+# Loading the required packages and supplementary code for sampling and analysis.
+library(IDPmisc)
+library('rjags')
+library(RColorBrewer)
+
+# This file contains tools for analysis and visualization.
+source("mcmc_utils_all.R") 
+
+# This file contains the thermal response functions and their derivatives
+source("temp_functions_all.R") 
+
+# Temperature sequence
+temp = seq(5,45,by=0.1)  
+t<-length(temp)
+
+
+## Loading in samples from the Rsave (CHIKV_ParameterFits.Rsave), which have the samples
+## for a, b, c, MDR, TFD, e2a created in the CHIKV_IndividualParameterFitCode.R
+# load("Albopictus_ParameterFits_2016-03-30.Rsave")
+load("Informative_Albopictus_ParameterFits_2016-03-30.Rsave")
+
+# load("LifespanFits_2016-03-30.Rsave")
+load("LifespanFits_2016-03-30-informative.Rsave")
+lf.samps <- lf.CHIKV.samps
+
+# Length of samples, assuming they're all the same length
+n = dim(a.samps)[1]
+# n.mu = dim(mu.samps)[1]
+
+# Thinned samples
+thinned<-seq(1, n, by = 5) 
+lthin = length(thinned)
+
+# Creating a small constant to keep denominators from being zero.
+ec<-0.000001           
+
+### Albopictus R0 model plotting and validation
+# load("Albopictus_model_outputs-uninformative.Rsave")
+load("Albopictus_model_outputs-informative.Rsave")
+
+albo.R0 = R0
+albo.R0.M = R0.M
+a.M.albo = a.M
+b.M.albo = b.M
+c.M.albo = c.M
+MDR.M.albo = MDR.M
+e2a.M.albo = e2a.M
+PDR.M.albo = PDR.M
+TFD.M.albo = TFD.M
+lf.M.albo = lf.M
+a.albo = a
+b.albo = b
+c.albo = c
+MDR.albo = MDR
+e2a.albo = e2a
+PDR.albo = PDR
+TFD.albo = TFD
+lf.albo = lf
+a.samps.albo = a.samps
+TFD.samps.albo = TFD.samps
[…]

### 2023-12-11 code/Mordecai_2017/lifespan-comp-script-informative.R

@@ -1,0 +1,211 @@
+## Load relevant packages and materials
+library(IDPmisc)
+library('rjags')
+library(tidyverse)
+
+# This file contains tools for analysis and visualization.
+source("code/Mordecai_2017/mcmc_utils_all.R")
+
+# This file contains the thermal response functions and their derivatives.
+source("code/Mordecai_2017/temp_functions_all.R")
+## Load data for first model fit
+data.all <- read.csv("data/raw/Mordecai_2017/aegyptiDENVmodelTempData_2016-03-30.csv", header=TRUE)
+
+load("code/Mordecai_2017/aedes_prior_gamma_fits.Rsave")
+
+## Specify the MCMC Input Parameters
+n.chains <- 5
+n.adapt<-5000
+n.samps<-5000
+
+## Choose the response variable
+## The Rohani data have unrealistically long lifespans; omit them
+# data.p <- data.all[which(data.all$trait.name=="p"),]
+data.days <- data.all[which(data.all$trait.name=="p/days"),]
+data.1mu <- data.all[which(data.all$trait.name=="1/mu"),]
+
+# Convert Yang data to lifespan
+data.days$trait <- 1/data.days$trait
+
+
+## Manipulating the survival data so we can examine it as mu 
+ec <- 0.000001
+
+
+## Rohani et al. 2009 data were the proportion surviving for 31, 27, 23 days at 26, 28, and 30C, respectively
+## Convert to mortality
+# data.p$trait = -log(data.p$trait)/rep(c(31,27,23),2)
+# data.p$trait <- 1/data.p$trait
+data <- rbind(data.days, data.1mu) #data.p,   
+
+plot(trait ~ T, data = data)
+points(trait ~ T, data = subset(data, trait.name=="p/days"), col=2, pch=16)
+points(trait ~ T, data = subset(data, trait.name=="1/mu"), col=3, pch=16)
+
+hypers = gamma.fits.lf*0.01
+
+## Set up the jags code, which contains the specifics of the quadratic model with the
+## default priors. As well as a few different jags models that contain different things.
+
+jags <- jags.model('code/Mordecai2017/jags-quad-neg-informative.bug',
+                   data = list('Y' = data$trait, 'T' = data$T, 'N'=length(data$T), 'hypers' = hypers),
+                   n.chains = n.chains,
[…]

### 2023-12-11 code/Mordecai_2017/mcmc_utils_all.R

@@ -1,0 +1,267 @@
+## This file contains utility functions for manipulating mcmc samps,
+## and calculating/plotting predictions
+
+library(IDPmisc)
+library('rjags')
+
+## first some functions to put the mcmc samples into a properly
+## labeled data frame, depending on the functional form
+
+# Added by Daniel W, for the linear, columns = inter, slope, sigma
+make.linear.samps<-function(coda.samps, nchains=2, samp.lims=c(151, 5000), sig=TRUE){
+  n.inter<-slope<-sigma<-NULL
+  l1<-samp.lims[1]
+  l2<-samp.lims[2]
+  for(i in 1:nchains){
+    n.inter<-c(n.inter, coda.samps[[i]][l1:l2,3])
+    slope<-c(slope, coda.samps[[i]][l1:l2,1])
+    if(sig) sigma<-c(sigma, coda.samps[[i]][l1:l2,2])
+  }
+  if(sig){
+    samps<-data.frame(matrix(c(n.inter, slope, sigma), ncol=3, byrow=FALSE))
+    names(samps)<-c("n.inter", "slope", "sigma")
+  }
+  else{
+    samps<-data.frame(matrix(c(n.inter, slope), ncol=2, byrow=FALSE))
+    names(samps)<-c("n.inter", "slope", "sigma")
+    
+  }
+  return(samps)
+}
+
+make.nlinear.samps<-function(coda.samps, nchains=2, samp.lims=c(151, 5000), sig=TRUE){
+  inter<-n.slope<-sigma<-NULL
+  l1<-samp.lims[1]
+  l2<-samp.lims[2]
+  for(i in 1:nchains){
+    inter<-c(inter, coda.samps[[i]][l1:l2,1])
+    n.slope<-c(n.slope, coda.samps[[i]][l1:l2,2])
+    if(sig) sigma<-c(sigma, coda.samps[[i]][l1:l2,3])
+  }
+  if(sig){
+    samps<-data.frame(matrix(c(inter, n.slope, sigma), ncol=3, byrow=FALSE))
+    names(samps)<-c("inter", "n.slope", "sigma")
+  }
+  else{
+    samps<-data.frame(matrix(c(inter, n.slope), ncol=2, byrow=FALSE))
+    names(samps)<-c("inter", "n.slope", "sigma")
+    
+  }
+  return(samps)
+}
[…]

### 2023-12-11 code/collect_references.R

@@ -1,0 +1,285 @@
+library(tidyverse)
+
+
+# Mordecai 2013 -----------------------------------------------------------
+data.Mordecai2013 <- read.csv("data/raw/Mordecai_2013/Mordecai_2013_supp_data.csv") %>% 
+  select(trait.name, ref, mosquito_species, pathogen) %>% 
+  unique() %>% 
+  mutate(source = "Mordecai 2013")
+
+
+# Mordecai 2017 -----------------------------------------------------------
+data.Mordecai2017.Aegypti <- read.csv("data/raw/Mordecai_2017/aegyptiDENVmodelTempData_2016-03-30.csv", header = TRUE) %>%
+  # Exclude the Focks & Barrera 2006 data because they're from a model
+  filter(ref != "Focks_Barrera_2006_Research&TrainingTropicalDis_Geneva_Paper") %>%
+  # Exclude the Rohani et al 2009 data because it has "unrealistically long lifespans"
+  filter(ref != "Rohani_et_al_2009_SEJTropMedPH") %>%
+  # Exclude outliers from Beserra 2009 data
+  filter(!(ref == "Beserra_2009" & trait.name == "EFD" & trait > 15)) %>% 
+  mutate(mosquito_species = "Aedes aegypti") %>%
+  mutate(pathogen = ifelse(trait.name %in% c("b", "c", "PDR", "EIP"), case_when(
+    ref == "Alto&Bettinardi_2013_AJTMH" ~ "DENV",
+    ref == "Carrington_et_al_2013_PNTD" ~ "DENV",
+    ref == "Davis_1932_AmJEpidemiology" ~ "YFV",
+    ref == "Focks_et_al_1995_AJTMH" ~ "DENV",
+    ref == "Lambrects_et_al_2011_PNAS" ~ "DENV",
+    ref == "McLeah_et_al_1975_MosquitoNews" ~ "DENV",
+    ref == "McLean_et_al_1974_CanJMicobiol" ~ "DENV",
+    ref == "Watts_et_al_1987_AJTMH" ~ "DENV"
+  ), NA)) %>% 
+  select(trait.name, ref, mosquito_species, pathogen) %>% 
+  unique()
+
+data.Mordecai2017.Albopictus <- read.csv("data/raw/Mordecai_2017/albopictusCHIKVmodelTempData_2016-03-26.csv", header = TRUE) %>%
+  # The starved mosquitoes had much shorter survival than all other data, so remove them
[…]

### 2023-12-11 code/data-cleaning.R

@@ -1,0 +1,476 @@
+## Title: Mosquito Thermal Trait Data processing ###############################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Translate data from multiple sources into the format used in our
+##          analyses
+##
+## Contents: 0) Set-up, load in necessary packages
+##           1) Load in all data sets
+##           2) Combine data sets
+##           3) Rename non-focal focal systems and synonymous traits
+##           4) Data visualizations / diagnostics
+##           5) Export data set
+##
+##
+## Inputs:  data is found in data/raw/ in folders labeled by the first author
+##          and year of publication of the article we obtained the data from
+##
+##          A table explaining how traits are transformed into the ones used in
+##          analyses
+##
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized February 2023
+
+
+# 0) Set-up, load in necessary packages and data-sets ---------------------
+library(tidyverse)
+
+# 1) Load in all data sets ------------------------------------------------
+
+### * Mordecai 2013 ----
+# -- Mordecai_2013_supp_data.csv
+# -- Bayoh2001_mortality.csv (survival data for Anopheles gambiae from Bayoh 2001,
+#    taken from Supplementary Data of Mordecai 2013. See Bayoh2001-lifespan-analysis.R for details)
+data.Mordecai2013 <- read.csv("data/raw/Mordecai_2013/Mordecai_2013_supp_data.csv", header = TRUE) %>%
+  # Add in lifespan data
+  rbind(read_csv("data/clean/Bayoh2001_mortality.csv")) %>% 
+  mutate(lead_author = "Mordecai") %>%
+  # Make bc a probability
+  mutate(trait = ifelse(trait.name == "bc", trait / 100, trait)) %>% 
+  # Fix EIP entry errors (EIP = 0 really means parasite never developed)
+  mutate(trait = ifelse(trait.name == "EIP" & trait == 0, Inf, trait)) %>% 
+  mutate(year = "2013") %>%
[…]

### 2023-12-11 code/get-outputs.R

@@ -1,0 +1,708 @@
+## Title: Calculate Topt and critical thermal extrema #######################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Transform trait values, which we have fit TPCs to from data, in
+##          order to use in model analyses
+##
+## Contents: 0) Set-up, load in necessary packages and data-sets
+##           1) Define accessory functions
+##           2) Calculate R0 TPCs
+##           3) Calculate Topt
+##           4) Calculate Topt alternate: restrict to R0 > 1
+##           5) Calculate CTmin, CTmax, and CTwidth
+##           *) Diagnostics and visualizations
+##
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized March 2023
+# _______________________________________________________________________________
+
+# 0) Set-up, load in necessary packages and data-sets ---------------------
+
+# Load Libraries
+library(tidyverse)
+library(reshape2)
+library(multidplyr)
+library(foreach)
+library(doParallel)
+library(progress)
+
+eps <- .Machine$double.eps
+
+# Suppress summarise info
+options(dplyr.summarise.inform = FALSE)
+
+# Initialize a data frame to save our analyses
+init.df <- tibble(system_ID = character(), Temperature = double(), 
+                  Model = character(), sigmaH = double(), KH = double(), 
+                  variable = character(), lowHCI = double(), highHCI = double(),
+                  mean = double(), median = double())
+
+
+# Load in vector trait data
+data.Vec <- read_rds("results/VecTPC_vals.rds")
+# # Thin out the vector trait data samples
+# thin_size <- 2000
+# samples <- unique(data.Vec$sample_num)
+# num_samples <- length(samples)
+# sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
+# 
+# data.Vec <- data.Vec %>%
+#   filter(sample_num %in% sample_inds)
+
+# Load in host trait data
+data.Host <- read_rds("results/Host_vals.rds")
+
[…]

### 2023-12-11 code/get-thermal-trait-priors.R

@@ -1,0 +1,732 @@
+## Title: Prior distributions of mosquito thermal traits #######################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Compute prior distributions for thermal trait parameters and provide
+##          functions for sampling from these distributions
+##
+## Contents: 0) Set-up, load in necessary packages and data-sets
+##           1) Define accessory functions
+##           2) Calculate prior distributions of thermal trait parameters from data
+##           3) Save thermal trait parameter distributions
+##           4) Functions to sample from thermal trait parameter distributions
+##
+##
+## Inputs:  data - data/clean/data_for_TPC_fitting.csv
+##                 data/clean/trait_TPC_forms.csv
+##                 data/clean/gamma_fits.csv
+##
+##          code - code/Mordecai_2017/mcmc_utils_all.R
+##                 code/Mordecai_2017/temp_functions_all.R
+##
+## Outputs: data - data/clean/TPC_param_samples.csv
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized February 2023
+## Modified from original code provided in the following articles:
+# * Mordecai, E. A., J. M. Caldwell, M. K. Grossman, C. A. Lippi, L. R. Johnson, M. Neira, J. R. Rohr, S. J. Ryan, V. Savage, M. S. Shocket, R. Sippy, A. M. Stewart Ibarra, M. B. Thomas, and O. Villena. 2019. Thermal biology of mosquito-borne disease. Ecology letters 22:1690–1708.
+# * Mordecai, E. A., J. M. Cohen, M. V. Evans, P. Gudapati, L. R. Johnson, C. A. Lippi, K. Miazgowicz, C. C. Murdock, J. R. Rohr, S. J. Ryan, V. Savage, M. S. Shocket, A. Stewart Ibarra, M. B. Thomas, and D. P. Weikel. 2017. Detecting the impact of temperature on transmission of Zika, dengue, and chikungunya using mechanistic models. PLoS neglected tropical diseases 11:e0005568.
+# * Mordecai, E. A., K. P. Paaijmans, L. R. Johnson, C. Balzer, T. Ben-Horin, E. de Moor, A. McNally, S. Pawar, S. J. Ryan, T. C. Smith, and K. D. Lafferty. 2013. Optimal temperature for malaria transmission is dramatically lower than previously predicted. Ecology letters 16:22–30.
[…]

### 2023-12-11 code/host-traits.R

@@ -1,0 +1,63 @@
+## Title: Vertebrate host traits and parameters #######################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Record and save host traits for use in analyses
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized March 2023
+# _______________________________________________________________________________
+
+library(tidyverse)
+
+## Set resolution for host trait variation
+# Host density vector: Number of values to include to consider for vertebrate host density
+KH_vec_length <- 300
+
+# Biting tolerance vector: Number of values to consider for biting tolerance
+sigmaH_vec_length <- 300
+
+## Host life history & behavioral traits
+# Host recruitment rate:
+# upper estimate from range for Primate traits: (0.001150685, 0.009624300)
+lambdaH_baseline <- .005
+
+# Host mortality rate:
+# estimate from range for Primate traits: lifespan (8.6, 60) years
+muH_baseline <- 1 / (365 * 20)
+
+# Host maximum biting tolerance (mosquitoes bites per day)
+sigmaH_vec <- 10^seq(-0.25, 3.25, length.out = sigmaH_vec_length - 7) %>%
+  c(1, 10, 20, 50, 100, 1000, Inf) %>%
+  unique() %>% sort()
+sigmaH_baseline <- 100
+
+# Host carrying capacity
+KH_vec <- 10^seq(-2, 5, length.out = KH_vec_length - 6) %>%
+  c(10^seq(-2,5)) %>%
+  unique() %>% sort()
+
+## Host-related pathogen parameters
+# Probability of becoming infected after bite from infectious mosquito
+# operates as a scaling parameter
+betaH_baseline <- 1
+
+# Host recovery rate
+# plausible estimate for infectious period = (5-14 days)
+gammaH_vec <- 1 / c(5, 14)
+gammaH_baseline <- 1 / 5
+
+data.Host <- expand_grid(
+  # Life-history parameters
+  lambdaH = lambdaH_baseline,
+  muH = muH_baseline,
+  KH = KH_vec,
+  sigmaH = sigmaH_vec,
+  # Infection-related parameters
+  gammaH = gammaH_baseline,
+  betaH = betaH_baseline) %>%
+  as.data.frame() %>%
+  mutate(Model = ifelse(is.infinite(sigmaH), "Ross-Macdonald model", "Chitnis model"))
+
+# Save host traits
+write_rds(data.Host, "results/Host_vals.rds")

### 2023-12-11 code/sensitivity.R

@@ -1,0 +1,1007 @@
+## Title: Sensitivity and uncertainty analysis of Topt, CTmin, CTmax, and CTwidth
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Determine which traits most underlie the variation in key outputs
+##
+## Contents: 0) Set up, load in necessary packages and data-sets
+##           1) Define accessory functions
+##           2) Set up data frames
+##           3) Topt local, global sensitivity, uncertainty
+##           4) CTmin local, global sensitivity, uncertainty
+##           5) CTmax local, global sensitivity, uncertainty
+##           6) CTwidth local, global sensitivity, uncertainty
+##           *) Diagnostics and visualizations
+##
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized March 2023
+# _______________________________________________________________________________
+
+# 0) Set-up, load in necessary packages and data-sets ---------------------
+
+# Load Libraries
+library(tidyverse)
+library(reshape2)
+library(multidplyr)
+library(foreach)
+library(doParallel)
+library(progress)
+library(latex2exp) # nec
+library(viridis) # nec
+library(cowplot) # nec
+library(MetBrewer) #nec
+library(svglite) #nec
+library(HDInterval)
+
+# Set up parallel
+if (!exists("cl")) {
+  cl <- parallel::makeCluster(parallel::detectCores() - 2)
+  registerDoSNOW(cl)
+}
+
+eps <- .Machine$double.eps
+
+# Initialize a data frame to save our analyses
+init.df <- tibble(system_ID = c(), Temperature = c(), Model = c(),
+                  sigmaH = c(), KH = c(), variable = c(),
+                  lowHCI = c(), highHCI = c(), mean = c(), median = c())
+
+# Load needed datasets
+
+# Host trait dataset
+data.Host <- read_rds("results/Host_vals.rds")
+# Vector trait dataset
+data.Vec <- read_rds("results/VecTPC_vals.rds")
+
+# R0 data
+data.R0 <- read_rds("results/R0_vals.rds")
+
[…]

### 2023-12-11 code/trait-transform.R

@@ -1,0 +1,228 @@
+## Title: Transform TPC traits into model parameters #######################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Transform trait values, which we have fit TPCs to from data, in 
+##          order to use in model analyses
+##
+## Contents: 0) Set-up, load in necessary packages and data-sets
+##           1) Define accessory functions
+##           2) Create TPCs and deal with missing data
+##           3) Create parameters data frame
+##           4) Save parameters data frame
+##           *) Diagnostics and visualizations
+##
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized March 2023
+# _______________________________________________________________________________
+
+# 0) Set-up, load in necessary packages and data-sets ---------------------
+
+# Load Libraries
+library(tidyverse)
+library(reshape2)
+
+# 1) Define accessory functions -------------------------------------------
+# Define TPC functions
+# Briere function
+Briere <- function(q, Tmin, Tmax) {
+  function(t) {
+    pmax(q * t * (t - Tmin) * (Tmax - t)^(1 / 2), 0, na.rm = TRUE)
+  }
+}
+# Quadratic function
+Quadratic <- function(q, Tmin, Tmax) {
+  function(t) {
+    pmax(-q * (t - Tmin) * (t - Tmax), 0, na.rm = TRUE)
+  }
+}
+# Alternate Quadratic function
+AltQuadratic <- function(q, Tmin, Tmax) {
+  function(t) {
+    1/(q * t^2 - Tmin * t + Tmax)
+  }
+}
+
+# Linear
+Linear <- function(q, Tmax) {
+  function(t) {
+    pmax(q * (Tmax - t), 0, na.RM = FALSE)
+  }
+}
+
+# Function: designate proper thermal response function
+# - output is a function of temperature
+get.thermal.response <- function(data_in, Temperature) {
+  parms <- dplyr::select(data_in, c, T0, Tm)
+  function_type <- dplyr::select(data_in, func)
+  
+  temp_function <- case_when(
+    function_type == "Briere" ~ Briere(parms$c, parms$T0, parms$Tm),
+    function_type == "Quadratic" ~ Quadratic(parms$c, parms$T0, parms$Tm),
[…]

### 2023-12-11 code/vector-traits.R

@@ -1,0 +1,95 @@
+## Title: Mosquito Thermal Trait Data processing ###############################
+##
+## Project: Global zoonoses - spillover of mosquito-borne pathogens
+##
+## Purpose: Conduct all parts of the analysis
+##
+## Contents: 0) Set-up, load in necessary packages and data-sets
+##           1) Load empirical trait data
+##           2) Fit trait thermal performance curves to trait data
+##           3) Translate traits into model parameters
+##           4) Build data set incorporating all axes of variation
+##           5) Calculate model outputs
+##           6) Illustrate model outputs (might be done separately)
+##           7) Conduct sensitivity analysis
+##
+## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
+## Initialized March 2023
+
+
+# 0) Set-up, load in necessary packages and data-sets ---------------------
+library(tidyverse)
+
+# 1) Load empirical trait data --------------------------------------------
+
+# # Run this to produce workable dataset from raw data for the first time
+plot_bool <- FALSE # decide whether you'd like to generate a diagnostic plot
+source("code/data-cleaning.R")
+
+# # Alternatively, run this to load pre-processed dataset
+# # load dataset for fitting trait TPCs
+# data.in.TPC <- read_rds("data/clean/data_for_TPC_fitting.rds")
+
+# 2) Fit trait thermal performance curves to trait data -------------------
+
+# Run this to generate samples of trait TPC parameters from informed posterior distributions for the first time
+# Set parameters for MCMC
+n.chains <- 5
+n.adapt <- 5000
+n.samps <- 5000
+# Do you want to look at diagnostic plots?
+plot_bool <- FALSE
+source("code/get-thermal-trait-priors.R")
+write_rds(data.in.transform, "results/TPC_param_samples.rds")
+
+# # Alternatively, run this to load pre-processed data set
+# data.in.transform <- read_rds("results/TPC_param_samples.rds")
+
+# 3) Translate traits into model parameters -------------------------------
+
+# Define temperature range of study
+Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
+
+# Thin sample size
[…]

### 2023-12-11 manuscript-figures.Rmd
add summary of TPC fits and justification for An. gambiae lifespan fitting

@@
 ---
-title: "Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission"
+title: "Figures from: Impacts of host availability and temperature on mosquito-borne parasite transmission"
 author: |
@@
 
+# Uncomment this to reduce resolution of trait TPCs, to help with memory issues
 # thin_size <- 500
@@
 
-```{r fig-S8_2_dR0dvar_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$.
+```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$.
 Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
@@
                filter(KH %in% KH_vals & sigmaH %in% unique(data.dR0dT$sigmaH))) %>%
-  # Restrict to relevant temperatures (V0 and R0 > 0)
+  # Restrict to relevant temperatures (i.e. where V0 and R0 > 0)
   right_join(temp_lims) %>% 
@@
 
-# # R0 derivative dataframe
-# R0deriv_df <- data.R0 %>% 
-#   group_by(system_ID, Model, sigmaH, KH) %>% 
-#   arrange(system_ID, Model, sigmaH, KH, Temperature) %>%
-#   mutate(deriv = (mean - lag(mean)) / (Temperature - lag(Temperature)))
-
-# test_plot <- R0deriv_df %>% 
-#   filter(KH %in% c(1), sigmaH %in% c(100, Inf), median > 0) %>% 
-#   ggplot(aes(x = Temperature, y = deriv)) +
-#   geom_line() +
-#   geom_hline(yintercept = 0) +
-#   facet_rep_grid(
-#     rows = vars(KH, sigmaH),
-#     cols = vars(system_label),
-#     labeller = labeller(
-#       system_label = sens_labels,
-#       sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-#       KH = as_labeller(appender_KH, default = label_parsed)
-#     ),
-#     scales = "free"
-#   ) 
-# test_plot
-
-# NB: in order to produce an R0 TPC, overall derivative should go from positive to negative
+# NB: in order to produce an R0 TPC, "overall" derivative should go from positive to negative
 plot.dR0dk <- dR0dk.df %>%
@@
 
-```{r fig-S8_3_dR0dvar_comparison, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
+```{r fig-7_explain_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
 Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
@@
 Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
-Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
-'}
+Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.'}
 
@@
          prop_sens = abs_median / total_sens) %>% 
-  arrange(system_label, Temperature, KH, sigmaH, focal_var) #%>% 
-# filter(focal_var %in% c("Parasite development rate", "Biting frequency"))
-# # mutate(median = abs(median)) %>% 
-# select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
-# pivot_wider(names_from = KH, values_from = prop_sens) %>% 
-# mutate(sens_comp = ifelse(`10` == 0 & `1` == 0,
-#                           0,
-#                           (`10` - `1`) / ((`10` + `1`)/2)))
-# mutate(sens_comp = (`10` - `1`) / `1`)
+  arrange(system_label, Temperature, KH, sigmaH, focal_var)
 
@@
 
-```{r fig-S8_4_dR0dvar_compzoom, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
-Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
-Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
-Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
-Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
-'}
+``` {r}
+# 1. change in non-normalized sensitivity as KH: 1 to 100
+compzoom_dR0dk.df_1 <- dR0dk.df %>%
+  filter(sigmaH == 10, focal_var != "Overall") %>% 
+  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
+  pivot_wider(names_from = KH, values_from = median) %>%
+  mutate(abs_comp = `1` - `100`)
+
+# 2. Absolute change in non-normalized sensitivity as KH: 1 to 100
+compzoom_dR0dk.df_2 <- dR0dk.df %>%
+  filter(sigmaH == 10, focal_var != "Overall") %>% 
+  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
+  pivot_wider(names_from = KH, values_from = median) %>%
+  mutate(abs_comp = abs(`1` - `100`))
+
+# 3. Proportional change in non-normalized sensitivity as KH: 1 to 100
+compzoom_dR0dk.df_3 <- dR0dk.df %>%
+  filter(sigmaH == 10, focal_var != "Overall") %>% 
+  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
+  pivot_wider(names_from = KH, values_from = median) %>%
+  mutate(abs_comp = (`1` - `100`)/(`1`+1))
+
+# 4. Proportional change in non-normalized sensitivity as KH: 1 to 100
+compzoom_dR0dk.df_4 <- dR0dk.df %>%
+  filter(sigmaH == 10, focal_var != "Overall") %>% 
+  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
+  pivot_wider(names_from = KH, values_from = median) %>%
+  mutate(temp_comp = `1` - `100`) %>% 
+  group_by(system_ID, Temperature) %>% 
+  mutate(total_comp = sum(temp_comp),
+         abs_comp = temp_comp / sum(temp_comp))
 
@@
 plot.compzoom_dR0dk
-```
-
-```{r fig-S8_R0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_unc}  The uncertainty of $\\mathcal{R}_0$ to mosquito traits across temperatures as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$ when vertebrate host population density is set to one individual per hectare.
-Temperatures are restricted to those at which $\\mathcal{R}_0$ is positive for the given system.
-At the cool end of the thermal niche, variation in $\\mathcal{R}_0$ is mostly driven by the probability of surviving the extrinsic incubation period, except in the case of (d) \\textit{An.
-gambiae} and \\textit{P.
-falciparum}.
-As temperature is increased, the influence of adult mosquito lifespan also increases to eventually become the most influential parameter for all systems except (e) \\textit{Cx.
-quinquefasciatus} and WNV.'}
-Temp_range_for_plot <- R0.HPD %>%
-  ungroup() %>%
-  dplyr::filter(rel_HPD_width > eps) %>%
-  dplyr::select(Temperature) %>%
-  range()
-
-plot.R0.rel.sens <- R0.HPD %>%
-  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
-  # For each KH value, sum up all uncertainty values to get total uncertainty across parameters
-  group_by(system_ID, sigmaH, KH, Temperature) %>%
-  mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each uncertainty value by the total uncertainty
-  mutate(sens_rel = rel_HPD_width / sens_total) %>%
-  arrange(sens_rel) %>%
-  arrange(focal_var) %>%
-  # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
-  geom_area() +
-  scale_fill_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(
-    name = unname(TeX("Relative contribution to $R_0$ HPD width"))
-  ) +
-  facet_grid(
-    cols = vars(system_label),
-    rows = vars(sigmaH),
-    labeller = labeller(
-      system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
-    ),
-    scales = "free"
-  ) +
-  theme_minimal(10) +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 10),
-    legend.position = "bottom",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text.x = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-plot.R0.rel.sens
 ```

### 2023-12-11 code/AnGamb_lf_just.R

@@ -1,0 +1,89 @@
+# Anopheles gambiae lifespan justification
+library(tidyverse)
+
+# Get appropriate data
+data <- read_rds("data/clean/data_for_TPC_fitting.rds") %>% 
+  filter(system_ID %in% c(
+    "Anopheles gambiae / Plasmodium falciparum",
+    "Anopheles gambiae / Plasmodium spp.",
+    "Anopheles gambiae / none",
+    "Anopheles spp. / Plasmodium falciparum",
+    "Anopheles spp. / Plasmodium spp.",
+    "Anopheles spp. / none"),
+    trait.name %in% c("lf")
+  ) %>% 
+  arrange(T)
+
+# Set up nonlinear fits
+y = data$trait
+x = data$T
+
+# Get fits
+Briere_fit <- nls(y ~ c * x * (x - T0) * sqrt(Tm - x),
+                  start = list(c = 1, T0 = 0, Tm = 50))
+Quad_fit <- nls(y ~ -c * (x - T0) * (x - Tm),
+                start = list(c = 1, T0 = 0, Tm = 50))
+z = 1/y
+mu_Quad_fit <- nls(z ~ c * x^2 - r * x + t,
+                   start = list(c = 1, r = 1, t = 1))
+
+# Collect fits
+fit_table <- tibble(T = seq(0,50, by = 0.1), 
+                    Briere = predict(Briere_fit, newdata = list(x = seq(0,50, by = 0.1))), 
+                    Quadratic = predict(Quad_fit, newdata = list(x = seq(0,50, by = 0.1))), 
+                    mu_Quadratic = 1/predict(mu_Quad_fit, newdata = list(x = seq(0,50, by = 0.1)))
+                    ) %>% 
+  pivot_longer(cols = c("Briere", "Quadratic", "mu_Quadratic"), names_to = "model") %>% 
+  group_by(T) %>% 
+  mutate(abs_change = (value[model == "mu_Quadratic"] - value),
+         perc_change = abs_change / value[model == "mu_Quadratic"]
+         )
+
+# Determine where V0 is greater than zero
+temp_lims <- read_rds("results/medianVec_vals.rds") %>% 
+  filter(system_ID ==  "Anopheles gambiae / Plasmodium falciparum",
+         V0 > 0
+         ) %>% 
+  summarise(min_Temp = min(Temperature),
+            max_Temp = max(Temperature))
+  
+
+trait_plots <- fit_table %>% 
+  ggplot(aes(x = T)) +
[…]

### 2023-12-11 code/vector-traits.R

@@ -42,6 +42,20 @@ plot_bool <- FALSE
 source("code/get-thermal-trait-priors.R")
 write_rds(data.in.transform, "results/TPC_param_samples.rds")
 
+# Get summary statistics of each trait for each system
+table <- read_rds("results/TPC_param_samples.rds") %>% 
+  pivot_longer(cols = c("c","T0", "Tm"), names_to = "hyperparameter") %>% 
+  group_by(system_name = system_ID, trait, hyperparameter, `function` = func) %>% 
+  filter(!is.na(value)) %>% # removes T0 for Culex lifespan, which is linear and hence only has 2 parameters
+  mutate(mean = mean(value),
+            median = median(value),
+            lowHCI_89 = quantile(value, 0.055),
+            highHCI_89 = quantile(value, 0.945)) %>% 
+  dplyr::select(-c(value, sample_num, func, system_ID)) %>% 
+  distinct()
+
+write_csv(table, "results/TPC_fit_summary.csv")
+
 # # Alternatively, run this to load pre-processed data set
 # data.in.transform <- read_rds("results/TPC_param_samples.rds")
 
@@ -58,7 +72,7 @@ source("code/trait-transform.R")
 
 write_rds(data.in.params, "results/VecTPC_vals.rds", compress = "gz")
 
-# Mean values
+# Save trait mean values
 mean.Vec <- data.in.params %>%
   dplyr::select(-c(mosquito_species, pathogen, muL, etaL)) %>%
   pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
@@ -75,7 +89,7 @@ mean.Vec <- data.in.params %>%
 
 write_rds(mean.Vec, "results/meanVec_vals.rds", compress = "gz")
 
-# Median values (this one is used more frequently)
+# Save trait median values (this one is used more frequently)
 median.Vec <- data.in.params %>%
   dplyr::select(-c(mosquito_species, pathogen, muL, etaL)) %>%
   pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%

### 2023-12-13 manuscript-figures.Rmd
small edits to figures

@@
                              TeX("(c) Eggs per female per day: $\\sigma_V f$"),
-                             TeX("(d) Immature mosquito development rate: $\\rho_L$ (day$^{-1}$)"),
-                             TeX("(e) Probability of immature mosquito survival: $\\delta_L$"),
+                             TeX("(d) Mosquito development rate: $\\rho_L$ (day$^{-1}$)"),
+                             TeX("(e) Prob. of immature mosquito survival: $\\delta_L$"),
                              TeX("(f) Probability of surviving EIP: $\\theta_V$"),
@@
 
-# Supplementary Figures
-
-```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
-The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
-and \\textit{P.
-falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
-Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
-Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
-Vertebrate host population density is varied on a $\\log_{10}$ scale.
-All remaining parameters are given in Table 1 and Figure 3.'}
-# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
-
-# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
-# y = Temperature
-# color = R0
-# curves:
-#   R0 = 1 contour (black curve)
-#   Topt (red curve)
-
-# Facets:
-# Rows = levels of vertebrate host population density
-# Columns = two MBPT systems
-# Total = 6 plots
-
-## Set up plot data frame
-# We re-create the output data frame so that we can vary sigmaH correctly.
-# We also drop the resolution of KH down to just three values
-# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"
-
-## Configure data frame for plotting
-R0_df <- data.R0 %>%
-  select(system_ID, system_label, Temperature, sigmaH, KH, median, mean) %>%
-  rename(R0 = mean) %>%
-  # Consider only 3 values of KH (on a log10-scale)
-  filter(KH %in% c(.1, 1, 10)) %>%
-  # Choose a limited range of sigmaH values
-  filter(sigmaH < 10^2.275 | is.infinite(sigmaH)) %>%
-  # Group by plotting variables
-  group_by(system_ID, KH, sigmaH) %>%
-  # Calculate Topt (which.max requires grouping)
-  mutate(Topt = `Temperature`[which.max(R0)]) %>%
-  as_tibble() %>%
-  arrange(system_ID, sigmaH, Temperature)
-
-## Add a "point at infinity" for sigmaH
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^2.75
-
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^2.4
-
-R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 8)
-
-Topt_for_R0_df <- data.Topt %>%
-  # Arrange along the plotting variables
-  arrange(system_ID, sigmaH, KH, median) %>%
-  mutate(sigmaH_proxy = sigmaH)
-Topt_for_R0_df <- inf_skew_func(Topt_for_R0_df, infinite_skew, infinite_divide, 8)
-
-## PLOTTING ##
-
-## Options
-# Define sigmaH tick breaks and labels
-sigmaH_breaks_heatmap <- c(10^c(seq(-1, 2, by = 1)), infinite_divide, infinite_skew)
-sigmaH_labels_heatmap <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-
-# Labels for facet rows
-R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
-mylabels <- as_labeller(c(
-  `0.1` = "0.1 vertebrate hosts / ha",
-  `1` = "1 vertebrate host / ha",
-  `10` = "10 vertebrate hosts / ha"
-))
-
-R0_heatmap_labels <- as_labeller(c(
-  "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti*  \nand  DENV",
-  "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti*  \nand  ZIKV",
-  "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand  DENV",
-  "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae*  \nand  *P. falciparum*",
-  "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
-))
-
-# Breaks used to decide fill for the heat map
-fill_breaks <- c(1, seq(5, 20, by = 5), Inf)
-
-# Define colors for heat map so that values of R0>1 go from yellow to red
-my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))
-
-## PLOT ##
-R0_plot <- R0_df %>%
-  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature)) +
-  # Mosquito thermal tolerance range lines
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmin_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmax_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-  # R0 contours for FINITE sigmaH:
-  geom_contour_filled(
-    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
-    mapping = aes(z = R0),
-    breaks = fill_breaks
-  ) +
-  # R0 contours for INFINITE sigmaH:
-  geom_contour_filled(
-    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
-    mapping = aes(z = R0),
-    breaks = fill_breaks
-  ) +
-  # R0 = 1 contour:
-  geom_contour(aes(colour = "R0=1", z = R0), breaks = c(1), size = 1) +
-  # Topt curve:
-  geom_path(
-    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)) %>% arrange(sigmaH_proxy),
-    mapping = aes(
-      x = sigmaH_proxy,
-      y = median,
-      colour = "Topt"
-    ),
-    lwd = 1,
-    linetype = 1
-  ) +
-  # white lines breaking up finite/infinite sigmaH values
-  geom_vline(
-    aes(xintercept = 0.85 * infinite_divide),
-    colour = "white",
-    lwd = .8,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = infinite_divide),
-    colour = "white",
-    lwd = .8,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = 1.2 * infinite_divide),
-    colour = "white",
-    lwd = .8,
-    show.legend = FALSE
-  ) +
-  # x-axis:
-  scale_x_log10(
-    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
-    breaks = sigmaH_breaks_heatmap,
-    labels = sigmaH_labels_heatmap,
-    expand = c(0, 0)
-  ) +
-  # y-axis:
-  scale_y_continuous(
-    name = expression("Temperature "(degree * C)),
-    expand = c(0, 0),
-    limits = c(16, 35),
-    breaks = seq(10, 36, by = 2)
-  ) +
-  # color:
-  scale_colour_manual(
-    name = "",
-    labels = c(
-      "R0=1" = unname(TeX("$R_0=1$")),
-      "Topt" = "Transmission\nthermal\noptimum",
-      "VTTR" = "Mosquito\npopulation\nthermal\nniche"
-    ),
-    values = c("black", "purple", "grey"),
-    guide = guide_legend(
-      order = 1,
-      keyheight = unit(2, "cm"),
-      override.aes = list(size = 6)
-    )
-  ) +
-  # fill:
-  scale_fill_manual(
-    name = TeX("$R_0$"),
-    values = my.cols,
-    guide = guide_colorsteps(
-      order = 2,
-      breaks = fill_breaks,
-      barheight = unit(8, "cm")
-    )
-  ) +
-  # faceting:
-  facet_grid(
-    rows = vars(KH),
-    cols = vars(system_label),
-    labeller = labeller(
-      .rows = mylabels,
-      .cols = R0_heatmap_labels
-    ),
-    # repeat.tick.labels = "left"
-  ) +
-  # theme options:
-  theme_minimal_hgrid(10) +
-  theme(
-    axis.line = element_line(),
-    legend.text = element_text(size = 10),
-    legend.text.align = 0,
-    strip.text.y = ggtext::element_markdown(
-      size = 7,
-      hjust = 0.5
-    ),
-    strip.text.x = ggtext::element_markdown(
-      size = 7,
-      hjust = 0
-    ),
-    panel.spacing = unit(2, "pt")
-  )
-
-# Plot it
-R0_plot
-```
-
-```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
-The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
-and \\textit{P.
-falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
-Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
-Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
-Vertebrate host population density is varied on a $\\log_{10}$ scale.
-All remaining parameters are given in Table 1 and Figure 3.'}
-Topt_df <- data.Topt %>%
-  filter(KH < 10^4 + 1) %>%
-  pivot_wider(
-    id_cols = c("system_label", "Model", "sigmaH", "KH"),
-    names_from = variable,
-    values_from = c("mean", "median", "lowHCI", "highHCI")
-  ) %>%
-  rename(
-    mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
-    highHCI = highHCI_Topt
-  ) %>%
-  # Arrange along the plotting variables
-  arrange(system_label, KH, median, sigmaH) %>%
-  ungroup()
-
-# PLOTTING
-Topt_plot <- Topt_df %>%
-  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
-  ## Set up plot ##
-  # color = sigmaH
-  ggplot(aes(x = KH, colour = as.factor(sigmaH))) +
-  # Topt curves:
-  geom_path(aes(y = median), lwd = 1) +
-  # x-axis: log10 scale, no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    breaks = c(10^c(seq(-1, 4, by = 1))),
-    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  # y-axis
-  scale_y_continuous(
-    name = expression("Thermal optimum "(degree * C)),
-    expand = c(0, 0),
-    limits = c(21, 30.5),
-    breaks = seq(21, 32, by = 1)
-  ) +
-  # color:
-  scale_colour_manual(
-    name = "Vertebrate host biting tolerance\n(bites per host per day)",
-    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
-    breaks = c(1, 10, 100, Inf),
-    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
-  ) +
-  scale_fill_manual(
-    name = "Vertebrate host biting tolerance\n(bites per host per day)",
-    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
-    breaks = c(1, 10, 100, Inf),
-    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
-  ) +
-  # faceting:
-  facet_wrap(~system_label, nrow = 2, labeller = labeller()) +
-  # theme options:
-  theme_minimal(10) +
-  guides(color = guide_legend(override.aes = list(size = 4))) +
-  theme(
-    legend.position = "bottom",
-    legend.margin = margin(),
-    legend.direction = "vertical",
-    legend.title = element_text(size = 10),
-    legend.text = element_text(
-      size = 10,
-      hjust = 0
-    ),
-    legend.justification = "left",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# Plot
-shift_legend(Topt_plot)
-```
-
-```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} The thermal optima predicted by the model can be substantially different at low levels of biting tolerance.
-At low host population densities, there may be warmer (a, b, c, e) or cooler (d) thermal optima when biting tolerance is low compared to when it is high.
-Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
-Vertebrate host biting tolerance is varied on a $\\log_{10}$ scale with a break to indicate values of $\\mathcal{R}_0$ when biting tolerance is unlimited.
-'}
-# x-axis = vertebrate host biting tolerance
-# y-axis = thermal optimum
-# color = vertebrate host population density
-
-infinite_skew <- 10^3.7
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^3.35 # 10^log10(max_sigmaH*1)
-
-Topt_df <- data.Topt %>%
-  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
-                               sigmaH,
-                               infinite_skew
-  ))
-Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)
-
-sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15 * infinite_divide, infinite_skew)
-sigmaH_labels <- c(TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$")), TeX("$\\ldots$"), TeX("$\\infty$"))
-
-Topt_plot <- Topt_df %>%
-  # Choose appropriate pop. dens. values and group
-  filter(KH %in% 10^seq(0, 3)) %>%
-  arrange(system_label, KH, sigmaH, median) %>%
-  ## Set up plot ##
-  # color = sigmaH
-  ggplot(aes(x = sigmaH_proxy, colour = as.factor(KH))) +
-  # Topt curves:
-  geom_path(aes(y = median), lwd = 1) +
-  # white lines breaking up finite/infinite sigmaH values:
-  geom_vline(
-    aes(xintercept = 1.05 * infinite_divide),
-    colour = "white",
-    lwd = .9,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = 1.15 * infinite_divide),
-    colour = "white",
-    lwd = .9,
-    show.legend = FALSE
-  ) +
-  geom_vline(
-    aes(xintercept = 1.25 * infinite_divide),
-    colour = "white",
-    lwd = .9,
-    show.legend = FALSE
-  ) +
-  # x-axis: Use a log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
-    expand = c(0, 0),
-    # limits = c(0.5, 150),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels
-  ) +
-  # y-axis
-  scale_y_continuous(
-    name = expression("Thermal optimum "(degree * C)),
-    expand = c(0, 0), # c(0.05, 0.05),
-    limits = c(21, 30), # mean: 21-31, median: 21-32
-    breaks = seq(21, 32, by = 1)
-  ) +
-  # color:
-  scale_colour_manual(
-    name = "Vertebrate host population\ndensity (ind/ha)",
-    values = met.brewer("Hokusai3", 4)
-  ) +
-  scale_fill_manual(
-    name = "Vertebrate host population\ndensity (ind/ha)",
-    values = met.brewer("Hokusai3", 4)
-  ) +
-  # faceting:
-  facet_wrap(~system_label,
-             scales = "free",
-             nrow = 2,
-             labeller = labeller()
-  ) +
-  # theme options:
-  theme_minimal(10) +
-  guides(color = guide_legend(override.aes = list(size = 4))) +
-  theme(
-    legend.position = "bottom",
-    legend.margin = margin(),
-    legend.direction = "vertical",
-    legend.title = element_text(size = 10),
-    legend.text = element_text(
-      size = 10,
-      hjust = 0
-    ),
-    legend.justification = "left",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# Plot
-shift_legend(Topt_plot)
-```
-
-```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} The critical thermal minimum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
-Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
-In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text).
-Shown here are the median values of the critical thermal minimum with respect to mosquito trait TPC hyperparameter posterior distributions.
-Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
-'}
-#   x    = biting tolerance (with a point at infinity)
-#   y    = vertebrate host population density
-# colour = parasite critical thermal minimum (CTmin)
-# Facets = systems
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
-max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^2.35
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^2.7
-
-# Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-
-CTmin_df <- data.CT %>%
-  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
-  pivot_wider(names_from = variable, values_from = median) %>% 
-  # If CTwidth is essentially zero, set CTmin to Inf indicating R0 < 1
-  mutate(CTmin = if_else(CTwidth < eps, Inf, CTmin)) %>%
-  mutate(sigmaH_proxy = sigmaH) %>%
-  # Arrange along the plotting variables
-  arrange(system_ID, KH, sigmaH_proxy, CTmin) %>%
-  ungroup() %>%
-  # Assign a value for cases where R0<1 for all temperatures
-  mutate(CTmin = ifelse(is.finite(CTmin), CTmin, 100))
-
-CTmin_df <- inf_skew_func(CTmin_df, infinite_skew, infinite_divide, 8)
-
-maxCTmin <- ceiling(max(filter(CTmin_df, CTmin<100)$CTmin))
-
-CTmin_breaks <- c(seq(14, 35, by = 2), 101)
-
-CTmin_heat_plots <- CTmin_df %>%
-  ## Set up plot ##
-  # x = biting tolerance (with a point at infinity),
-  # y = vertebrate host population density,
-  # color = width of parasite thermal median_CTwidth
-  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmin)) +
-  # CTmin for FINITE sigmaH:
-  geom_contour_filled(
-    data = filter(
-      CTmin_df,
-      sigmaH_proxy < 10^2.2
-    ),
-    breaks = CTmin_breaks
-  ) +
-  # CTmin for INFINITE sigmaH:
-  geom_contour_filled(
-    data = filter(
-      CTmin_df,
-      sigmaH_proxy > 10^2.4,
-      sigmaH_proxy < infinite_divide
-    ),
-    breaks = CTmin_breaks
-  ) +
-  # x-axis: log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(0.05, 1E4),
-    breaks = 10^seq(-1, 4, 1),
-    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  # y-axis: log10-scale y axis, with no buffer space
-  scale_y_log10(
-    name = TeX("Biting tolerance (bites per host per day)"),
-    expand = c(0, 0),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels
-  ) +
-  # fill:
-  scale_fill_manual(
-    name = "Critical thermal minimum (°C)",
-    values = c(viridis(9), "grey", "grey"),
-    labels = ~ ifelse(.x < maxCTmin, .x, "n/a")
-  ) +
-  # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-  # legend:
-  guides(fill = guide_coloursteps(
-    title.position = "top",
-    title.hjust = 0.5,
-    barwidth = 12,
-    show.limits = TRUE
-  )) +
-  # theme options:
-  theme_minimal(10) +
-  theme(
-    legend.box = "horizontal",
-    legend.position = "bottom",
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.direction = "horizontal",
-    legend.justification = "left",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# Plot
-shift_legend(CTmin_heat_plots)
-```
-
-```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} The critical thermal maximum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
-Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
-In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text).
-Shown here are the median values of the critical thermal maximum with respect to mosquito trait TPC hyperparameter posterior distributions.
-Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
-'}
-#   x    = biting tolerance (with a point at infinity)
-#   y    = vertebrate host population density
-# colour = parasite critical thermal maximum (CTmax)
-# Facets = systems
-
-# add many proxy sigmaH points at infinity to make the values easier to see there
-max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
-# Value of sigmaH to replace 'Inf' with for plotting
-infinite_skew <- 10^2.35
-# Used to create a gap dividing finite and infinite sigmaH
-infinite_divide <- 10^2.7
-
-# Define sigmaH tick breaks and labels
-sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
-sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
-
-CTmax_df <- data.CT %>%
-  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
-  pivot_wider(names_from = variable, values_from = median) %>% 
-  # If CTwidth is essentially zero, set CTmax to -Inf indicating R0 < 1
-  mutate(CTmax = if_else(CTwidth < eps, Inf, CTmax)) %>%
-  mutate(sigmaH_proxy = sigmaH) %>%
-  # Arrange along the plotting variables
-  arrange(system_ID, KH, sigmaH_proxy, CTmax) %>%
-  ungroup() %>%
-  # Assign a value for cases where R0<1 for all temperatures
-  mutate(CTmax = ifelse(is.finite(CTmax), CTmax, -100))
-
-CTmax_df <- inf_skew_func(CTmax_df, infinite_skew, infinite_divide, 8)
-
-minCTmax <- floor(min(filter(CTmax_df, CTmax>0)$CTmax))
-
-CTmax_breaks <- c(-101, seq(21, 35, by = 2))
-
-CTmax_heat_plots <- CTmax_df %>%
-  ## Set up plot ##
-  # x = biting tolerance (with a point at infinity),
-  # y = vertebrate host population density,
-  # color = width of parasite thermal median_CTwidth
-  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmax)) +
-  # CTmin for FINITE sigmaH:
-  geom_contour_filled(
-    data = filter(
-      CTmax_df,
-      sigmaH_proxy < 10^2.2
-    ),
-    breaks = CTmax_breaks
-  ) +
-  # CTmin for INFINITE sigmaH:
-  geom_contour_filled(
-    data = filter(
-      CTmax_df,
-      sigmaH_proxy > 10^2.4,
-      sigmaH_proxy < infinite_divide
-    ),
-    breaks = CTmax_breaks
-  ) +
-  # x-axis: log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(0.05, 1E4),
-    breaks = 10^seq(-1, 4, 1),
-    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  # y-axis: log10-scale y axis, with no buffer space
-  scale_y_log10(
-    name = TeX("Biting tolerance (bites per host per day)"),
-    expand = c(0, 0),
-    breaks = sigmaH_breaks,
-    labels = sigmaH_labels
-  ) +
-  # fill:
-  scale_fill_manual(
-    name = "Critical thermal maximum (°C)",
-    values = c("grey", viridis(9)),
-    labels = ~ ifelse(.x < minCTmax - 1, "n/a", .x)
-  ) +
-  # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-  # legend:
-  guides(fill = guide_coloursteps(
-    title.position = "top",
-    title.hjust = 0.5,
-    barwidth = 12,
-    show.limits = TRUE
-  )) +
-  # theme options:
-  theme_minimal(10) +
-  theme(
-    legend.box = "horizontal",
-    legend.position = "bottom",
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.direction = "horizontal",
-    legend.justification = "left",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-# Plot
-shift_legend(CTmax_heat_plots)
-```
-
-```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} The critical thermal minimum ($\\textrm{CT}_{\\min}$, blue curves) and maximum ($\\textrm{CT}_{\\max}$, red curves) for parasite population persistence depend on vertebrate host availability, even when vertebrate hosts tolerate any level of mosquito biting (dotted curves).
-Transmission is sustained ($\\mathcal{R}_0$>1) in the regions enclosed by the red and blue curves.
-$\\textrm{CT}_{\\min}$ is a convex function of vertebrate host population density while $\\textrm{CT}_{\\max}$ is concave.
-The points where the red and blue curves touch indicate thresholds of vertebrate host population density beyond which parasite population persistence is no longer possible at any temperature (i.e.
-$\\mathcal{R}_0$(T)<1) (see Figure 6 in the main text).
-Shown here are the median values of the critical thermal minimum, maximum, and mosquito thermal tolerance niche with respect to mosquito trait TPC hyperparameter posterior distributions.
-Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
-All remaining parameters are given in Table 1 and Figure 2.'}
-# x-axis = vertebrate host population density
-# y-axis = Temperature
-# linetype = biting tolerance
-# colour = CT_min (blue), CT_max (red)
-
-CTRange_df <- data.CT %>%
-  # Arrange along the plotting variables
-  select(system_label, sigmaH, KH, variable, value = median) %>%
-  # Choose a few sigmaH values to plot, including Inf
-  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
-  filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 101)]) %>%
-  pivot_wider(
-    id_cols = c("system_label", "sigmaH", "KH"),
-    names_from = variable, values_from = value
-  ) %>%
-  group_by(system_label, KH, sigmaH) %>%
-  mutate(CTwidth = max(CTmax - CTmin, 0)) %>%
-  filter(CTwidth > 0.05) %>%
-  # Arrange along the plotting variables
-  arrange(system_label, KH, sigmaH, CTmax, CTmin) %>%
-  ungroup() %>%
-  melt(id = c("system_label", "KH", "sigmaH")) %>%
-  arrange(KH, sigmaH)
-
-CTRange_plots <- CTRange_df %>%
-  ## Set up plot ##
-  # x-axis = population density, y-axis = temperature,
-  # color = thermal extrema, linetype = sigmaH
-  ggplot(
-    aes(x = KH, y = value, linetype = as.factor(sigmaH), color = variable)
-  ) +
-  # Mosquito thermal tolerance range lines
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmin_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-  geom_hline(
-    data = MosqThermRange_df,
-    aes(yintercept = CTmax_V0, colour = "VTTR"),
-    lwd = 1.275
-  ) +
-  # Curves showing CTmin and CTmax
-  geom_line(
-    data = filter(CTRange_df, variable == "CTmin"),
-    lwd = 1
-  ) +
-  geom_line(
-    data = filter(CTRange_df, variable == "CTmax"),
-    lwd = 1
-  ) +
-  # x-axis: log10-scale with no buffer space
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    limits = c(1E-2, 1E5),
-    breaks = 10^seq(-1, 4),
-    labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  # y-axis: small buffer space
-  scale_y_continuous(
-    name = expression("Temperature "(degree * C)),
-    expand = c(0.05, 0.05),
-    limits = c(min(MosqThermRange_df$CTmin_V0), max(MosqThermRange_df$CTmax_V0)),
-    breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
-                 floor(range(CTRange_df$value, na.rm = TRUE)[2]),
-                 by = 2
-    )
-  ) +
-  # linetype:
-  scale_linetype_manual(
-    name = "Vertebrate host biting tolerance\n(bites per host per day)",
-    values = c("solid", "dashed", "longdash", "dotted"),
-    breaks = c(1, 10, 100, Inf),
-    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
-  ) +
-  # color:
-  scale_colour_manual(
-    name = "Thermal extrema",
-    breaks = c("CTmax", "CTmin", "VTTR"),
-    labels = c("Critical maximum", "Critical minimum", "Mosquito population\nthermal niche"),
-    values = c("red", "blue", "grey"),
-    guide = guide_legend(keyheight = unit(40, "cm"))
-  ) +
-  # faceting:
-  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-  # legend:
-  guides(
-    color = guide_legend(override.aes = list(size = 4), order = 1),
-    linetype = guide_legend(keywidth = 4, order = 2),
-  ) +
-  # theme options:
-  theme_minimal_hgrid(10) +
-  theme(
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 10,
-      hjust = 0
-    )
-  )
-
-# Plot
-shift_legend(CTRange_plots)
-```
-
-```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}
-# Estimating the difference between Topt and Topt_RM numerically using our previous data
-Toptdiff_CCH <- data.Topt %>%
-  ungroup() %>%
-  select(system_ID, sigmaH, KH, median) %>%
-  rename(Topt = median) %>%
-  filter(is.finite(sigmaH)) %>%
-  distinct()
-
-Toptdiff_RM <- data.Topt %>%
-  ungroup() %>%
-  filter(is.infinite(sigmaH)) %>%
-  select(system_ID, KH, median) %>%
-  rename(Topt_RM = median) %>%
-  distinct()
-
-Toptdiff_df <- left_join(Toptdiff_CCH, Toptdiff_RM) %>%
-  mutate(Toptdiff = Topt_RM - Topt) %>%
-  mutate(absToptdiff = abs(Toptdiff)) %>%
-  mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>%
-  mutate(sigmaHKH = sigmaH * KH) %>%
-  group_by(system_ID) %>%
-  filter(absToptdiff == max(absToptdiff)) %>%
-  select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>%
-  distinct()
-
-# Calculating Topt0 using the "simplified" equation
-Topt0_df <- median.Vec %>%
-  filter(V0 > 1) %>%
-  mutate(muV = 1 / (lf + eps)) %>%
-  mutate(P_EIP = exp(-muV / etaV)) %>%
-  mutate(proxy_0 = lf * betaV * P_EIP / (KL * rhoL * (lf - 1 / (sigmaV_f * deltaL)))) %>%
-  select(system_ID, Temperature, proxy_0) %>%
-  group_by(system_ID)
-
-Topt0_base_estimates <- Topt0_df %>%
-  group_by(system_ID) %>%
-  # Calculate Topt_0
-  filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>%
-  rename(Topt_0 = Temperature)
-
-# Calculating Topt0 using the "simplified" equation
-ToptRM_df <- median.Vec %>%
-  mutate(muV = 1 / (lf + eps)) %>%
-  mutate(P_EIP = exp(-muV / etaV)) %>%
-  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>%
-  select(system_ID, Temperature, proxy_RM) %>%
-  group_by(system_ID)
-
-ToptRM_base_estimates <- data.Topt %>%
-  group_by(system_ID) %>%
-  filter(is.infinite(sigmaH)) %>%
-  select(system_ID, median) %>%
-  rename(Topt_RM = median) %>%
-  distinct()
-
-Topt_estimates_median <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
-  select(system_ID, Topt_RM, Topt_0) %>%
-  mutate(Topt_diff = Topt_RM - Topt_0) %>%
-  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)
-```
-
-```{r fig-S7_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum and maximum and thermal optimum vary across transmission systems and levels of vertebrate host availability.
-Distributions for the limited biting tolerance case (solid lines) and unlimited biting tolerance case (dashed lines) are shown above and below the vertebrate host population density levels, respectively.
-As vertebrate host population density is increased, the distributions become approximately equal, with the critical thermal minimum and maximum converging to each other at sufficiently high population densities.
-The \\textit{An.
-gambiae} and \\textit{P.
-falciparum} system shows the most drastic differences between the limited and unlimited biting tolerance cases at low vertebrate host population density levels.
-Vertebrate host population density is varied on a $\\log_{10}$ scale.
-'}
-# half-violin plots
-plot.densities_violin_inline <- ggplot() +
-  # CT min
-  geom_violinhalf(
-    data = filter(
-      all.density.df, variable == "Critical thermal minimum",
-      sigmaH == 100
-    ),
-    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
-    lwd = 0.75
-  ) +
-  geom_violinhalf(
-    data = filter(
-      all.density.df, variable == "Critical thermal minimum",
-      sigmaH == Inf
-    ),
-    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
-    lwd = 0.75,
-    flip = TRUE
-  ) +
-  # CT max
-  geom_violinhalf(
-    data = filter(
-      all.density.df, variable == "Critical thermal maximum",
-      sigmaH == 100
-    ),
-    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
-    lwd = 0.75
-  ) +
-  geom_violinhalf(
-    data = filter(
-      all.density.df, variable == "Critical thermal maximum",
-      sigmaH == Inf
-    ),
-    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
-    lwd = 0.75,
-    flip = TRUE
-  ) +
-  # Thermal optima
-  geom_violinhalf(
-    data = filter(
-      all.density.df, variable == "Thermal optimum",
-      sigmaH == 100
-    ),
-    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
-    lwd = 0.75
-  ) +
-  geom_violinhalf(
-    data = filter(
-      all.density.df, variable == "Thermal optimum",
-      sigmaH == Inf
-    ),
-    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
-    lwd = 0.75,
-    flip = TRUE
-  ) +
-  scale_x_discrete(
-    name = "Vertebrate host population density (ind/ha)"
-  ) +
-  scale_y_continuous(
-    name = "Temperature (°C)",
-    expand = c(0, 0)
-  ) +
-  scale_linetype(
-    name = "Biting tolerance\n(bites per host per day)"
-  ) +
-  scale_fill_discrete(
-    name = "",
-    breaks = c("CTmin", "Topt", "CTmax"),
-    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
-  ) +
-  facet_wrap(~system_label, labeller = labeller(), scales = "free_x") +
-  theme_minimal_grid(10) +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  ) +
-  coord_flip()
-shift_legend(plot.densities_violin_inline)
-```
-
-```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$.
+```{r fig-7_explain_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
 Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
@@
 Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
-Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
-'}
+Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.'}
+
 KH_vals <- c(1, 100)
+sigmaH_val <- 10
 
 data.dR0dT <- data.dR0dvar %>%
-  filter((KH %in% KH_vals & sigmaH == 10) | (KH == 100 & is.infinite(sigmaH)))
+  filter((KH %in% KH_vals & sigmaH == sigmaH_val) | (KH == 100 & is.infinite(sigmaH)))
 
 temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-  filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) %>%
+  filter(KH %in% KH_vals & sigmaH %in% c(sigmaH_val, Inf)) %>%
   filter(!is.na(median_R0), median_R0 > eps) %>%
@@
 
-# NB: in order to produce an R0 TPC, "overall" derivative should go from positive to negative
-plot.dR0dk <- dR0dk.df %>%
+comp_dR0dk.df <- dR0dk.df %>%
+  # filter(sigmaH == 10) %>% 
+  filter(focal_var != "Overall") %>% 
+  group_by(system_ID, Temperature, sigmaH, KH) %>% 
+  mutate(abs_median = abs(median),
+         total_sens = sum(abs_median),
+         prop_sens = abs_median / total_sens) %>% 
+  arrange(system_label, Temperature, KH, sigmaH, focal_var)
+
+plot.comp_dR0dk <- comp_dR0dk.df %>%
+  filter(is.finite(sigmaH)) %>% 
   # filter(focal_var %in% c("Overall")) %>%
   # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = norm_median, color = focal_var, 
-             # linetype = (as.factor(sign_median))
+  ggplot(aes(x = Temperature, y = prop_sens, fill = focal_var, color = focal_var,
   )) +
-  geom_line(lwd = 0.5) +
+  # geom_area() +
+  geom_line(lwd = 1) +
   geom_hline(yintercept = 0, lwd = 0.25) +
@@
     name = "Focal trait:",
-    values = rev(c(c4a("misc.okabe", 7), "black"))
+    values = rev(c4a("misc.okabe", 7))
+  ) +
+  scale_fill_manual(
+    name = "Focal trait:",
+    values = rev(c4a("misc.okabe", 7))
   ) +
@@
   scale_y_continuous(
-    name = unname(TeX("Normalized local sensitivity of $\\,R_0$ to temperature")),
-    # limits = c(-1, 1),
-    # limits = 10^c(-4, 4),
-    # breaks = 10^(seq(-4, 4)),
-    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
-    # trans = "log10",
+    name = unname(TeX("Contributions to overall local sensitivity of $\\,R_0$")),
     expand = c(0, 0)
   ) +
-  # scale_linetype_manual(
-  #   name = "Sign of sensitivity:",
-  #   values = c(1, 3),
-  #   breaks = c(1, -1),
-  #   labels = c("Positive", "Negative")
-  # ) +
   facet_rep_grid(
-    rows = vars(KH, sigmaH),
+    rows = vars(sigmaH, KH),
     cols = vars(system_label),
@@
 
-plot.dR0dk
-```
-
-```{r fig-7_explain_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
-Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
-Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
-Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
-Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.'}
-
-comp_dR0dk.df <- dR0dk.df %>%
-  # filter(sigmaH == 10) %>% 
-  filter(focal_var != "Overall") %>% 
-  group_by(system_ID, Temperature, sigmaH, KH) %>% 
-  mutate(abs_median = abs(median),
-         total_sens = sum(abs_median),
-         prop_sens = abs_median / total_sens) %>% 
-  arrange(system_label, Temperature, KH, sigmaH, focal_var)
-
-plot.comp_dR0dk <- comp_dR0dk.df %>%
-  # filter(focal_var %in% c("Overall")) %>%
-  # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = prop_sens, fill = focal_var, color = focal_var,
-             # linetype = (as.factor(sign_median))
+# plot.comp_dR0dk
+
+compzoom_dR0dk.df <- comp_dR0dk.df %>%
+  filter(sigmaH == sigmaH_val) %>% 
+  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
+  pivot_wider(names_from = KH, values_from = prop_sens) %>%
+  mutate(abs_comp = `100` - `1`)
+
+plot.compzoom_dR0dk <- compzoom_dR0dk.df %>% 
+  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var,
   )) +
-  # geom_area() +
   geom_line(lwd = 1) +
@@
   scale_y_continuous(
-    name = unname(TeX("Contributions to overall local sensitivity of $\\,R_0$")),
-    # limits = c(-100, 100),
-    # limits = c(-0.2, 0.1),
-    # limits = 10^c(-4, 4),
-    # breaks = 10^(seq(-4, 4)),
-    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
-    # trans = "log10",
+    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 100$ ")),
     expand = c(0, 0)
   ) +
-  # scale_linetype_manual(
-  #   name = "Sign of sensitivity:",
-  #   values = c(1, 3),
-  #   breaks = c(1, -1),
-  #   labels = c("Positive", "Negative")
-  # ) +
   facet_rep_grid(
-    rows = vars(sigmaH, KH),
+    # rows = vars(sigmaH),
     cols = vars(system_label),
@@
       system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-      KH = as_labeller(appender_KH, default = label_parsed)
+      # sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      # KH = as_labeller(appender_KH, default = label_parsed)
     ),
@@
 
-plot.comp_dR0dk
+plot.compzoom_dR0dk
 ```
-
-``` {r}
-# 1. change in non-normalized sensitivity as KH: 1 to 100
-compzoom_dR0dk.df_1 <- dR0dk.df %>%
-  filter(sigmaH == 10, focal_var != "Overall") %>% 
-  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
-  pivot_wider(names_from = KH, values_from = median) %>%
-  mutate(abs_comp = `1` - `100`)
-
-# 2. Absolute change in non-normalized sensitivity as KH: 1 to 100
-compzoom_dR0dk.df_2 <- dR0dk.df %>%
-  filter(sigmaH == 10, focal_var != "Overall") %>% 
-  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
-  pivot_wider(names_from = KH, values_from = median) %>%
-  mutate(abs_comp = abs(`1` - `100`))
-
-# 3. Proportional change in non-normalized sensitivity as KH: 1 to 100
-compzoom_dR0dk.df_3 <- dR0dk.df %>%
-  filter(sigmaH == 10, focal_var != "Overall") %>% 
-  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
-  pivot_wider(names_from = KH, values_from = median) %>%
-  mutate(abs_comp = (`1` - `100`)/(`1`+1))
-
-# 4. Proportional change in non-normalized sensitivity as KH: 1 to 100
-compzoom_dR0dk.df_4 <- dR0dk.df %>%
-  filter(sigmaH == 10, focal_var != "Overall") %>% 
-  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, median) %>%
-  pivot_wider(names_from = KH, values_from = median) %>%
-  mutate(temp_comp = `1` - `100`) %>% 
-  group_by(system_ID, Temperature) %>% 
-  mutate(total_comp = sum(temp_comp),
-         abs_comp = temp_comp / sum(temp_comp))
-
-compzoom_dR0dk.df <- comp_dR0dk.df %>%
-  filter(sigmaH == 10) %>% 
-  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
-  pivot_wider(names_from = KH, values_from = prop_sens) %>%
-  mutate(abs_comp = abs(`1`) - abs(`100`))
-
-plot.compzoom_dR0dk <- compzoom_dR0dk.df %>% 
-  # filter(focal_var %in% c("Parasite development rate", "Adult mortality rate", "Biting frequency")) %>%
+# Supplementary Figures
+
+```{r fig-S0_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model.
+Curves are shown in color for each of the five systems we considered.
+Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive).
+Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d).
+Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7.
+The \\textit{Aedes aegypti} and DENV and \\textit{Ae.
+aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al.
+(2018)).
+All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020.
+Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions.
+A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
+## Set up plot dataframe
+MosqThermTraits_df <- median.Vec %>% 
+  dplyr::select(Temperature, system_ID, `Mosquito population density` = V0)  %>%
+  group_by(Temperature, system_ID)
+
+MosqThermTraits_plot <- MosqThermTraits_df %>%
+  # Set up plotting variables and theme
+  # x = Temperature, y = trait value
+  ggplot(mapping = aes(x = Temperature, y = `Mosquito population density`, group = system_ID)) +
+  # Plot trait values:
+  geom_line(aes(colour = system_ID), size = 1) +
+  # x-axis:
+  scale_x_continuous(
+    name = "Temperature (°C)",
+    expand = c(0, 0),
+    limits = c(10, 40),
+    breaks = seq(10, 40, 2)
+  ) +
+  # y-axis:
+  scale_y_continuous("Equilibrium adult mosquito population density", 
+                     expand = c(0.05, 0)) +
+  # color:
+  scale_color_manual(
+    name = "System:",
+    values = met.brewer("Egypt", 5, direction = -1),
+    labels = function(x) {
+      case_when(
+        x == "Aedes aegypti / DENV" ~ "*Aedes aegypti* and DENV",
+        x == "Aedes aegypti / ZIKV" ~ "*Ae. aegypti* and ZIKV",
+        x == "Aedes albopictus / DENV" ~ "*Aedes albopictus* and DENV",
+        x == "Anopheles gambiae / Plasmodium falciparum" ~ "*Anopheles gambiae* and *Plasmodium falciparum*",
+        x == "Culex quinquefasciatus / WNV" ~ "*Culex quinquefasciatus* and WNV"
+      )
+    }
+  )  +
+  # legend:
+  guides(color = guide_legend(override.aes = list(size = 4))) +
+  # theme options:
+  theme_minimal(10) +
+  theme(
+    legend.margin = margin(),
+    legend.text = ggtext::element_markdown(),
+    legend.direction = "vertical",
+    legend.justification = "center",
+    strip.text = element_text(
+      face = "bold",
+      hjust = 0
+    )
+  )
+
+MosqThermTraits_plot
+```
+
+```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
+The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
+and \\textit{P.
+falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
+Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
+Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+All remaining parameters are given in Table 1 and Figure 3.'}
+# Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
+
+# x = vertebrate host biting tolerance (needs to vary from "zero" to "infinity")
+# y = Temperature
+# color = R0
+# curves:
+#   R0 = 1 contour (black curve)
+#   Topt (red curve)
+
+# Facets:
+# Rows = levels of vertebrate host population density
+# Columns = two MBPT systems
+# Total = 6 plots
+
+## Set up plot data frame
+# We re-create the output data frame so that we can vary sigmaH correctly.
+# We also drop the resolution of KH down to just three values
+# Need to update functions so that sigmaH == Inf <~> Model == "Ross-Macdonald"
+
+## Configure data frame for plotting
+R0_df <- data.R0 %>%
+  select(system_ID, system_label, Temperature, sigmaH, KH, median, mean) %>%
+  rename(R0 = mean) %>%
+  # Consider only 3 values of KH (on a log10-scale)
+  filter(KH %in% c(.1, 1, 10)) %>%
+  # Choose a limited range of sigmaH values
+  filter(sigmaH < 10^2.275 | is.infinite(sigmaH)) %>%
+  # Group by plotting variables
+  group_by(system_ID, KH, sigmaH) %>%
+  # Calculate Topt (which.max requires grouping)
+  mutate(Topt = `Temperature`[which.max(R0)]) %>%
+  as_tibble() %>%
+  arrange(system_ID, sigmaH, Temperature)
+
+## Add a "point at infinity" for sigmaH
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^2.75
+
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^2.4
+
+R0_df <- inf_skew_func(R0_df, infinite_skew, infinite_divide, 8)
+
+Topt_for_R0_df <- data.Topt %>%
+  # Arrange along the plotting variables
+  arrange(system_ID, sigmaH, KH, median) %>%
+  mutate(sigmaH_proxy = sigmaH)
+Topt_for_R0_df <- inf_skew_func(Topt_for_R0_df, infinite_skew, infinite_divide, 8)
+
+## PLOTTING ##
+
+## Options
+# Define sigmaH tick breaks and labels
+sigmaH_breaks_heatmap <- c(10^c(seq(-1, 2, by = 1)), infinite_divide, infinite_skew)
+sigmaH_labels_heatmap <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+# Labels for facet rows
+R0_df$KH <- factor(R0_df$KH, levels = c(.1, 1, 10))
+mylabels <- as_labeller(c(
+  `0.1` = "0.1 vertebrate hosts / ha",
+  `1` = "1 vertebrate host / ha",
+  `10` = "10 vertebrate hosts / ha"
+))
+
+R0_heatmap_labels <- as_labeller(c(
+  "(a) *Ae. aegypti* and DENV" = "(a) *Ae. aegypti*  \nand  DENV",
+  "(b) *Ae. aegypti* and ZIKV" = "(b) *Ae. aegypti*  \nand  ZIKV",
+  "(c&#41; *Ae. albopictus* and DENV" = "(c&#41; *Ae. albopictus*  \nand  DENV",
+  "(d) *An. gambiae* and *P. falciparum*" = "(d) *An. gambiae*  \nand  *P. falciparum*",
+  "(e) *Cx. quinquefasciatus* and WNV" = "(e) *Cx. quinquefasciatus*  \nand  WNV"
+))
+
+# Breaks used to decide fill for the heat map
+fill_breaks <- c(1, seq(5, 20, by = 5), Inf)
+
+# Define colors for heat map so that values of R0>1 go from yellow to red
+my.cols <- rev(c(rev(brewer.pal(length(fill_breaks) - 1, "YlOrRd"))))
+
+## PLOT ##
+R0_plot <- R0_df %>%
+  ggplot(mapping = aes(x = sigmaH_proxy, y = Temperature)) +
+  # Mosquito thermal tolerance range lines
+  geom_hline(
+    data = MosqThermRange_df,
+    aes(yintercept = CTmin_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  geom_hline(
+    data = MosqThermRange_df,
+    aes(yintercept = CTmax_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  # R0 contours for FINITE sigmaH:
+  geom_contour_filled(
+    data = filter(R0_df, sigmaH_proxy < infinite_divide**0.98),
+    mapping = aes(z = R0),
+    breaks = fill_breaks
+  ) +
+  # R0 contours for INFINITE sigmaH:
+  geom_contour_filled(
+    data = filter(R0_df, sigmaH_proxy > infinite_divide**1.02),
+    mapping = aes(z = R0),
+    breaks = fill_breaks
+  ) +
+  # R0 = 1 contour:
+  geom_contour(aes(colour = "R0=1", z = R0), breaks = c(1), size = 1) +
+  # Topt curve:
+  geom_path(
+    data = filter(Topt_for_R0_df, KH %in% c(.1, 1, 10)) %>% arrange(sigmaH_proxy),
+    mapping = aes(
+      x = sigmaH_proxy,
+      y = median,
+      colour = "Topt"
+    ),
+    lwd = 1,
+    linetype = 1
+  ) +
+  # white lines breaking up finite/infinite sigmaH values
+  geom_vline(
+    aes(xintercept = 0.85 * infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = 1.2 * infinite_divide),
+    colour = "white",
+    lwd = .8,
+    show.legend = FALSE
+  ) +
+  # x-axis:
+  scale_x_log10(
+    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
+    breaks = sigmaH_breaks_heatmap,
+    labels = sigmaH_labels_heatmap,
+    expand = c(0, 0)
+  ) +
+  # y-axis:
+  scale_y_continuous(
+    name = expression("Temperature "(degree * C)),
+    expand = c(0, 0),
+    limits = c(16, 35),
+    breaks = seq(10, 36, by = 2)
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "",
+    labels = c(
+      "R0=1" = unname(TeX("$R_0=1$")),
+      "Topt" = "Transmission\nthermal\noptimum",
+      "VTTR" = "Mosquito\npopulation\nthermal\nniche"
+    ),
+    values = c("black", "purple", "grey"),
+    guide = guide_legend(
+      order = 1,
+      keyheight = unit(2, "cm"),
+      override.aes = list(size = 6)
+    )
+  ) +
+  # fill:
+  scale_fill_manual(
+    name = TeX("$R_0$"),
+    values = my.cols,
+    guide = guide_colorsteps(
+      order = 2,
+      breaks = fill_breaks,
+      barheight = unit(8, "cm")
+    )
+  ) +
+  # faceting:
+  facet_grid(
+    rows = vars(KH),
+    cols = vars(system_label),
+    labeller = labeller(
+      .rows = mylabels,
+      .cols = R0_heatmap_labels
+    ),
+    # repeat.tick.labels = "left"
+  ) +
+  # theme options:
+  theme_minimal_hgrid(10) +
+  theme(
+    axis.line = element_line(),
+    legend.text = element_text(size = 10),
+    legend.text.align = 0,
+    strip.text.y = ggtext::element_markdown(
+      size = 7,
+      hjust = 0.5
+    ),
+    strip.text.x = ggtext::element_markdown(
+      size = 7,
+      hjust = 0
+    ),
+    panel.spacing = unit(2, "pt")
+  )
+
+# Plot it
+R0_plot
+```
+
+```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
+The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
+and \\textit{P.
+falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
+Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
+Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+All remaining parameters are given in Table 1 and Figure 3.'}
+Topt_df <- data.Topt %>%
+  filter(KH < 10^4 + 1) %>%
+  pivot_wider(
+    id_cols = c("system_label", "Model", "sigmaH", "KH"),
+    names_from = variable,
+    values_from = c("mean", "median", "lowHCI", "highHCI")
+  ) %>%
+  rename(
+    mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
+    highHCI = highHCI_Topt
+  ) %>%
+  # Arrange along the plotting variables
+  arrange(system_label, KH, median, sigmaH) %>%
+  ungroup()
+
+# PLOTTING
+Topt_plot <- Topt_df %>%
+  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
+  ## Set up plot ##
+  # color = sigmaH
+  ggplot(aes(x = KH, colour = as.factor(sigmaH))) +
+  # Topt curves:
+  geom_path(aes(y = median), lwd = 1) +
+  # x-axis: log10 scale, no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    breaks = c(10^c(seq(-1, 4, by = 1))),
+    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  # y-axis
+  scale_y_continuous(
+    name = expression("Thermal optimum "(degree * C)),
+    expand = c(0, 0),
+    limits = c(21, 30.5),
+    breaks = seq(21, 32, by = 1)
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "Vertebrate host biting tolerance\n(bites per host per day)",
+    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
+    breaks = c(1, 10, 100, Inf),
+    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
+  ) +
+  scale_fill_manual(
+    name = "Vertebrate host biting tolerance\n(bites per host per day)",
+    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
+    breaks = c(1, 10, 100, Inf),
+    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
+  ) +
+  # faceting:
+  facet_wrap(~system_label, nrow = 2, labeller = labeller()) +
+  # theme options:
+  theme_minimal(10) +
+  guides(color = guide_legend(override.aes = list(size = 4))) +
+  theme(
+    legend.position = "bottom",
+    legend.margin = margin(),
+    legend.direction = "vertical",
+    legend.title = element_text(size = 10),
+    legend.text = element_text(
+      size = 10,
+      hjust = 0
+    ),
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(Topt_plot)
+```
+
+```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} The thermal optima predicted by the model can be substantially different at low levels of biting tolerance.
+At low host population densities, there may be warmer (a, b, c, e) or cooler (d) thermal optima when biting tolerance is low compared to when it is high.
+Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
+Vertebrate host biting tolerance is varied on a $\\log_{10}$ scale with a break to indicate values of $\\mathcal{R}_0$ when biting tolerance is unlimited.
+'}
+# x-axis = vertebrate host biting tolerance
+# y-axis = thermal optimum
+# color = vertebrate host population density
+
+infinite_skew <- 10^3.7
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^3.35 # 10^log10(max_sigmaH*1)
+
+Topt_df <- data.Topt %>%
+  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH),
+                               sigmaH,
+                               infinite_skew
+  ))
+Topt_df <- inf_skew_func(Topt_df, infinite_skew, infinite_divide, 6)
+
+sigmaH_breaks <- c(10^c(seq(-1, 3, by = 1)), 1.15 * infinite_divide, infinite_skew)
+sigmaH_labels <- c(TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$")), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+Topt_plot <- Topt_df %>%
+  # Choose appropriate pop. dens. values and group
+  filter(KH %in% 10^seq(0, 3)) %>%
+  arrange(system_label, KH, sigmaH, median) %>%
+  ## Set up plot ##
+  # color = sigmaH
+  ggplot(aes(x = sigmaH_proxy, colour = as.factor(KH))) +
+  # Topt curves:
+  geom_path(aes(y = median), lwd = 1) +
+  # white lines breaking up finite/infinite sigmaH values:
+  geom_vline(
+    aes(xintercept = 1.05 * infinite_divide),
+    colour = "white",
+    lwd = .9,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = 1.15 * infinite_divide),
+    colour = "white",
+    lwd = .9,
+    show.legend = FALSE
+  ) +
+  geom_vline(
+    aes(xintercept = 1.25 * infinite_divide),
+    colour = "white",
+    lwd = .9,
+    show.legend = FALSE
+  ) +
+  # x-axis: Use a log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
+    expand = c(0, 0),
+    # limits = c(0.5, 150),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels
+  ) +
+  # y-axis
+  scale_y_continuous(
+    name = expression("Thermal optimum "(degree * C)),
+    expand = c(0, 0), # c(0.05, 0.05),
+    limits = c(21, 30), # mean: 21-31, median: 21-32
+    breaks = seq(21, 32, by = 1)
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "Vertebrate host population\ndensity (ind/ha)",
+    values = met.brewer("Hokusai3", 4)
+  ) +
+  scale_fill_manual(
+    name = "Vertebrate host population\ndensity (ind/ha)",
+    values = met.brewer("Hokusai3", 4)
+  ) +
+  # faceting:
+  facet_wrap(~system_label,
+             scales = "free",
+             nrow = 2,
+             labeller = labeller()
+  ) +
+  # theme options:
+  theme_minimal(10) +
+  guides(color = guide_legend(override.aes = list(size = 4))) +
+  theme(
+    legend.position = "bottom",
+    legend.margin = margin(),
+    legend.direction = "vertical",
+    legend.title = element_text(size = 10),
+    legend.text = element_text(
+      size = 10,
+      hjust = 0
+    ),
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(Topt_plot)
+```
+
+```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} The critical thermal minimum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
+Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
+In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text).
+Shown here are the median values of the critical thermal minimum with respect to mosquito trait TPC hyperparameter posterior distributions.
+Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
+'}
+#   x    = biting tolerance (with a point at infinity)
+#   y    = vertebrate host population density
+# colour = parasite critical thermal minimum (CTmin)
+# Facets = systems
+
+# add many proxy sigmaH points at infinity to make the values easier to see there
+max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^2.35
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^2.7
+
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+CTmin_df <- data.CT %>%
+  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
+  pivot_wider(names_from = variable, values_from = median) %>% 
+  # If CTwidth is essentially zero, set CTmin to Inf indicating R0 < 1
+  mutate(CTmin = if_else(CTwidth < eps, Inf, CTmin)) %>%
+  mutate(sigmaH_proxy = sigmaH) %>%
+  # Arrange along the plotting variables
+  arrange(system_ID, KH, sigmaH_proxy, CTmin) %>%
+  ungroup() %>%
+  # Assign a value for cases where R0<1 for all temperatures
+  mutate(CTmin = ifelse(is.finite(CTmin), CTmin, 100))
+
+CTmin_df <- inf_skew_func(CTmin_df, infinite_skew, infinite_divide, 8)
+
+maxCTmin <- ceiling(max(filter(CTmin_df, CTmin<100)$CTmin))
+
+CTmin_breaks <- c(seq(14, 35, by = 2), 101)
+
+CTmin_heat_plots <- CTmin_df %>%
+  ## Set up plot ##
+  # x = biting tolerance (with a point at infinity),
+  # y = vertebrate host population density,
+  # color = width of parasite thermal median_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmin)) +
+  # CTmin for FINITE sigmaH:
+  geom_contour_filled(
+    data = filter(
+      CTmin_df,
+      sigmaH_proxy < 10^2.2
+    ),
+    breaks = CTmin_breaks
+  ) +
+  # CTmin for INFINITE sigmaH:
+  geom_contour_filled(
+    data = filter(
+      CTmin_df,
+      sigmaH_proxy > 10^2.4,
+      sigmaH_proxy < infinite_divide
+    ),
+    breaks = CTmin_breaks
+  ) +
+  # x-axis: log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E4),
+    breaks = 10^seq(-1, 4, 1),
+    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  # y-axis: log10-scale y axis, with no buffer space
+  scale_y_log10(
+    name = TeX("Biting tolerance (bites per host per day)"),
+    expand = c(0, 0),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels
+  ) +
+  # fill:
+  scale_fill_manual(
+    name = "Critical thermal minimum (°C)",
+    values = c(viridis(9), "grey", "grey"),
+    labels = ~ ifelse(.x < maxCTmin, .x, "n/a")
+  ) +
+  # faceting:
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
+  # legend:
+  guides(fill = guide_coloursteps(
+    title.position = "top",
+    title.hjust = 0.5,
+    barwidth = 12,
+    show.limits = TRUE
+  )) +
+  # theme options:
+  theme_minimal(10) +
+  theme(
+    legend.box = "horizontal",
+    legend.position = "bottom",
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.direction = "horizontal",
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(CTmin_heat_plots)
+```
+
+```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} The critical thermal maximum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
+Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
+In the region where vertebrate host population density and biting tolerance are both less than 10, critical thermal minima and maxima are very similar (see Figure 6 in the main text).
+Shown here are the median values of the critical thermal maximum with respect to mosquito trait TPC hyperparameter posterior distributions.
+Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
+'}
+#   x    = biting tolerance (with a point at infinity)
+#   y    = vertebrate host population density
+# colour = parasite critical thermal maximum (CTmax)
+# Facets = systems
+
+# add many proxy sigmaH points at infinity to make the values easier to see there
+max_sigmaH <- max(filter(data.CT, is.finite(sigmaH))$sigmaH)
+# Value of sigmaH to replace 'Inf' with for plotting
+infinite_skew <- 10^2.35
+# Used to create a gap dividing finite and infinite sigmaH
+infinite_divide <- 10^2.7
+
+# Define sigmaH tick breaks and labels
+sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
+sigmaH_labels <- c(paste(c(10^c(seq(-1, 2, by = 1)))), TeX("$\\ldots$"), TeX("$\\infty$"))
+
+CTmax_df <- data.CT %>%
+  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
+  pivot_wider(names_from = variable, values_from = median) %>% 
+  # If CTwidth is essentially zero, set CTmax to -Inf indicating R0 < 1
+  mutate(CTmax = if_else(CTwidth < eps, Inf, CTmax)) %>%
+  mutate(sigmaH_proxy = sigmaH) %>%
+  # Arrange along the plotting variables
+  arrange(system_ID, KH, sigmaH_proxy, CTmax) %>%
+  ungroup() %>%
+  # Assign a value for cases where R0<1 for all temperatures
+  mutate(CTmax = ifelse(is.finite(CTmax), CTmax, -100))
+
+CTmax_df <- inf_skew_func(CTmax_df, infinite_skew, infinite_divide, 8)
+
+minCTmax <- floor(min(filter(CTmax_df, CTmax>0)$CTmax))
+
+CTmax_breaks <- c(-101, seq(21, 35, by = 2))
+
+CTmax_heat_plots <- CTmax_df %>%
+  ## Set up plot ##
+  # x = biting tolerance (with a point at infinity),
+  # y = vertebrate host population density,
+  # color = width of parasite thermal median_CTwidth
+  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmax)) +
+  # CTmin for FINITE sigmaH:
+  geom_contour_filled(
+    data = filter(
+      CTmax_df,
+      sigmaH_proxy < 10^2.2
+    ),
+    breaks = CTmax_breaks
+  ) +
+  # CTmin for INFINITE sigmaH:
+  geom_contour_filled(
+    data = filter(
+      CTmax_df,
+      sigmaH_proxy > 10^2.4,
+      sigmaH_proxy < infinite_divide
+    ),
+    breaks = CTmax_breaks
+  ) +
+  # x-axis: log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(0.05, 1E4),
+    breaks = 10^seq(-1, 4, 1),
+    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  # y-axis: log10-scale y axis, with no buffer space
+  scale_y_log10(
+    name = TeX("Biting tolerance (bites per host per day)"),
+    expand = c(0, 0),
+    breaks = sigmaH_breaks,
+    labels = sigmaH_labels
+  ) +
+  # fill:
+  scale_fill_manual(
+    name = "Critical thermal maximum (°C)",
+    values = c("grey", viridis(9)),
+    labels = ~ ifelse(.x < minCTmax - 1, "n/a", .x)
+  ) +
+  # faceting:
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
+  # legend:
+  guides(fill = guide_coloursteps(
+    title.position = "top",
+    title.hjust = 0.5,
+    barwidth = 12,
+    show.limits = TRUE
+  )) +
+  # theme options:
+  theme_minimal(10) +
+  theme(
+    legend.box = "horizontal",
+    legend.position = "bottom",
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    legend.direction = "horizontal",
+    legend.justification = "left",
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  )
+
+# Plot
+shift_legend(CTmax_heat_plots)
+```
+
+```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} The critical thermal minimum ($\\textrm{CT}_{\\min}$, blue curves) and maximum ($\\textrm{CT}_{\\max}$, red curves) for parasite population persistence depend on vertebrate host availability, even when vertebrate hosts tolerate any level of mosquito biting (dotted curves).
+Transmission is sustained ($\\mathcal{R}_0$>1) in the regions enclosed by the red and blue curves.
+$\\textrm{CT}_{\\min}$ is a convex function of vertebrate host population density while $\\textrm{CT}_{\\max}$ is concave.
+The points where the red and blue curves touch indicate thresholds of vertebrate host population density beyond which parasite population persistence is no longer possible at any temperature (i.e.
+$\\mathcal{R}_0$(T)<1) (see Figure 6 in the main text).
+Shown here are the median values of the critical thermal minimum, maximum, and mosquito thermal tolerance niche with respect to mosquito trait TPC hyperparameter posterior distributions.
+Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
+All remaining parameters are given in Table 1 and Figure 2.'}
+# x-axis = vertebrate host population density
+# y-axis = Temperature
+# linetype = biting tolerance
+# colour = CT_min (blue), CT_max (red)
+
+CTRange_df <- data.CT %>%
+  # Arrange along the plotting variables
+  select(system_label, sigmaH, KH, variable, value = median) %>%
+  # Choose a few sigmaH values to plot, including Inf
+  filter(sigmaH %in% c(1, 10, 100, Inf)) %>%
+  filter(KH %in% unique(KH)[seq(1, length(unique(KH)), length.out = 101)]) %>%
+  pivot_wider(
+    id_cols = c("system_label", "sigmaH", "KH"),
+    names_from = variable, values_from = value
+  ) %>%
+  group_by(system_label, KH, sigmaH) %>%
+  mutate(CTwidth = max(CTmax - CTmin, 0)) %>%
+  filter(CTwidth > 0.05) %>%
+  # Arrange along the plotting variables
+  arrange(system_label, KH, sigmaH, CTmax, CTmin) %>%
+  ungroup() %>%
+  melt(id = c("system_label", "KH", "sigmaH")) %>%
+  arrange(KH, sigmaH)
+
+CTRange_plots <- CTRange_df %>%
+  ## Set up plot ##
+  # x-axis = population density, y-axis = temperature,
+  # color = thermal extrema, linetype = sigmaH
+  ggplot(
+    aes(x = KH, y = value, linetype = as.factor(sigmaH), color = variable)
+  ) +
+  # Mosquito thermal tolerance range lines
+  geom_hline(
+    data = MosqThermRange_df,
+    aes(yintercept = CTmin_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  geom_hline(
+    data = MosqThermRange_df,
+    aes(yintercept = CTmax_V0, colour = "VTTR"),
+    lwd = 1.275
+  ) +
+  # Curves showing CTmin and CTmax
+  geom_line(
+    data = filter(CTRange_df, variable == "CTmin"),
+    lwd = 1
+  ) +
+  geom_line(
+    data = filter(CTRange_df, variable == "CTmax"),
+    lwd = 1
+  ) +
+  # x-axis: log10-scale with no buffer space
+  scale_x_log10(
+    name = TeX("Vertebrate host population density (ind/ha)"),
+    expand = c(0, 0),
+    limits = c(1E-2, 1E5),
+    breaks = 10^seq(-1, 4),
+    labels = TeX(c("$0.1$", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"))
+  ) +
+  # y-axis: small buffer space
+  scale_y_continuous(
+    name = expression("Temperature "(degree * C)),
+    expand = c(0.05, 0.05),
+    limits = c(min(MosqThermRange_df$CTmin_V0), max(MosqThermRange_df$CTmax_V0)),
+    breaks = seq(floor(range(CTRange_df$value, na.rm = TRUE)[1]),
+                 floor(range(CTRange_df$value, na.rm = TRUE)[2]),
+                 by = 2
+    )
+  ) +
+  # linetype:
+  scale_linetype_manual(
+    name = "Vertebrate host biting tolerance\n(bites per host per day)",
+    values = c("solid", "dashed", "longdash", "dotted"),
+    breaks = c(1, 10, 100, Inf),
+    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
+  ) +
+  # color:
+  scale_colour_manual(
+    name = "Thermal extrema",
+    breaks = c("CTmax", "CTmin", "VTTR"),
+    labels = c("Critical maximum", "Critical minimum", "Mosquito population\nthermal niche"),
+    values = c("red", "blue", "grey"),
+    guide = guide_legend(keyheight = unit(40, "cm"))
+  ) +
+  # faceting:
+  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
+  # legend:
+  guides(
+    color = guide_legend(override.aes = list(size = 4), order = 1),
+    linetype = guide_legend(keywidth = 4, order = 2),
+  ) +
+  # theme options:
+  theme_minimal_hgrid(10) +
+  theme(
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 10,
+      hjust = 0
+    )
+  )
+
+# Plot
+shift_legend(CTRange_plots)
+```
+
+```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}
+# Estimating the difference between Topt and Topt_RM numerically using our previous data
+Toptdiff_CCH <- data.Topt %>%
+  ungroup() %>%
+  select(system_ID, sigmaH, KH, median) %>%
+  rename(Topt = median) %>%
+  filter(is.finite(sigmaH)) %>%
+  distinct()
+
+Toptdiff_RM <- data.Topt %>%
+  ungroup() %>%
+  filter(is.infinite(sigmaH)) %>%
+  select(system_ID, KH, median) %>%
+  rename(Topt_RM = median) %>%
+  distinct()
+
+Toptdiff_df <- left_join(Toptdiff_CCH, Toptdiff_RM) %>%
+  mutate(Toptdiff = Topt_RM - Topt) %>%
+  mutate(absToptdiff = abs(Toptdiff)) %>%
+  mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>%
+  mutate(sigmaHKH = sigmaH * KH) %>%
+  group_by(system_ID) %>%
+  filter(absToptdiff == max(absToptdiff)) %>%
+  select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>%
+  distinct()
+
+# Calculating Topt0 using the "simplified" equation
+Topt0_df <- median.Vec %>%
+  filter(V0 > 1) %>%
+  mutate(muV = 1 / (lf + eps)) %>%
+  mutate(P_EIP = exp(-muV / etaV)) %>%
+  mutate(proxy_0 = lf * betaV * P_EIP / (KL * rhoL * (lf - 1 / (sigmaV_f * deltaL)))) %>%
+  select(system_ID, Temperature, proxy_0) %>%
+  group_by(system_ID)
+
+Topt0_base_estimates <- Topt0_df %>%
+  group_by(system_ID) %>%
+  # Calculate Topt_0
+  filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>%
+  rename(Topt_0 = Temperature)
+
+# Calculating Topt0 using the "simplified" equation
+ToptRM_df <- median.Vec %>%
+  mutate(muV = 1 / (lf + eps)) %>%
+  mutate(P_EIP = exp(-muV / etaV)) %>%
+  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>%
+  select(system_ID, Temperature, proxy_RM) %>%
+  group_by(system_ID)
+
+ToptRM_base_estimates <- data.Topt %>%
+  group_by(system_ID) %>%
+  filter(is.infinite(sigmaH)) %>%
+  select(system_ID, median) %>%
+  rename(Topt_RM = median) %>%
+  distinct()
+
+Topt_estimates_median <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
+  select(system_ID, Topt_RM, Topt_0) %>%
+  mutate(Topt_diff = Topt_RM - Topt_0) %>%
+  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM) %>% 
+  arrange(system_ID)
+```
+
+```{r fig-S7_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum and maximum and thermal optimum vary across transmission systems and levels of vertebrate host availability.
+Distributions for the limited biting tolerance case (solid lines) and unlimited biting tolerance case (dashed lines) are shown above and below the vertebrate host population density levels, respectively.
+As vertebrate host population density is increased, the distributions become approximately equal, with the critical thermal minimum and maximum converging to each other at sufficiently high population densities.
+The \\textit{An.
+gambiae} and \\textit{P.
+falciparum} system shows the most drastic differences between the limited and unlimited biting tolerance cases at low vertebrate host population density levels.
+Vertebrate host population density is varied on a $\\log_{10}$ scale.
+'}
+# half-violin plots
+plot.densities_violin_inline <- ggplot() +
+  # CT min
+  geom_violinhalf(
+    data = filter(
+      all.density.df, variable == "Critical thermal minimum",
+      sigmaH == 100
+    ),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
+    lwd = 0.75
+  ) +
+  geom_violinhalf(
+    data = filter(
+      all.density.df, variable == "Critical thermal minimum",
+      sigmaH == Inf
+    ),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
+    lwd = 0.75,
+    flip = TRUE
+  ) +
+  # CT max
+  geom_violinhalf(
+    data = filter(
+      all.density.df, variable == "Critical thermal maximum",
+      sigmaH == 100
+    ),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
+    lwd = 0.75
+  ) +
+  geom_violinhalf(
+    data = filter(
+      all.density.df, variable == "Critical thermal maximum",
+      sigmaH == Inf
+    ),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
+    lwd = 0.75,
+    flip = TRUE
+  ) +
+  # Thermal optima
+  geom_violinhalf(
+    data = filter(
+      all.density.df, variable == "Thermal optimum",
+      sigmaH == 100
+    ),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
+    lwd = 0.75
+  ) +
+  geom_violinhalf(
+    data = filter(
+      all.density.df, variable == "Thermal optimum",
+      sigmaH == Inf
+    ),
+    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
+    lwd = 0.75,
+    flip = TRUE
+  ) +
+  scale_x_discrete(
+    name = "Vertebrate host population density (ind/ha)"
+  ) +
+  scale_y_continuous(
+    name = "Temperature (°C)",
+    expand = c(0, 0)
+  ) +
+  scale_linetype(
+    name = "Biting tolerance\n(bites per host per day)"
+  ) +
+  scale_fill_discrete(
+    name = "",
+    breaks = c("CTmin", "Topt", "CTmax"),
+    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
+  ) +
+  facet_wrap(~system_label, labeller = labeller(), scales = "free_x") +
+  theme_minimal_grid(10) +
+  theme(
+    legend.margin = margin(0, 0, 0, 0),
+    legend.title = element_text(size = 10),
+    axis.title.x = element_text(hjust = 0.5),
+    strip.text = ggtext::element_markdown(
+      size = 10,
+      hjust = 0,
+      padding = margin(0, 0, 0, 0),
+      margin = margin(1, 1, 1, 1)
+    )
+  ) +
+  coord_flip()
+shift_legend(plot.densities_violin_inline)
+```
+
+```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$.
+Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
+Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
+Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
+Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
+'}
+KH_vals = c(1,100)
+
+data.dR0dT <- data.dR0dvar %>%
+  filter((KH %in% KH_vals & sigmaH == 10) | (KH == 100 & is.infinite(sigmaH)))
+
+temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
+  filter(KH %in% KH_vals & sigmaH %in% c(100, Inf)) %>%
+  filter(!is.na(median_R0), median_R0 > eps) %>%
+  group_by(system_ID) %>% 
+  summarise(min_Temp = min(Temperature),
+            max_Temp = max(Temperature))
+
+val_lims <- tibble(sigmaH = unique(data.dR0dT$sigmaH), 
+                   min_median = c(-90, -0.05), 
+                   max_median = c(5, 0.5))
+
+dR0dk.df <- data.dR0dT %>% 
+  filter(
+    KH %in% KH_vals,
+    sigmaH %in% unique(data.dR0dT$sigmaH)
+  ) %>%
+  right_join(select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
+               filter(KH %in% KH_vals & sigmaH %in% unique(data.dR0dT$sigmaH))) %>%
+  # Restrict to relevant temperatures (i.e. where V0 and R0 > 0)
+  right_join(temp_lims) %>% 
+  group_by(system_ID) %>% 
+  filter(Temperature > min_Temp, Temperature < max_Temp) %>% 
+  filter(!is.na(median)) %>% 
+  ungroup() %>% 
+  # Restrict plotted values (so all plots are visible)
+  right_join(val_lims) %>% 
+  group_by(sigmaH) %>% 
+  # filter(median > min_median, median < max_median) %>% 
+  ungroup() %>% 
+  # filter(median_R0 > 0) %>%
+  mutate(abs_median = abs(median)) %>%
+  # Normalize values to better tell which is most important
+  mutate(sign_median = sign(median)) %>%
+  group_by(system_ID, sigmaH, KH) %>%
+  mutate(norm_median = ifelse(sign_median>0,
+                              abs_median / max(median, na.rm = TRUE),
+                              abs_median / min(median, na.rm = TRUE))
+         ) %>%
+  filter(sign_median != 0, !is.na(sign_median)) %>%
+  arrange(sign_median) %>%
+  arrange(Temperature)
+
+# NB: in order to produce an R0 TPC, "overall" derivative should go from positive to negative
+plot.dR0dk <- dR0dk.df %>%
+  # filter(focal_var %in% c("Overall")) %>%
   # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var,
+  ggplot(aes(x = Temperature, y = median, color = focal_var, 
              # linetype = (as.factor(sign_median))
   )) +
-  # geom_area() +
-  # geom_smooth(se = FALSE) +
-  geom_line(lwd = 1) +
+  geom_line(lwd = 0.5) +
   geom_hline(yintercept = 0, lwd = 0.25) +
@@
     name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_fill_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
+    values = rev(c(c4a("misc.okabe", 7), "black"))
   ) +
@@
   scale_y_continuous(
-    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 10$ ")),
-    # limits = c(-100, 100),
-    # limits = c(-0.2, 0.1),
-    # limits = 10^c(-4, 4),
-    # breaks = 10^(seq(-4, 4)),
-    # labels = TeX(c("$10^{-4}$", "$10^{-3}$", "$10^{-2}$", "$10^{-1}$", "$10^0$", "$10^1$", "$10^2$", "$10^3$", "$10^4$")),
-    # trans = "log10",
+    name = unname(TeX("Contribution to local temperature sensitivity of $\\,R_0$")),
+
     expand = c(0, 0)
   ) +
-  # scale_linetype_manual(
-  #   name = "Sign of sensitivity:",
-  #   values = c(1, 3),
-  #   breaks = c(1, -1),
-  #   labels = c("Positive", "Negative")
-  # ) +
-  facet_rep_grid(
-    rows = vars(sigmaH),
+  coord_capped_cart(ylim = c(-1,1)) +
+  facet_grid(
+    rows = vars(KH, sigmaH),
     cols = vars(system_label),
@@
       system_label = sens_labels,
-      # sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-      # KH = as_labeller(appender_KH, default = label_parsed)
+      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
+      KH = as_labeller(appender_KH, default = label_parsed)
     ),
@@
   theme(
+    panel.spacing = unit(1, "lines"),
     legend.margin = margin(0, 0, 0, 0),
@@
 
-plot.compzoom_dR0dk
+plot.dR0dk
 ```

### 2023-12-19 manuscript-figures.Rmd
cleaning up comments and streamlining how data is saved

@@
 library(see) # for half-violin plots
-library(zplyr) #devtools::install_github("burchill/zplyr") from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contdact comparison figure
+library(zplyr) # devtools::install_github("burchill/zplyr") from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contdact comparison figure
 
@@
 
+# Labels for systems
 sens_labels <- as_labeller(c(
@@
 # Load required data ----
-
 eps <- .Machine$double.eps
 
-# Vector trait TPC data
-
-# Create data frame of TPCs
-
+# Run 'code/vector-traits.R' and 'get-outputs.R' first to produce these data
+
+# Vector trait thermal performance curve data
 data.Vec <- read_rds("results/VecTPC_vals.rds") %>%
@@
 
-# Uncomment this to reduce resolution of trait TPCs, to help with memory issues
-# thin_size <- 500
-# num_samples <- length(unique(data.Vec$sample_num))
-# sample_inds <- sample(1:num_samples, thin_size, replace = FALSE)
-# 
-# data.Vec <- filter(data.Vec, sample_num %in% sample_inds)
-
-# R0 data
+# R0 data: thermal performance curves and heatmap
 data.R0_TPCs <- read_rds("results/R0_TPC_vals.rds") %>%
@@
   filter(KH > 0.01)
-
-# Uncertainty data for R0
-R0.HPD <- read_rds("results/R0_HPD_unc.rds") %>%
-  ungroup() %>%
-  pathosystem_labeller() %>%
-  focalvar_labeller()
 
@@
 
-## Get values of vector traits across samples
+## Get summary statistics of vector traits across samples
 # Mean values
@@
 ## Define the contact models
-# For each model, there is a vector-to-host and host-to-vector term
+# For each model, there is a vector-to-host and host-to-vector contact term
 
@@
 
-host_annoyance_threshold <- 100
-sigma_H <- host_annoyance_threshold
+# Biting tolerance
+sigma_H <- 100
 
@@
   ) +
-  # hide legend
+  # hide color legend
   guides(color = FALSE)
@@
     name = "",
-    expand = c(0, 0),
-    # limits = c(0, NA)
+    expand = c(0, 0)
   )
@@
 # y-axes = R0 (normalized so that max(R0) = 1)
-# plots = one for each mosquito+pathogen combination, "system_ID"
+# plots = one for each mosquit0o+pathogen combination, "system_ID"
 # curve 1 = Ross-Macdonald R0 (shape doesn't depend on KH)
@@
   facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
-  # legend
+  # legend:
   guides(
@@
 
-# Value of sigmaH to replace 'Inf' with for plotting
+# Value of sigmaH to replace 'Inf' with for visual plotting
 infinite_skew <- 10^2.35
-# Used to create a gap dividing finite and infinite sigmaH
+# Used to create a visual gap dividing finite and infinite sigmaH
 infinite_divide <- 10^2.7
@@
 
-# Define sigmaH tick breaks and labels
+# Define visual tick breaks and labels for sigmaH (biting tolerance)
 sigmaH_breaks <- c(10^c(seq(-1, 2, by = 1)), 10^2.3125, 10^2.5625)
@@
   ) +
-  # # R0 = 1 contour: use where CTwidth = 0 (i.e. where R0<1 at any temperature)
+  # R0 = 1 contour: uses where CT_width = 0 (i.e. where R0<1 at any temperature)
   geom_contour(
@@
     title.hjust = 0.5,
-    barwidth = 12, # unit(5, "cm"),
+    barwidth = 12,
     show.limits = TRUE
@@
 
+# Set values for vertebrate host population density and biting tolerance
 KH_vals <- c(1, 100)
@@
 
-data.dR0dT <- data.dR0dvar %>%
-  filter((KH %in% KH_vals & sigmaH == sigmaH_val) | (KH == 100 & is.infinite(sigmaH)))
-
+# Calculate temperature limits for each system
 temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-  filter(KH %in% KH_vals & sigmaH %in% c(sigmaH_val, Inf)) %>%
+  filter(KH %in% KH_vals & sigmaH == sigmaH_val) %>%
   filter(!is.na(median_R0), median_R0 > eps) %>%
   group_by(system_ID) %>%
-  summarise(min_Temp = min(Temperature),
-            max_Temp = max(Temperature))
-
-val_lims <- tibble(sigmaH = unique(data.dR0dT$sigmaH), 
-                   min_median = c(-90, -0.05), 
-                   max_median = c(5, 0.5))
-
-dR0dk.df <- data.dR0dT %>%
-  filter(
-    KH %in% KH_vals,
-    sigmaH %in% unique(data.dR0dT$sigmaH)
-  ) %>%
-  right_join(select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-               filter(KH %in% KH_vals & sigmaH %in% unique(data.dR0dT$sigmaH))) %>%
-  # Restrict to relevant temperatures (i.e. where V0 and R0 > 0)
+  summarise(
+    min_Temp = min(Temperature),
+    max_Temp = max(Temperature)
+  )
+
+# Calculate 'proportional contribution to sensitivity' for plotting
+dR0dT.df <- data.dR0dvar %>%
+  # Filter to relevant values of KH and sigmaH
+  filter(KH %in% KH_vals & sigmaH == sigmaH_val) %>% 
+  # Restrict to temperatures where R0 > 0
   right_join(temp_lims) %>%
@@
   ungroup() %>%
-  # Restrict plotted values (so all plots are visible)
-  right_join(val_lims) %>% 
-  group_by(sigmaH) %>% 
-  # filter(median > min_median, median < max_median) %>% 
-  ungroup() %>% 
-  # filter(median_R0 > 0) %>%
-  mutate(abs_median = abs(median)) %>%
-  # Normalize values to better tell which is most important
-  mutate(sign_median = sign(median)) %>%
-  group_by(system_ID, sigmaH, KH) %>%
-  mutate(norm_median = ifelse(sign_median>0,
-                              sign_median * median / max(median, na.rm = TRUE),
-                              sign_median * median / min(median, na.rm = TRUE))) %>%
-  filter(sign_median != 0, !is.na(sign_median)) %>%
-  arrange(sign_median) %>%
-  arrange(Temperature)
-
-comp_dR0dk.df <- dR0dk.df %>%
-  # filter(sigmaH == 10) %>% 
+  # Remove 'Overall' sensitivity: this will be used for comparison
   filter(focal_var != "Overall") %>%
   group_by(system_ID, Temperature, sigmaH, KH) %>%
-  mutate(abs_median = abs(median),
+  mutate(
+    # Absolute value of R0 sensitivities
+    abs_median = abs(median),
+    # Total absolute sensitivity
     total_sens = sum(abs_median),
-         prop_sens = abs_median / total_sens) %>% 
-  arrange(system_label, Temperature, KH, sigmaH, focal_var)
-
-plot.comp_dR0dk <- comp_dR0dk.df %>%
-  filter(is.finite(sigmaH)) %>% 
-  # filter(focal_var %in% c("Overall")) %>%
-  # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = prop_sens, fill = focal_var, color = focal_var,
-  )) +
-  # geom_area() +
+    # Proportion of sensitivity due to particular trait
+    prop_sens = abs_median / total_sens
+  ) %>%
+  arrange(system_label, Temperature, KH, sigmaH, focal_var) %>% 
+  # Calculate change in contribution as host pop. density increases from 1 to 100
+  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
+  pivot_wider(names_from = KH, values_from = prop_sens) %>%
+  mutate(abs_comp = `100` - `1`)
+
+# Plot figure
+plot.compzoom_dR0dk <- dR0dT.df %>%
+  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var, )) +
+  # Plot change in sensitivity contributions
   geom_line(lwd = 1) +
+  # Horizontal line at zero, to emphasize change in sign
   geom_hline(yintercept = 0, lwd = 0.25) +
+  # Color and fill: by focal trait
   scale_color_manual(
@@
   ) +
+  # x- and y- axes
   scale_x_continuous(expand = c(0, 0)) +
   scale_y_continuous(
-    name = unname(TeX("Contributions to overall local sensitivity of $\\,R_0$")),
+    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 100$ ")),
     expand = c(0, 0)
   ) +
+  # Columns = systems
   facet_rep_grid(
-    rows = vars(sigmaH, KH),
     cols = vars(system_label),
@@
       system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-      KH = as_labeller(appender_KH, default = label_parsed)
     ),
@@
   ) +
+  # Add legend
   guides(linetype = guide_legend(
@@
 
-# plot.comp_dR0dk
-
-compzoom_dR0dk.df <- comp_dR0dk.df %>%
-  filter(sigmaH == sigmaH_val) %>% 
-  select(system_ID, Temperature, sigmaH, KH, focal_var, system_label, prop_sens) %>%
-  pivot_wider(names_from = KH, values_from = prop_sens) %>%
-  mutate(abs_comp = `100` - `1`)
-
-plot.compzoom_dR0dk <- compzoom_dR0dk.df %>% 
-  ggplot(aes(x = Temperature, y = abs_comp, fill = focal_var, color = focal_var,
-  )) +
-  geom_line(lwd = 1) +
-  geom_hline(yintercept = 0, lwd = 0.25) +
-  scale_color_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_fill_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(
-    name = unname(TeX("Change in contributions to overall local sensitivity of $\\,R_0$ \n  from $\\,K_H = 1$ to $\\,K_H = 100$ ")),
-    expand = c(0, 0)
-  ) +
-  facet_rep_grid(
-    # rows = vars(sigmaH),
-    cols = vars(system_label),
-    labeller = labeller(
-      system_label = sens_labels,
-      # sigmaH = as_labeller(appender_sigmaH, default = label_parsed),
-      # KH = as_labeller(appender_KH, default = label_parsed)
-    ),
-    scales = "free"
-  ) +
-  guides(linetype = guide_legend(
-    title.position = "left",
-    title.vjust = 0.5,
-    direction = "vertical"
-  )) +
-  theme_minimal_hgrid(10) +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 8),
-    legend.position = "bottom",
-    legend.justification = 0.5,
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text.x = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
 plot.compzoom_dR0dk
@@
 
-```{r fig-S0_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoThermalTraits} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model.
+```{r fig-S0_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoDensity} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model.
 Curves are shown in color for each of the five systems we considered.
@@
 A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
+
 ## Set up plot dataframe
@@
   scale_y_continuous("Equilibrium adult mosquito population density",
-                     expand = c(0.05, 0)) +
+                     expand = c(0.05, 0)
+  ) +
   # color:
@@
 All remaining parameters are given in Table 1 and Figure 3.'}
+
 # Plot R0 vs. temperature and biting tolerance (sigmaH). One panel each for low, mid, high vert host pop density.
@@
 All remaining parameters are given in Table 1 and Figure 3.'}
+
+# Put together dataframe for plotting
 Topt_df <- data.Topt %>%
   filter(KH < 10^4 + 1) %>%
-  pivot_wider(
-    id_cols = c("system_label", "Model", "sigmaH", "KH"),
-    names_from = variable,
-    values_from = c("mean", "median", "lowHCI", "highHCI")
-  ) %>%
-  rename(
-    mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt,
-    highHCI = highHCI_Topt
-  ) %>%
   # Arrange along the plotting variables
@@
 '}
+
 # x-axis = vertebrate host biting tolerance
@@
 
-maxCTmin <- ceiling(max(filter(CTmin_df, CTmin<100)$CTmin))
+maxCTmin <- ceiling(max(filter(CTmin_df, CTmin < 100)$CTmin))
 
@@
 
-minCTmax <- floor(min(filter(CTmax_df, CTmax>0)$CTmax))
+minCTmax <- floor(min(filter(CTmax_df, CTmax > 0)$CTmax))
 
@@
 ```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}
-# Estimating the difference between Topt and Topt_RM numerically using our previous data
+
+# Numerical estimates of the difference between Topt and Topt^RM
 Toptdiff_CCH <- data.Topt %>%
@@
 
-# Calculating Topt0 using the "simplified" equation
+# Calculating Topt_0: Chitnis case
 Topt0_df <- median.Vec %>%
@@
 
-# Calculating Topt0 using the "simplified" equation
+# Calculating Topt_0: Ross-Macdonald case
 ToptRM_df <- median.Vec %>%
@@
 '}
+
 # half-violin plots
 plot.densities_violin_inline <- ggplot() +
-  # CT min
+  # Critical thermal minimum
   geom_violinhalf(
@@
   ) +
-  # CT max
+  # Critical thermal maximum
   geom_violinhalf(
@@
   ) +
+  # x- and y- axes
   scale_x_discrete(
@@
   ) +
+  # linetype:
   scale_linetype(
@@
   ) +
+  # fill:
   scale_fill_discrete(
@@
   ) +
+  # facet by systems
   facet_wrap(~system_label, labeller = labeller(), scales = "free_x") +
@@
   coord_flip()
+
 shift_legend(plot.densities_violin_inline)
+
+# Note: the following text was added via Adobe Illustrator for cases where R0 never exceeds 1:
+# "R_0 < 1 at all temperatures"
 ```
@@
 '}
-KH_vals = c(1,100)
-
-data.dR0dT <- data.dR0dvar %>%
-  filter((KH %in% KH_vals & sigmaH == 10) | (KH == 100 & is.infinite(sigmaH)))
-
+
+# Set population density values of interest
+KH_vals <- c(1, 100)
+
+# Get temperature limits for each system where R0 > 0
 temp_lims <- select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
@@
   group_by(system_ID) %>%
-  summarise(min_Temp = min(Temperature),
-            max_Temp = max(Temperature))
-
-val_lims <- tibble(sigmaH = unique(data.dR0dT$sigmaH), 
-                   min_median = c(-90, -0.05), 
-                   max_median = c(5, 0.5))
-
-dR0dk.df <- data.dR0dT %>% 
-  filter(
-    KH %in% KH_vals,
-    sigmaH %in% unique(data.dR0dT$sigmaH)
-  ) %>%
-  right_join(select(data.R0, system_ID, system_label, Temperature, Model, sigmaH, KH, median_R0 = median) %>%
-               filter(KH %in% KH_vals & sigmaH %in% unique(data.dR0dT$sigmaH))) %>%
+  summarise(
+    min_Temp = min(Temperature),
+    max_Temp = max(Temperature)
+  )
+
+# Put together data frame for plotting
+dR0dT.df <- data.dR0dvar %>%
+  # Filter to KH = 1, 100 and sigmaH = 10, Inf
+  filter((KH %in% KH_vals & sigmaH == 10) | (KH == 100 & is.infinite(sigmaH))) %>% 
   # Restrict to relevant temperatures (i.e. where V0 and R0 > 0)
@@
   group_by(system_ID) %>%
-  filter(Temperature > min_Temp, Temperature < max_Temp) %>% 
-  filter(!is.na(median)) %>% 
-  ungroup() %>% 
-  # Restrict plotted values (so all plots are visible)
-  right_join(val_lims) %>% 
-  group_by(sigmaH) %>% 
-  # filter(median > min_median, median < max_median) %>% 
-  ungroup() %>% 
-  # filter(median_R0 > 0) %>%
-  mutate(abs_median = abs(median)) %>%
-  # Normalize values to better tell which is most important
-  mutate(sign_median = sign(median)) %>%
-  group_by(system_ID, sigmaH, KH) %>%
-  mutate(norm_median = ifelse(sign_median>0,
-                              abs_median / max(median, na.rm = TRUE),
-                              abs_median / min(median, na.rm = TRUE))
-         ) %>%
-  filter(sign_median != 0, !is.na(sign_median)) %>%
-  arrange(sign_median) %>%
-  arrange(Temperature)
-
+  filter(Temperature > min_Temp, Temperature < max_Temp)
+
+# Plot figure
 # NB: in order to produce an R0 TPC, "overall" derivative should go from positive to negative
-plot.dR0dk <- dR0dk.df %>%
-  # filter(focal_var %in% c("Overall")) %>%
+plot.dR0dk <- dR0dT.df %>%
   # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = median, color = focal_var, 
-             # linetype = (as.factor(sign_median))
+  ggplot(aes(
+    x = Temperature, y = median, color = focal_var,
   )) +
+  # lines: values of R0 sensitivities
   geom_line(lwd = 0.5) +
+  # add a line at y = 0 to emphasize sign changes
   geom_hline(yintercept = 0, lwd = 0.25) +
+  # color: focal trait
   scale_color_manual(
@@
   ) +
+  # x- and y- axes:
   scale_x_continuous(expand = c(0, 0)) +
@@
     name = unname(TeX("Contribution to local temperature sensitivity of $\\,R_0$")),
-
     expand = c(0, 0)
   ) +
-  coord_capped_cart(ylim = c(-1,1)) +
+  # Restrict y-axis to -1 to 1
+  coord_capped_cart(ylim = c(-1, 1)) +
+  # Rows = combinations of KH and sigmaH
+  # Columns = systems
   facet_grid(
@@
 
-```{r fig-S9_ddTR0_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:ddTR0_unc} The uncertainty in the sensitivity of $\\mathcal{R}_0$ with respect to temperature.'}
-## Plot R0 uncertainty
-Temp_range_for_plot <- ddTR0.HPD %>%
-  ungroup() %>%
-  dplyr::filter(HPD_width > eps) %>%
-  select(Temperature) %>%
-  range()
-
-plot.ddTR0.rel.sens <- ddTR0.HPD %>%
-  filter(KH %in% c(1) & sigmaH %in% c(100, Inf)) %>%
-  # For each KH value, sum up all uncertainty values to get total uncertainty across parameters
-  group_by(system_ID, sigmaH, KH, Temperature) %>%
-  mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each uncertainty value by the total uncertainty
-  mutate(sens_rel = rel_HPD_width / sens_total) %>%
-  arrange(sens_rel) %>%
-  arrange(focal_var) %>%
-  # Make a stacked plot, colored by parameter
-  ggplot(aes(x = Temperature, y = sens_rel, fill = focal_var)) +
-  geom_area() +
-  scale_fill_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_x_continuous(expand = c(0, 0)) +
-  scale_y_continuous(
-    name = unname(TeX("Relative contribution to $dR_0 / dT$ HPD width"))
-  ) +
-  facet_grid(
-    cols = vars(system_label),
-    rows = vars(sigmaH),
-    labeller = labeller(
-      system_label = sens_labels,
-      sigmaH = as_labeller(appender_sigmaH, default = label_parsed)
-    ),
-    scales = "free"
-  ) +
-  theme_minimal(10) +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 10),
-    legend.position = "bottom",
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text.x = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-
-plot.ddTR0.rel.sens
-```
-
 ```{r fig-S10_Topt_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc} The uncertainty of $T_{\\textrm{opt}}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width when $\\sigma_H$ is 100 bites per vertebrate host per day.
@@
 '}
+
+# Set up data frame and plot
 plot.Topt.rel.sens <- Topt.HPD %>%
@@
   distinct() %>%
+  # Filter to relevant values of KH and sigmaH
   filter(sigmaH == 100) %>%
@@
   geom_area() +
+  # fill: focal trait
   scale_fill_manual(
@@
   ) +
+  # x-axis:
   scale_x_log10(
@@
   ) +
+  # y-axis:
   scale_y_continuous(
@@
   ) +
+  # wrap by system
   facet_wrap(~system_label) +
@@
 
-```{r fig-S10_2_dToptdKH_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_unc2} The uncertainty in the sensitivity of the thermal optimum to host availability as a function of vertebrate host population density when $\\sigma_H = 100$.'}
-dToptdKH.HPD <- dToptdKH.HPD %>%
-  filter(!is.na(rel_HPD_width)) %>%
-  # For each KH value, sum up all uncertainty values to get total uncertainty
-  group_by(system_ID, sigmaH, KH) %>%
-  mutate(sens_total = sum(rel_HPD_width)) %>%
-  # Divide each uncertainty value by the total uncertainty
-  mutate(sens_rel = rel_HPD_width / sens_total)
-
-plot.dToptdKH.rel.sens <- dToptdKH.HPD %>%
-  # Make a stacked plot, colored by parameter
-  ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
-  geom_area() +
-  scale_fill_manual(
-    name = "Focal trait:",
-    values = rev(c4a("misc.okabe", 7))
-  ) +
-  scale_x_log10(
-    name = TeX("Vertebrate host population density (ind/ha)"),
-    expand = c(0, 0),
-    breaks = 10^seq(-2, 4, 1),
-    labels = TeX(c("$0.01$", "$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
-  ) +
-  scale_y_continuous(
-    name = unname(TeX("Relative contribution to $ dT_{opt}/dK_H$ HPD width"))
-  ) +
-  facet_wrap(~system_label) +
-  theme_minimal(10) +
-  theme(
-    legend.margin = margin(0, 0, 0, 0),
-    legend.title = element_text(size = 10),
-    legend.text = element_text(size = 10),
-    axis.title.x = element_text(hjust = 0.5),
-    strip.text.x = ggtext::element_markdown(
-      size = 10,
-      hjust = 0,
-      padding = margin(0, 0, 0, 0),
-      margin = margin(1, 1, 1, 1)
-    )
-  )
-shift_legend(plot.dToptdKH.rel.sens)
-```
-
 ```{r fig-S11_CTmin_uncertainty, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin_unc} The uncertainty of $\\textrm{CT}_{\\min}$ to mosquito traits across vertebrate host population densities as measured by the change in the 95\\% highest posterior density interval width for two values of $\\sigma_H$.
@@
 '}
+
+# Set up dataframe for plotting
 CTmin_df <- CT.HPD %>%
@@
   ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  # Area plot of relative sensitivity/uncertainty
   geom_area() +
+  # fill: focal trait
   scale_fill_manual(
@@
   ) +
+  # x-axis: 
   scale_x_log10(
@@
   ) +
+  # Columns = systems
+  # Rows = sigmaH values
   facet_grid(
@@
 '}
-plot.CTmax.rel.sens <- CT.HPD %>%
+
+# Set up dataframe for plotting
+CTmax_df <- CT.HPD %>%
   filter(variable == "CTmax") %>%
@@
   # Divide each uncertainty value by the total uncertainty
-  mutate(sens_rel = rel_HPD_width / sens_total) %>%
+  mutate(sens_rel = rel_HPD_width / sens_total) # %>%
+
 # Make a stacked plot, colored by parameter
+plot.CTmax.rel.sens <- CTmax_df %>%
   ggplot(aes(x = KH, y = sens_rel, fill = focal_var)) +
+  # Area plot of relative sensitivity/uncertainty
   geom_area() +
+  # fill: focal trait
   scale_fill_manual(
@@
   ) +
+  # y-axis:
   scale_y_continuous(
-    name = unname(TeX("Relative contribution to $CT_{max}$ HPD width"))
-  ) +
+    name = unname(TeX("Relative contribution to $CT_{min}$ HPD width"))
+  ) +
+  # Columns = systems
+  # Rows = sigmaH values
   facet_grid(
@@
 '}
+
+# Set up dataframe and plot
 plot.CTwidth.rel.sens <- CT.HPD %>%
@@
   ) +
+  # columns = systems
+  # rows = sigmaH values
   facet_grid(

### 2023-12-19 code/get-outputs.R

@@ -16,7 +16,7 @@
 ##
 ## Written and maintained by: Kyle Dahlin, kydahlin@gmail.com
 ## Initialized March 2023
-# _______________________________________________________________________________
+# ______________________________________________________________________________
 
 # 0) Set-up, load in necessary packages and data-sets ---------------------
 
@@ -33,23 +33,24 @@ eps <- .Machine$double.eps
 # Suppress summarise info
 options(dplyr.summarise.inform = FALSE)
 
-# Initialize a data frame to save our analyses
-init.df <- tibble(system_ID = character(), Temperature = double(), 
-                  Model = character(), sigmaH = double(), KH = double(), 
-                  variable = character(), lowHCI = double(), highHCI = double(),
-                  mean = double(), median = double())
-
+# Initialize a data frame with correct column names and types
+init.df <- tibble(
+  system_ID = character(), Temperature = double(),
+  Model = character(), sigmaH = double(), KH = double(),
+  variable = character(), lowHCI = double(), highHCI = double(),
+  mean = double(), median = double()
+)
 
 # Load in vector trait data
 data.Vec <- read_rds("results/VecTPC_vals.rds")
-# # Thin out the vector trait data samples
-# thin_size <- 2000
-# samples <- unique(data.Vec$sample_num)
-# num_samples <- length(samples)
-# sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
-# 
-# data.Vec <- data.Vec %>%
-#   filter(sample_num %in% sample_inds)
+
+# Thin out the vector trait data samples
+thin_size <- 100
+samples <- unique(data.Vec$sample_num)
+num_samples <- length(samples)
+sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
+data.Vec <- data.Vec %>%
+  filter(sample_num %in% sample_inds)
 
 # Load in host trait data
 data.Host <- read_rds("results/Host_vals.rds")
@@ -57,61 +58,65 @@ data.Host <- read_rds("results/Host_vals.rds")
[…]

### 2023-12-19 code/host-traits.R

@@ -12,10 +12,10 @@ library(tidyverse)
 
 ## Set resolution for host trait variation
 # Host density vector: Number of values to include to consider for vertebrate host density
-KH_vec_length <- 300
+KH_vec_length <- 30 #300
 
 # Biting tolerance vector: Number of values to consider for biting tolerance
-sigmaH_vec_length <- 300
+sigmaH_vec_length <- 30 #300
 
 ## Host life history & behavioral traits
 # Host recruitment rate:

### 2023-12-19 code/sensitivity.R

@@ -54,6 +54,14 @@ data.Host <- read_rds("results/Host_vals.rds")
 # Vector trait dataset
 data.Vec <- read_rds("results/VecTPC_vals.rds")
 
+# Thin out the vector trait data samples
+thin_size <- 100
+samples <- unique(data.Vec$sample_num)
+num_samples <- length(samples)
+sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
+data.Vec <- data.Vec %>%
+  filter(sample_num %in% sample_inds)
+
 # R0 data
 data.R0 <- read_rds("results/R0_vals.rds")
 
@@ -72,28 +80,12 @@ appender_KH <- function(string) {
   unname(TeX(paste("$K_H = $", string)))}
 
 # 2) Set up mosquito trait data frames ----------------------------------------
+## Get summary statistics of vector traits across samples
+# Mean values
+mean.Vec <- read_rds("results/meanVec_vals.rds")
 
-# Get mean values of mosquito traits
-mean.Vec <- data.Vec %>% 
-  select(-c(KL, mosquito_species, pathogen, muL, etaL)) %>% 
-  pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
-  group_by(system_ID, Temperature, variable) %>% 
-  summarise(mean = mean(value)) %>% 
-  pivot_wider(names_from = "variable", values_from = "mean") %>% 
-  mutate(etaL = rhoL / (deltaL + eps)) %>%
-  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
-  mutate(muL = etaL - rhoL)
-
-# Get meadin values of mosquito traits
-median.Vec <- data.Vec %>% 
-  select(-c(KL, mosquito_species, pathogen, muL, etaL)) %>% 
-  pivot_longer(cols = lf:V0, names_to = "variable", values_to = "value") %>%
-  group_by(system_ID, Temperature, variable) %>% 
-  summarise(median = median(value)) %>% 
-  pivot_wider(names_from = "variable", values_from = "median") %>% 
-  mutate(etaL = rhoL / (deltaL + eps)) %>%
-  # Aquatic-stage mosquito mortality rate. This should be ~infinite if deltaL = 0
-  mutate(muL = etaL - rhoL)
+# Median values (this one is used more frequently)
[…]

### 2023-12-19 code/vector-traits.R

@@ -34,9 +34,9 @@ source("code/data-cleaning.R")
 
 # Run this to generate samples of trait TPC parameters from informed posterior distributions for the first time
 # Set parameters for MCMC
-n.chains <- 5
-n.adapt <- 5000
-n.samps <- 5000
+n.chains <- 2 #5
+n.adapt <- 1000 #5000
+n.samps <- 1000 #5000
 # Do you want to look at diagnostic plots?
 plot_bool <- FALSE
 source("code/get-thermal-trait-priors.R")
@@ -65,7 +65,7 @@ write_csv(table, "results/TPC_fit_summary.csv")
 Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
 
 # Thin sample size
-thin_size <- 5000 # full = 1000, thin = 100
+thin_size <- 1000 # full = 5000, thin = 1000
 
 plot_bool = FALSE
 source("code/trait-transform.R")

### 2023-12-19 code/get-outputs.R
set simulation parameters for analysis

@@ -44,14 +44,6 @@ init.df <- tibble(
 # Load in vector trait data
 data.Vec <- read_rds("results/VecTPC_vals.rds")
 
-# Thin out the vector trait data samples
-thin_size <- 100
-samples <- unique(data.Vec$sample_num)
-num_samples <- length(samples)
-sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
-data.Vec <- data.Vec %>%
-  filter(sample_num %in% sample_inds)
-
 # Load in host trait data
 data.Host <- read_rds("results/Host_vals.rds")
 

### 2023-12-19 code/host-traits.R

@@ -12,10 +12,10 @@ library(tidyverse)
 
 ## Set resolution for host trait variation
 # Host density vector: Number of values to include to consider for vertebrate host density
-KH_vec_length <- 30 #300
+KH_vec_length <- 300
 
 # Biting tolerance vector: Number of values to consider for biting tolerance
-sigmaH_vec_length <- 30 #300
+sigmaH_vec_length <- 300
 
 ## Host life history & behavioral traits
 # Host recruitment rate:

### 2023-12-19 code/sensitivity.R

@@ -54,14 +54,6 @@ data.Host <- read_rds("results/Host_vals.rds")
 # Vector trait dataset
 data.Vec <- read_rds("results/VecTPC_vals.rds")
 
-# Thin out the vector trait data samples
-thin_size <- 100
-samples <- unique(data.Vec$sample_num)
-num_samples <- length(samples)
-sample_inds <- sample(samples, min(num_samples, thin_size), replace = FALSE)
-data.Vec <- data.Vec %>%
-  filter(sample_num %in% sample_inds)
-
 # R0 data
 data.R0 <- read_rds("results/R0_vals.rds")
 

### 2023-12-19 code/vector-traits.R

@@ -34,9 +34,9 @@ source("code/data-cleaning.R")
 
 # Run this to generate samples of trait TPC parameters from informed posterior distributions for the first time
 # Set parameters for MCMC
-n.chains <- 2 #5
-n.adapt <- 1000 #5000
-n.samps <- 1000 #5000
+n.chains <- 5
+n.adapt <- 5000
+n.samps <- 5000
 # Do you want to look at diagnostic plots?
 plot_bool <- FALSE
 source("code/get-thermal-trait-priors.R")
@@ -65,7 +65,7 @@ write_csv(table, "results/TPC_fit_summary.csv")
 Temps <- seq(10, 40, length.out = 601) # full: length.out = 601, thin: length.out = 301
 
 # Thin sample size
-thin_size <- 1000 # full = 5000, thin = 1000
+thin_size <- 5000 # full = 5000, thin = 1000
 
 plot_bool = FALSE
 source("code/trait-transform.R")

### 2023-12-19 manuscript-figures.Rmd
ensure captions are consistent with ms

@@
 Lower panels: The relationships between the number of bites that a host receives per day and host and mosquito densities diverge at low host population densities (c) and, to a lesser extent, at high mosquito densities (d).
-For plots (a) and (c), mosquito population density is fixed at 1000 individuals per km2.
+For plots (a) and (c), mosquito population density is fixed at 1000 individuals per square kilometer.
 For plots (b) and (d), host population density is fixed at 10 individuals per square kilometer.
 Maximum mosquito biting rate is 0.45 bites per mosquito per day and maximum host biting rate is 100 bites per host per day.
-Mosquito and host population densities are plotted on a logarithmic scale.
-'}
+Mosquito and host population densities are plotted on a logarithmic scale.'}
+
 # resolution setting
@@
 Curves are shown in color for each of the five systems we considered.
-Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive).
+Temperatures vary from 10\\textdegree C to 35\\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive).
 Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d).
-Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7.
-The \\textit{Aedes aegypti} and DENV and \\textit{Ae.
+Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics described in Appendix S2.
+The \textit{Aedes aegypti} and DENV and \textit{Ae.
 aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al.
 (2018)).
-All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020.
+All functions and parameters for generating these curves are derived from Mordecai et al.
+(2013, 2017, 2019); Tesla et al.
+(2018); Shocket et al.
+(2020); Villena et al.
+(2022).
 Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions.
 A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
+
 ## Set up plot dataframe
@@
 ```{r fig-4_R0_TPCs, dev = c('pdf','svg', 'png'),  message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:R0_plots} $\\mathcal{R}_0$ as a function of temperature has the usual properties of a thermal performance curve (TPC): it is positive on a single bounded interval and has a unique maximum value.
-The shape of the $\\mathcal{R}_0$ TPC depends on vertebrate host availability and the mosquito-parasite system.
+The shape of the $\\mathcal{R}_0$ TPCdepends on vertebrate host availability and the mosquito-parasite system.
 The shape of the thermal response of $\\mathcal{R}_0$ derived from the Ross-Macdonald model (dotted black curves) is independent of vertebrate host population density while those derived from the Chitnis dynamic model are dependent on vertebrate host population density (solid lines in color).
@@
 Vertebrate host population density is varied on a log$_{10}$ scale.'}
+
 # Plot R0 vs. temperature curves. One plot for each system
@@
 In the Ross-Macdonald model, where biting tolerance is assumed to be infinite, $T_{\\mathrm{opt}}$ is independent of vertebrate host population density (upper bars in plots).
-But when biting tolerance is limited, $T_{\\mathrm{opt}}$ can vary as much as 5\textdegree C (d).
+But when biting tolerance is limited, $T_{\\mathrm{opt}}$ can vary as much as 5\\textdegree C (d).
 $T_{\\mathrm{opt}}$ may increase (d) or decrease (a, b, c, e) as vertebrate host population density or biting tolerance is increased.
@@
 $\\mathcal{R}_0$ is greater than one in the region contained within the black $\\mathcal{R}_0=1$ curve.
-All remaining parameters are given in Table 1 and Figure 3.
-'}
+All remaining parameters are given in Table 1 and Figure 3.'}
+
 # Shows how the transmission thermal optimum depends on vertebrate host availability (density and biting tolerance) in each of the systems we consider.
@@
 All remaining parameters are given in Table 1 and Figure 3.'}
+
 # Shows how the parasite thermal niche (temperatures between CT_min and CT_max)
@@
 
-```{r fig-7_explain_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} Comparison of the local sensitivities of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$.
-Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
-Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
-Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
-Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.'}
+```{r fig-7_explain_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_comp} The change in the contributions of the temperature-dependent mosquito traits to the overall temperature-sensitivity of $\\mathcal{R}_0$ as vertebrate host population density is increased from $1$ to $100$ individuals per hectare.
+There is a fairly consistent pattern in the change in importance for four out of the five systems.But, unlike the others, the \\textit{Anopheles gambiae} and \\textit{Plasmodium falciparum} system displays large changes in the contributions of biting frequency and parasite development rate at low temperatures and relatively small changes for adult mortality rate at warmer temperatures.
+This indicates that, through the incorporation of limited biting tolerance, a change in vertebrate host availability shifts the importance of certain temperature-dependent mosquito traits in determining the temperature-dependence of $\\mathcal{R}_0$.
+Shown here are the median values of $\\bar{\\mathcal{S}_p}(T, 100, 10) - \\bar{\\mathcal{S}_p}(T, 1, 10)$ as described by equation (2.4).'}
 
@@
 
-```{r fig-S0_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoDensity} Thermal performance curves (TPCs) for the mosquito and parasite traits used in our model.
-Curves are shown in color for each of the five systems we considered.
-Temperatures vary from 10\textdegree C to 35\textdegree C to encompass the full thermal niche of all mosquito species considered in this study (defined as the range of temperatures at which all traits for a given species are positive).
-Each trait is a unimodal function of temperature except for the lifespan of \\textit{Culex quinquefasciatus} (d).
-Recruitment rate (a) is derived from a sub-model of immature mosquito population dynamics in equations  (2.6) and (2.7.
-The \\textit{Aedes aegypti} and DENV and \\textit{Ae.
-aegypti} and ZIKV recruitment rate (a) and maximum biting frequency (b) curves overlap because infection is assumed to not affect these traits (but see Tesla et al.
-(2018)).
-All functions and parameters for generating these curves are derived from Mordecai et al., 2013, 2017, 2019; Tesla et al., 2018; Shocket et al., 2020.
-Shown here are the median values of the mosquito traits with respect to their TPC hyperparameter posterior distributions.
-A full description of how these curves were obtained is available in Appendix S2: Section S1.'}
+```{r fig-S0_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoDensity} Equilibrium mosquito population density, $V^*(T)$, as a function of temperature.
+Shown here are the median values of $V^*(T)$ with respect to the mosquito trait TPC hyperparameter posterior distributions.
+Because infection was not assumed to affect life history traits, the \\textit{Aedes aegypti} and DENV and \\textit{Ae.
+aegypti} and ZIKV curves overlap.
+As shown in Equation (2.1), $V^*(T)$ is a function of the immature mosquito development rate, probability of immature mosquito survival to adulthood, eggs per female per day, the adult mortality rate, and the carrying capacity for larval mosquitoes.
+This carrying capacity was assumed to be temperature-independent and set to 300, which resulted in a plausible range of mosquito population densities for the five systems.
+'}
 
@@
 
-```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
-The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
-and \\textit{P.
-falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
-Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
-Shown here are the median values of $T_{\\textrm{opt}}$ with respect to mosquito trait TPC hyperparameter posterior distributions.
-Vertebrate host population density is varied on a $\\log_{10}$ scale.
-All remaining parameters are given in Table 1 and Figure 3.'}
+```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} $\\mathcal{R}_0$ as a function of temperature and biting tolerance  ($\\sigma_H$) across three levels of vertebrate host population density: $0.1$, $1$, and $10$ vertebrate hosts per hectare.
+Shown here are the median values of $\\mathcal{R}_0$ with respect to mosquito trait TPC hyperparameter posterior distributions.
+Vertebrate host biting tolerance is varied on a $\\log_{10}$ scale with a break to indicate values of $\\mathcal{R}_0$ when biting tolerance is unlimited.'}
 
@@
 ```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
-The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles} spp.
-and \\textit{P.
-falciparum} (d) having an over 5\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
+The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles gambiae} and \\textit{Plasmodium falciparum} (d) having an over 5\\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
 Note that the thermal optimum can be an increasing (d) or decreasing (a, b, c, e) function of vertebrate host population density.
@@
 '}
+
 #   x    = biting tolerance (with a point at infinity)
@@
 Shown here are the median values of the critical thermal maximum with respect to mosquito trait TPC hyperparameter posterior distributions.
-Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.
-'}
+Both vertebrate host population density and biting tolerance are varied on a $\\log_{10}$ scale with a break in biting tolerance values to indicate when biting tolerance is unlimited.'}
+
 #   x    = biting tolerance (with a point at infinity)
@@
 All remaining parameters are given in Table 1 and Figure 2.'}
+
 # x-axis = vertebrate host population density
@@
 falciparum} system shows the most drastic differences between the limited and unlimited biting tolerance cases at low vertebrate host population density levels.
-Vertebrate host population density is varied on a $\\log_{10}$ scale.
-'}
+Vertebrate host population density is varied on a $\\log_{10}$ scale.'}
 
@@
 
-```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of $\\sigma_H$ and $K_H$.
-Generally, $\\mathcal{R}_0$ is most sensitive to biting frequency, the probability of surviving the extrinsic incubation period, and vector competence.
-Shown here are the median values of the derivative of $\\mathcal{R}_0$ with respect to each focal mosquito trait across the mosquito trait TPC hyperparameter posterior distributions.
-Sensitivity values are shown on a logarithmic scale with solid lines indicating positive values and dotted lines indicating negative.
-Temperatures are restricted to those at which the median of $\\mathcal{R}_0$ is positive for the given system.
+```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of biting tolerance ($\\sigma_H$) and vertebrate host population density ($K_H$).
+Overall, the sensitivity of $\\mathcal{R}_0$ to temperature decreases at higher temperatures.
+At high temperatures, adult mortality rate is the primary contributor to the temperature sensitivity of $\\mathcal{R}_0$ across all systems and all values of $\\sigma_H$ and $K_H$.
+At lower temperatures, the most important trait varies between the adult mortality rate, biting frequency, parasite development rate, or vector competence, depending on the system in question and values of the vertebrate host traits.
+The values shown here are the median values taken across the mosquito trait TPC hyperparameter posterior distributions of the contributions of each trait to the local sensitivity of derivative of $\\mathcal{R}_0$ to temperature: $\\frac{1}{\\mathcal{R}_0}\\frac{\\partial\\mathcal{R}_0}{\\partial p}\\frac{dp}{dT}$ where $p$ is a focal trait and $T$ is temperature.
+Values were scaled to span from -1 to 1 to enable comparisons across systems.
+Temperatures are restricted to those at which $\\mathcal{R}_0$ is positive for the given system.
 '}
@@
 Eggs per female per day tends to be most important when vertebrate host population density is low, though this not the case for (e) \\textit{Cx.
-quinquefasciatus} and WNV.Immature development rate and the probability of immature survival are never very influential parameters.
+quinquefasciatus} and WNV.
+Immature development rate and the probability of immature survival are never very influential parameters.
 Vertebrate host population density is varied on a $\\log_{10}$ scale.

### 2023-12-19 manuscript-figures.Rmd
match up figure numbers with ms

@@
 
-```{r fig-S0_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoDensity} Equilibrium mosquito population density, $V^*(T)$, as a function of temperature.
+```{r fig-S1_MosquitoDensity, dev = c('pdf','svg', 'png'),  out.width='100%', fig.height=6, fig.width=9, fig.align='center', fig.cap='\\label{fig:MosquitoDensity} Equilibrium mosquito population density, $V^*(T)$, as a function of temperature.
 Shown here are the median values of $V^*(T)$ with respect to the mosquito trait TPC hyperparameter posterior distributions.
@@
 
-```{r fig-S1_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} $\\mathcal{R}_0$ as a function of temperature and biting tolerance  ($\\sigma_H$) across three levels of vertebrate host population density: $0.1$, $1$, and $10$ vertebrate hosts per hectare.
+```{r fig-S2_R0_heatmap_plots_all, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=11, fig.align='center', fig.cap='\\label{fig:R0_heatmap_plots_all} $\\mathcal{R}_0$ as a function of temperature and biting tolerance  ($\\sigma_H$) across three levels of vertebrate host population density: $0.1$, $1$, and $10$ vertebrate hosts per hectare.
 Shown here are the median values of $\\mathcal{R}_0$ with respect to mosquito trait TPC hyperparameter posterior distributions.
@@
 
-```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
+```{r fig-S3_Topt_plots_varyKH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The transmission thermal optimum, $T_{\\textrm{opt}}$, is a sigmoidal function of vertebrate host population density.
 The variation in $T_{\\textrm{opt}}$ varies substantially between the five systems, with \\textit{Anopheles gambiae} and \\textit{Plasmodium falciparum} (d) having an over 5\\textdegree C change in $T_{\\textrm{opt}}$ as vertebrate host population density is increased.
@@
 
-```{r fig-S3_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} The thermal optima predicted by the model can be substantially different at low levels of biting tolerance.
+```{r fig-S4_Topt_plots_varysigmaH, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots} The thermal optima predicted by the model can be substantially different at low levels of biting tolerance.
 At low host population densities, there may be warmer (a, b, c, e) or cooler (d) thermal optima when biting tolerance is low compared to when it is high.
@@
 
-```{r fig-S4_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} The critical thermal minimum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
+```{r fig-S5_CTmin, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmin} The critical thermal minimum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
 Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
@@
 
-```{r fig-S5_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} The critical thermal maximum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
+```{r fig-S6_CTmax, dev = c('pdf','svg', 'png'), dev="cairo_pdf", message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CTmax} The critical thermal maximum for parasite population persistence as a function of vertebrate host population density and biting tolerance.
 Grey areas indicate combinations of vertebrate host population density and biting tolerance in which the parasite population is expected to not persist at any temperature.
@@
 
-```{r fig-S6_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} The critical thermal minimum ($\\textrm{CT}_{\\min}$, blue curves) and maximum ($\\textrm{CT}_{\\max}$, red curves) for parasite population persistence depend on vertebrate host availability, even when vertebrate hosts tolerate any level of mosquito biting (dotted curves).
+```{r fig-S7_CT_Range, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_Range} The critical thermal minimum ($\\textrm{CT}_{\\min}$, blue curves) and maximum ($\\textrm{CT}_{\\max}$, red curves) for parasite population persistence depend on vertebrate host availability, even when vertebrate hosts tolerate any level of mosquito biting (dotted curves).
 Transmission is sustained ($\\mathcal{R}_0$>1) in the regions enclosed by the red and blue curves.
@@
 
-```{r fig-S7_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum and maximum and thermal optimum vary across transmission systems and levels of vertebrate host availability.
+```{r fig-S8_CT_distributions, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:CT_dists} The distributions of the critical thermal minimum and maximum and thermal optimum vary across transmission systems and levels of vertebrate host availability.
 Distributions for the limited biting tolerance case (solid lines) and unlimited biting tolerance case (dashed lines) are shown above and below the vertebrate host population density levels, respectively.
@@
 
-```{r fig-S8_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of biting tolerance ($\\sigma_H$) and vertebrate host population density ($K_H$).
+```{r fig-S9_R0_sensitivity, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:dR0dvar_unc} The local sensitivity of $\\mathcal{R}_0$ to mosquito traits across temperatures for two values of biting tolerance ($\\sigma_H$) and vertebrate host population density ($K_H$).
 Overall, the sensitivity of $\\mathcal{R}_0$ to temperature decreases at higher temperatures.

### 2024-01-25 manuscript-figures.Rmd
final commit for publication

@@
 
-# Uncertainty data for the derivative of R0 wrt temperature
-ddTR0.HPD <- read_rds("results/ddTR0_HPD_unc.rds") %>%
-  ungroup() %>%
-  pathosystem_labeller() %>%
-  focalvar_labeller()
-
 # Uncertainty data for Topt
@@
   ungroup() %>%
-  pathosystem_labeller() %>%
-  focalvar_labeller()
-
-# Derivative of Topt with respect to host pop. density
-dToptdKH.HPD <- read_rds("results/dToptdKH_HPD_unc.rds") %>%
-  ungroup() %>%
-  distinct() %>%
-  filter(!is.na(HPD_width)) %>%
   pathosystem_labeller() %>%

### 2024-01-25 code/AnGamb_lf_just.R

@@ -1,89 +1,0 @@
-# Anopheles gambiae lifespan justification
-library(tidyverse)
-
-# Get appropriate data
-data <- read_rds("data/clean/data_for_TPC_fitting.rds") %>% 
-  filter(system_ID %in% c(
-    "Anopheles gambiae / Plasmodium falciparum",
-    "Anopheles gambiae / Plasmodium spp.",
-    "Anopheles gambiae / none",
-    "Anopheles spp. / Plasmodium falciparum",
-    "Anopheles spp. / Plasmodium spp.",
-    "Anopheles spp. / none"),
-    trait.name %in% c("lf")
-  ) %>% 
-  arrange(T)
-
-# Set up nonlinear fits
-y = data$trait
-x = data$T
-
-# Get fits
-Briere_fit <- nls(y ~ c * x * (x - T0) * sqrt(Tm - x),
-                  start = list(c = 1, T0 = 0, Tm = 50))
-Quad_fit <- nls(y ~ -c * (x - T0) * (x - Tm),
-                start = list(c = 1, T0 = 0, Tm = 50))
-z = 1/y
-mu_Quad_fit <- nls(z ~ c * x^2 - r * x + t,
-                   start = list(c = 1, r = 1, t = 1))
-
-# Collect fits
-fit_table <- tibble(T = seq(0,50, by = 0.1), 
-                    Briere = predict(Briere_fit, newdata = list(x = seq(0,50, by = 0.1))), 
-                    Quadratic = predict(Quad_fit, newdata = list(x = seq(0,50, by = 0.1))), 
-                    mu_Quadratic = 1/predict(mu_Quad_fit, newdata = list(x = seq(0,50, by = 0.1)))
-                    ) %>% 
-  pivot_longer(cols = c("Briere", "Quadratic", "mu_Quadratic"), names_to = "model") %>% 
-  group_by(T) %>% 
-  mutate(abs_change = (value[model == "mu_Quadratic"] - value),
-         perc_change = abs_change / value[model == "mu_Quadratic"]
-         )
-
-# Determine where V0 is greater than zero
-temp_lims <- read_rds("results/medianVec_vals.rds") %>% 
-  filter(system_ID ==  "Anopheles gambiae / Plasmodium falciparum",
-         V0 > 0
-         ) %>% 
-  summarise(min_Temp = min(Temperature),
-            max_Temp = max(Temperature))
-  
-
-trait_plots <- fit_table %>% 
-  ggplot(aes(x = T)) +
[…]

### 2024-01-25 code/data-cleaning.R

@@ -35,7 +35,7 @@ library(tidyverse)
 #    taken from Supplementary Data of Mordecai 2013. See Bayoh2001-lifespan-analysis.R for details)
 data.Mordecai2013 <- read.csv("data/raw/Mordecai_2013/Mordecai_2013_supp_data.csv", header = TRUE) %>%
   # Add in lifespan data
-  rbind(read_csv("data/clean/Bayoh2001_mortality.csv")) %>% 
+  rbind(read_csv("data/raw/Mordecai_2013/Bayoh2001_mortality.csv")) %>% 
   mutate(lead_author = "Mordecai") %>%
   # Make bc a probability
   mutate(trait = ifelse(trait.name == "bc", trait / 100, trait)) %>% 
